### 2013-12-16 docs/evol.tex
added initial repo

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
%\documentclass{sig-alternate}

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{color}
%\usepackage[T1]{fontenc}
\usepackage{titling}

\pdfpagewidth=8.5in
\pdfpageheight=11in

\begin{document}

\date{}

\title{\Large \bf Dismal Code: Studying the Evolution of Security Bugs}

%\setlength{\droptitle}{-0.05em}

\author{
{\rm Dimitris Mitropoulos, Vassilios Karakoidas, Panos Louridas}\\
{\it Department of Management Science and Technology,}\\
{\it Athens University of Economics and Business}\\
{\tt dimitro@aueb.gr, bkarak@aueb.gr, louridas@aueb.gr}
%\and
%{\rm Vassilios Karakoidas}\\
%Department of Management Science and Technology,
%Athens University of Economics and Business
%\and
%{\rm Panos Louridas}\\
%Department of Management Science and Technology,
%Athens University of Economics and Business
\and
{\rm Georgios Gousios}\\
{\it Software Engineering Research Group,}
{\it Delft University of Technology}\\
{\tt G.Gousios@tudelft.nl}
\and
{\rm Diomidis Spinellis}\\
{\it Department of Management Science and Technology,}\\
{\it Athens University of Economics and Business}\\
{\tt dds@aueb.gr}
}

\maketitle
%\thispagestyle{empty}
\thispagestyle{empty}
\pagestyle{empty}

\subsection*{Abstract}
{\bf Background.} Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.\\
{\bf Aim.} We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. Specifically, we studied
the evolution of security bugs through time. In addition, we examined
their persistence and their relationship with
a) the size of the corresponding version, and
b) other bug categories.\\
{\bf Method.} We analyzed every project version of the Maven repository by
using FindBugs, a popular static analysis tool.
To see how security bugs evolve over time we took advantage of
the repository's project history and dependency data.\\
{\bf Results.} Our results indicate that there is no simple rule governing
the number of security bugs as a project evolves.
In particular, we cannot say that across projects security-related
defect counts increase or decrease significantly over time.
Furthermore, security bugs are not eliminated in a
way that is particularly different from the other bugs.
In addition, the relation of security bugs with a project's size
appears to be different from the relation of the bugs
coming from other categories.
Finally, even if bugs seem to have similar behaviour,
severe security bugs seem to be unassociated with other bug categories.\\
{\bf Conclusions.} Our findings indicate that further research should be done
to analyze the evolution of security bugs. Given the fact that our experiment
included only Java projects, similar research could be done for another
ecosystem. Finally, the fact that projects have their own idiosyncrasies
concerning security bugs, could help us find the common characteristics
of the projects where security bugs increase over time.

\section{Introduction}

A security bug is a programming error that introduces a potentially exploitable
weakness into a computer system~\cite{SSL12}. This
weakness could lead to a security breach with unfortunate consequences in
different layers, like databases, native code, applications, libraries and
others. Despite the significant effort to detect and eliminate such
bugs, little attention has been paid to study them in relation to
software evolution~\cite{LRWPT97}. 
One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it.

In this paper we present how we used a large software ecosystem to analyse the
relationship of different types of security vulnerabilities to 
evolving software packages.
For our research we used {\it FindBugs},\endnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,HP07,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
(approximately 265{\sc gb} of data---see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
%This research builds upon our earlier work on the topic~\cite{MGS12}.

We chose to focus our study on security bugs rather than other types of
software defects. This is because compared to other bug categories,
failures due to security bugs have two distinct features:
they can severely affect an organization's infrastructure~\cite{SZ12}, and
they can cause significant financial damage to
an organization~\cite{TH04,BCL08}. 
Specifically,
whereas a software bug can cause a software artifact to fail,
a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain.
In this case, such bugs could give rise to a wide
range of security and privacy issues, like
the access of sensitive information,
the destruction or modification of data, and
denial of service.	
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be to mitigate such bugs.

% @dimitro: say why we did this work, not how we did it
The motivation behind our work was to validate whether programmers care for
the risk posed by security bugs when they release a new version of their software.
In addition, we wanted to investigate other critical features associated with such
vulnerabilities like the persistence of a bug;
in essence, to see whether critical bugs stay unresolved for a long time.
Also, we wanted to elaborate more on the relation of security
bugs with other bug categories.
In the same manner, we tried to examine the relationship
between the size of a project release and the number of security bugs that it contains,
knowing the that research has produced contradictory results on this
issue~\cite{SYTP85,NBZ06,GKMS00}.
Finally, we examined the Maven ecosystem as a whole from a security
perspective. Its structure gave us the opportunity to see if a project version that is a dependency of
a large number of others contains a low rate of security bugs.
%In this case we can strengthen the relationship between Linus' Law and
%software security as Meneely et al. have already indicated~\cite{MW10}.

In this work we:
\begin{itemize}
	\item Analyze how security bugs found through static analysis
evolve over time. To achieve this, we inspected all releases of every project.
Our hypothesis is that security bugs should decrease as a project evolves,
for they form critical issues, which developers should eliminate.
%We present evidence that defect counts remain relatively stable
%across project revisions.
	\item Examine security bug persistence across releases. 
We expect that security bugs should be eliminated earlier than other bugs.
%We find that a specific defect remains unfixed on average 
%for 3 revisions.
	\item Study the relation between security bugs and a project
release's size. Our hypothesis is that security bugs are proportional to a project
release's size (defined in terms of bytecode size).
%We show that many defect types are correlated with the project's
%size (with the notable exception of high-risk security defects).
	\item Examine the correlation of security bugs with other bug categories.
Our hypothesis is that security bugs appear together with bugs that
are related with performance, coding practices, and product stability.
%We show that a code base can have defect hotspots.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
  %\item Make available a carefully constructed dataset and a statistical toolkit for
   % performing analysis of the Java Maven ecosystem.
\end{itemize}

In the rest of this paper we
outline related work (Section \ref{sec:rel}),
describe the processing of our data and our experiment (Section \ref{sec:meth}),
present and discuss the results we obtained (Section \ref{sec:res}),
and end up with a conclusion and directions for future work (Section \ref{sec:con}).

\section{Related Work}
\label{sec:rel}

There are numerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions.

{\it Refactoring identification} through software evolution is an approach used to
relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
ratio of refactorings is usually followed by an increasing ratio of bug
reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
after an incomplete refactoring~\cite{GW05}.
Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
refactorings aid bug fixes.

{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach
involved the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
pattern prevalence tends to be the same in software collections.

{\it Querying techniques} are used to answer a broad range of questions
regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
al.~\cite{BN11,B11} proposed a framework that is based on
recursively enumerable languages. The framework can correlate software
bugs with developers in various ways. For instance, return the list of
bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
an approach for populating a release history database that combines code
information with bug tracking data. In this way, a developer can couple files
that contain common bugs, estimate code maturity with respect to the bugs,
etc. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
framework that integrates information about the Debian project from various
sources to answer queries related to software bugs and source code.

D'Ambros et al. have used {\it bug history analysis} to detect
the critical components of a project~\cite{D08}. This is done by using an
evolutionary meta-model~\cite{DL08}. The same approach was
also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
of bugs with software properties like code complexity, process quality and others
and to predict future properties.

The evolution of software artifacts has also been analysed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former, they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter, they computed a signature for every bug. This
signature contained elements like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b} proposed a history-based warning
prioritization algorithm by mining the history of bug-fixes of three
different projects. Working towards the same direction, Heckman
et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.

Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
Specifically, they analysed the changes of Linux file-system patches to extract
bug patterns and categorize bugs based on their impact. Their findings
indicated that the number of file-system bugs does not die down over time. By
categorizing bugs they also showed the frequency of specific bugs in specific
components.

Completing the above approaches, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea.
Ozment and Schechter~\cite{OS06} examined the code base of the Open{\sc bsd}
operating system to determine whether its security is increasing
over time. In particular, they measured the rate at which new code
has been introduced and the rate at which defects have been reported over
a 7.5 year period and fifteen releases.
Even though the authors present statistical evidence
of a decrease in the rate at which vulnerabilities are being reported,
defects seem to appear persistent for a period of at least 2.6 years.
Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\endnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research presented evidence that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
a study similar  to ours in which they have considered only four projects.
Their results demonstrate that the number of exploitable bugs does not
always improve with each new release and that the rate of discovery of
exploitable bugs begins to drop three to five years after the
initial release.

\section{Methodology}
\label{sec:meth}

Our experiment involved the collection of the metric results of the
FindBugs tool. Before and during the experiment, we performed a number
of filters on the data coming from the Maven repository, for reasons
that we will describe below.

\subsection{Experiment}
\label{sec:exp}

The goal of our experiment was to retrieve all the bugs that FindBugs reports,
from all the project versions existing on the Maven repository (in the Maven
repository, versions are {\it actual} releases). The experiment involved four entities:
a number of {\it workers} (a custom Python script), a {\it task queue}
mechanism (Rabbit{\sc mq}---version 3.0.1),
a {\it data repository} (Mongo{\sc db}---version 2.2),
and the {\it code repository}, which in our case it was
the public Maven repository.

%\begin{table}
%\centering
%\begin{threeparttable}
%\caption{Experiment Entities}
%\label{tbl:exp}
%\begin{tabular}{l r r}
%\hline
%Entity & Software Package & Version\\
%\hline
%Worker & Custom Python Script & 2.7\\
%Task Queue & RabbitMQ & 3.0.1 \\
%Data Repository & MongoDB & 2.2 \\
%Code Repository & Maven Central Repository & January 2012 \\
%\hline
%\end{tabular}
%\end{threeparttable}
%\end{table}

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.
It uses {\sc xml} to describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins.
To build a software component, it dynamically downloads Java libraries
and Maven plug-ins from the Maven central repository,
and stores them in a local cache. The repository can be updated with
new projects and also with new versions of existing projects.

First, we scanned the Maven repository for appropriate {\sc jar}s and created a
list that included them. We discuss the {\sc jar} selection process in the next 
section. With the {\sc jar} list at hand, we created a series of processing tasks
and added them to the task queue. Then we executed twenty five (Unix-based)
workers that checked out tasks from the queue, processed the data and stored the
results to the data repository.

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. When the task was completed the queue
was notified and the next task was requested. This process was executed for
all the available {\sc jar}s in the task queue. A schematic representation of
the data processing architecture can be seen in Figure~\ref{fig:arch}.

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The data processing architecture.}
  \label{fig:arch}
\end{figure}

\subsection{Data Provenance}
\label{sec:data}

Initially, we obtained a snapshot (January 2012) of the Maven repository and
handled it locally to retrieve a list of all the names of the project versions
that existed in it. A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.

FindBugs works by examining the compiled Java virtual
machine bytecodes of the programs it checks, using the bytecode engineering
library ({\sc bcel}).
To detect a bug, FindBugs uses various formal methods like
{\it control flow} and {\it data flow
analysis}. It has also other detectors that employ {\it visitor patterns} over
classes and methods by using {\it state machines} to reason about values stored
in variables or on the stack.
Since FindBugs analyses applications written in the Java
programming language, and the Maven repository
hosts projects from languages other than Java such as Scala, Groovy,
Clojure, etc., we filtered out such projects by performing a series of checks in
the repository data and metadata.

In addition, we implemented a series of audits in the worker scripts that
checked if the {\sc jar}s are valid in terms of implementation. For instance,
for every {\sc jar} the worker checked if there were any {\it .class} files
before invoking FindBugs. After the project filtering, we narrowed down
our data set to 17,505 projects with 115,214 versions.
Table~\ref{tbl:repository} summarises the data set information and
provides the basic descriptive statistic measurements. The distribution of version
count among the selected projects is presented in Figure~\ref{fig:version-count}.

The statistical measurements presented in Table~\ref{tbl:repository}
indicate that we have 17,505 projects and the data set's median is 3,
which means that almost 50\% (8,753 projects) of the project
population have 1 to 3 versions. In general, most projects have a few
number of versions, there are some projects with ten versions and
only a few with hundreds of versions. The maximum number of versions
for a project is 338. The 3$^{rd}$ quartile measurement also indicated
that 75\% (13,129) of the projects have a maximum of 8 versions.

\begin{table}[t]
\centering
\caption{Descriptive statistics measurements for the Maven repository.}
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 115,214\\
Min (versions per project) & 1\\
Max (versions per project) & 338\\
Mean (versions per project) & 6.58\\
Median (versions per project) & 3\\
Range (over versions) & 337\\
1$^{st}$ Quartile (over versions) & 1\\
3$^{rd}$ Quartile (over versions) & 8\\
\hline
\end{tabular}
\end{table}

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.37]{version_count.pdf}
	\caption{Distribution of version count among project population.}
	\label{fig:version-count}
\end{figure}

\subsection{Threats to Validity}
\label{sec:threats}

A threat to the internal validity of our experiment could be the false alarms of the
FindBugs tool~\cite{AP10, HP04}. False positives and negatives of static analysis tools and
how they can be reduced is an issue that has already been discussed in the literature
(see Section~\ref{sec:rel}).
In addition, reported security bugs may not be applicable to an
application's typical use context.
For instance, FindBugs could report an {\sc sql} injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false positive alarm.

Furthermore, given that our analysis is done on open-source projects
written in the Java programming language and hosted on Maven,
a threat to the external validity of our work
is the fact that our results may not be applicable to other
programming languages, ecosystems, and development cultures.
In particular, a large class of security problems such as
buffer overflows~\cite{K11} do not apply in our study since
Java enforces bound checking at runtime.

\section{Results and Analysis}
\label{sec:res}

Our findings can be analysed at two levels. First, we discuss some
primary observations concerning the security bugs of the Maven repository as a whole.
Then, we provide a comprehensive analysis of the results and highlight our key findings.

\begin{table*}[t]
\centering
\caption{Bug categorisation according to FindBugs.}
\label{tbl:bug-cat}
\begin{tabular}{l p{29em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table*}

\subsection{Overview and Initial Results}
\label{sec:overview}

FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
Malicious Code}. From the total number of releases, 4,353 of them contained
at least one bug coming from the first category
and 45,559 coming from the second.

Our first results involve the most popular bugs in the Maven repository.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories - 0.21\% + 21.81\%) are the most popular in the repository ($\geq 21\%$ each).
This could be a strong indication that programmers write code
that implements the required functionality without considering its many
security aspects; an issue that has already been reported in
literature~\cite{SH09}.
% An interesting observation is that 4,908 projects did not
% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
% This goes along with the relationship between the size of an artifact and it's
% bugs that is presented in the upcoming section.

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.35]{bug_percent}
	\caption{Bug percentage in Maven repository.}
	\label{fig:bug-per} 
\end{figure}

Another observation involves bugs that we could call {\it
Security High} and they are a subset of the {\it Security} category.
Such bugs are related to vulnerabilities that appear due to the lack of user-input
validation and can lead to damaging attacks like {\sc sql} injection and
Cross-Site Scripting~\cite{RL12}.
To exploit such vulnerabilities, a malicious user does
not have to know anything about the application internals.
For almost all the other security bugs (coming from
the {\it Malicious Code} category and the rest of
the {\it Security} category bugs),
another program should be written to incorporate references to
mutable objects, access non-final fields, etc.
Also, as bug descriptions indicate,\endnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
if an application has bugs coming from the {\it Security High} category,
it might have more vulnerabilities that FindBugs doesn't report.
Table~\ref{tbl:severe} presents the number
of releases where at least one of these bugs exists. In essence, 5,501 releases
($\approx 4,77\% $), contained at
least one severe security bug. Given the fact that other projects include these
versions as their dependencies, they are automatically rendered vulnerable if
they use the code fragments that include the defects.
The remaining bugs of the {\it Security} category
are grouped together with the bugs of the {\it Malicious Code} category
in another subcategory that we call {\it Security Low}.
This category contains for the most part, bugs
that imply violations of good {\sc oop} (object-oriented programming)
design (i.e. keeping variables private to classes and others).
The above categorization was done specifically to point out the
behaviour of bugs that currently top the corresponding lists of most
security providers.\endnote{\url{http://cwe.mitre.org/top25/index.html}}

\begin{table*}[t]
\centering
\caption{Number of project releases that contain at least one ``Security
  High" bug.}
\label{tbl:severe}
\leavevmode
	\begin{tabular}{p{31em} r}
	\hline
	Bug Description & Number of Project Releases\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
	{\sc pt}: absolute path traversal in servlet  & 103\\
	{\sc pt}: relative path traversal in servlet & 57\\
	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
	\hline
	\end{tabular}
\end{table*}

{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow''.
In a context like this, we expect that
the project versions that are dependencies to many other projects
would have a small number of security
bugs. To examine this variation of the Linus's Law and highlight the
{\it domino effect}~\cite{TH04} we did the
following: during the experiment we retrieved the
dependencies of every version. Based on this information we created a graph
that represented the snapshot of the Maven repository. The
nodes of the graph represented the versions and the vertices their dependencies.
The graph was not entirely accurate. For instance, if
a dependency was pointing only to a project (and not to a specific version), we chose to
select the latest version found on the repository. Also, this graph is not
complete. This is because there were missing versions.
% Practically, the corresponding {\it pom}, or {\it war} files existed on the
% repository, but the {\sc jar} file did not.
From the 565,680 vertices, 191,433
did not point to a specific version while 164,234 were pointing to missing ones.
The graph contained 80,354 nodes. Obviously, the number does not correspond to
the number of the total versions (see Section~\ref{sec:data}). This is because
some versions did not contain any information about their dependencies so they
are not represented in the graph. After creating the graph, we ran the PageRank
algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
examined the security bugs of the fifty most popular nodes based on their PageRank.
Contrary to Linus's Law, thirty three of them contained bugs coming from the
{\it Security Low} subcategory, while two of them contained {\it
  Security High} bugs.
Twenty five of them were latest versions at the time. This also highlights
the domino effect.
%No matter how well a programmer secures a software component
%it won't matter if he or she is using vulnerable code fragments coming
%from another library.

\subsection{Analysis}
\label{sec:analysis}

Here, we present our key findings concerning the evolution of security bugs.

\subsubsection{How Security Bugs Evolve Over Time}

The relation between bugs and time can be traced from the number of
bugs per category in each project version. We can then calculate the
Spearman correlations between the defects count and the ordinal
version number across all projects to see if bigger versions relate to
higher or lower defect counts. The results are shown in
Table~\ref{tbl:bugsperversion}. Although the tendency is for defect
counts to increase, this tendency is extremely slight.

The zero tendency applies to all versions of all projects together. 
The situation might be different in individual projects. We therefore
performed Spearman correlations between bug counts and version
ordinals in all projects we examined. These paint a different picture
from the above table, shown in Figure~\ref{fig:bugsversionscorr}. The
spike in point zero is explained by the large number of projects for
which no correlation could be established---note that the scale is
logarithmic. Still, we can see that there were projects where a
correlation could be established, either positive or negative. The
{\it Security High} category is particularly bimodal, but this is
explained by the small number of correlations that could be
established, nine in total.

Overall, Table~\ref{tbl:bugsperversion} and
Figure~\ref{fig:bugsversionscorr} suggest that \textbf{we cannot say that
across projects defect counts increase or decrease significantly
across time}. In individual projects, however, defect counts can have a
strong upwards or downwards tendency. There may be no such thing as a
``project'' in general, only particular projects with their own
idiosyncrasies, quality features, and coding practices.

Another take on this theme is shown in Figure~\ref{fig:bugdiffs},
which presents a histogram of the changes of different bug counts in
project versions. In most cases, a bug count does not change between
versions; but when it does change, it may change upwards or downwards.
Note also the spectacular changes of introducing or removing thousands
of defects; this may be the result of doing and undoing a pervasive
code change that runs foul of some bug identification rule.

\begin{table}[tphp]
    \centering
    \caption{Correlations between version and defects count.}
    \label{tbl:bugsperversion}
    \input{bugsperversion.tex}
\end{table}

\begin{figure*}[p]
  \centering
  \includegraphics[scale=0.30]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
  \centering
  \includegraphics[scale=0.35]{bugdiffs}
  \caption{Changes in bug counts between versions.}
  \label{fig:bugdiffs}
\end{figure*}

\subsubsection{Persistence of Security Bugs}

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project. To
``tag" a bug we created a bug identifier by using the type of the bug,
the method name and the class name in which the bug was found in. We
chose not to use the line number of the location of the bug since it
could change from version to version and after a possible code
refactoring. We grouped the persistence numbers by bug categories and
then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
category pairs. The results are presented in
Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
brackets show pairs where no statistically significant difference was
found.

In general, although the average number of versions bugs in different
bug categories that remained open was statistically different in many
cases, the difference is not spectacular. \textbf{In all cases a bug persists
on average between two and three versions}, with the difference being
in the decimal digits.

\subsubsection{The Relation of Defects with the size of a JAR}

We explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results, all statistically significant ($p
\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
  Security High} category stands out by having a remarkably lower
effect than the other categories}, even {\it Security Low} that nearly
tops the list. As we mentioned earlier, bugs that belong to the
{\it Security High} category are related to
user-input validation issues. Hence, even if a programmer adds
code to a new version, if this code does not require user
input, the possibility of such bug is minimal. 
% dds proposed the following:
%Given that, we could say that it would be productive to search for and fix
%security bugs even if a project grows bigger.

\begin{table}[hbt]
    \centering
    \caption{Correlations between {\sc jar} size and defects count.}
    \label{tbl:jarsizecorr}
    \input{jarsizecorr.tex}
\end{table}

\subsubsection{Security Bugs VS Other Bug Categories}

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime, see Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general \textbf{bugs do flock together}.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard. Thus, to find such
defects, code reviewers with experience in software security
issues might be needed.

%\begin{table*}[t]
%    \centering
%    \caption{Correlation matrix}
%    \label{tbl:corrmatrix}
%    \input{corrmatrix.tex}
%    \\
%    \small The matrix presents pairwise correlations between the
%        different bug categories.
%\end{table*}

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.43]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories.}
  \label{fig:corrplot}
\end{figure}

\section{Conclusions and Future Work}
\label{sec:con}

We analysed more than 260{\sc gb} of interdependent project versions to see
how security bugs evolve over time, their persistence, their relation
with other bug categories, and their relationship with size in terms
of bytecode.\endnote{Our data and code are available online at:
\url{https://github.com/bkarak/evol_security_publication_2012}}

Our primary hypothesis was that security bugs, and especially severe
ones, would be corrected as projects evolve. We found that, although
bugs do close over time in particular projects, we do not have an indication that across
projects they decrease as projects mature. Moreover, defect counts may
increase, as well as decrease in time. Contrary to our second research hypothesis,
we found that security
bugs are not eliminated in a way that is particularly different from the other bugs.
Also, having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. Concerning the relation between
severe security bugs and a project's size
we showed that they are not proportionally related.
Given that, we could say that it would be productive to search for and fix
security bugs even if a project grows bigger.
Furthermore, the pairwise correlations between all categories
indicated that even though all the other
categories are related, severe bugs do not appear together with the other bugs.
Also, it is interesting to see that security bugs were one of the top two
bug categories existing in a large ecosystem. Finally, we highlighted the
domino effect, and showed evidence that indicates that Linus's Law does not
apply in the case of the security bugs.

Contrary to the approaches that examine versions
formed after every change that has been committed to the repository,
our observations are made from a different perspective.
The versions examined in this work were actual releases
of the projects. As a result we do not have an indication of how many changes
have been made between the releases.
In essence, these {\sc jar}s were the ones that were or still are,
out there in the wild, being used either as applications,
or dependencies of others.

Furthermore, the fact that projects have their own idiosyncrasies concerning
security bugs, could help us answer questions like: what are the common
characteristics of the projects where security bugs increase over time?
In addition, by examining source code repositories more closely we could see how
different development styles (i.e. size of commits, number of developers)
affect projects.

By selecting an large ecosystem that includes applications written only
in Java, we excluded by default measurements that involve vulnerabilities like
the infamous buffer overflow defects~\cite{K11}. Still, by examining software
artifacts with similar characteristics facilitates the formation of
an experiment. Thus, future work on our approach could also involve
the observation of other ecosystems, that serve different languages,
in the same manner such as, Python's PyPY (Python Package Index),
Perl's {\sc cpan} (Comprehensive Perl Archive Network), and Ruby's
RubyGems.

\section{Acknowledgments}
This research has been co-financed by the European Union (European Social Fund
- {\sc esf}) and Greek national funds through the Operational Program
``Education and Lifelong Learning'' of the National Strategic Reference Framework -
Research Funding Program: Heracleitus II. Investing in knowledge society
through the {\sc esf}.

%The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
%and national funds and is a part of the Operational Programme ``Competitiveness \&
%Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).

{\footnotesize \bibliographystyle{acm}
\bibliography{evol}

\theendnotes

\begin{landscape}
  \begin{table}
    \setlength{\extrarowheight}{0.10cm}
    \caption{Bug persistence comparison.}
    \label{tbl:bug_persistence}
    \resizebox{0.95\columnwidth}{!}{
    \input{bug_persistence.tex}}\\
    The matrix presents pairwise Mann-Whitney $U$ test results
    between the different bug categories. Each cell contains the test
    result (the value of $U$), the $p$-value, the average for each
    category and the sample size for each category. Cells in brackets show
    pairs where no statistically significant difference was found.
  \end{table}
\end{landscape}

\end{document}

### 2013-12-16 docs/old style/evol.tex
added initial repo

--- 2013-12-16 docs/evol.tex
@@
-\documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
-%\documentclass{sig-alternate}
+\documentclass[conference]{llncs}
 
@@
 \usepackage{array}
-\usepackage{color}
-%\usepackage[T1]{fontenc}
-\usepackage{titling}
-
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
 
@@
 
-\date{}
+\title{Dismal Code: Studying the Evolution of Security Bugs}
 
-\title{\Large \bf Dismal Code: Studying the Evolution of Security Bugs}
-
-%\setlength{\droptitle}{-0.05em}
-
-\author{
-{\rm Dimitris Mitropoulos, Vassilios Karakoidas, Panos Louridas}\\
-{\it Department of Management Science and Technology,}\\
-{\it Athens University of Economics and Business}\\
-{\tt dimitro@aueb.gr, bkarak@aueb.gr, louridas@aueb.gr}
-%\and
-%{\rm Vassilios Karakoidas}\\
-%Department of Management Science and Technology,
-%Athens University of Economics and Business
-%\and
-%{\rm Panos Louridas}\\
-%Department of Management Science and Technology,
-%Athens University of Economics and Business
-\and
-{\rm Georgios Gousios}\\
-{\it Software Engineering Research Group,}
-{\it Delft University of Technology}\\
-{\tt G.Gousios@tudelft.nl}
-\and
-{\rm Diomidis Spinellis}\\
-{\it Department of Management Science and Technology,}\\
-{\it Athens University of Economics and Business}\\
-{\tt dds@aueb.gr}
-}
+\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Georgios Gousios \and Diomidis Spinellis }
+\institute{ Department of Management Science and Technology\\
+			Athens University of Economics and Business\\
+      		\email{\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
+			Software Engineering Research Group\\
+			Delft University of Technology\\
+			\email{G.Gousios@tudelft.nl}}
 
 \maketitle
-%\thispagestyle{empty}
-\thispagestyle{empty}
-\pagestyle{empty}
 
-\subsection*{Abstract}
-{\bf Background.} Security bugs are critical programming errors that can lead to serious
+\begin{abstract}
+%\boldmath
+Security bugs are critical programming errors that can lead to serious
 vulnerabilities in software. Such bugs may allow an attacker to take over
-an application, steal data or prevent the application from working at all.\\
-{\bf Aim.} We used the projects stored in the Maven repository to study the
+an application, steal data or prevent the application from working at all.
+We used the projects stored in the Maven repository to study the
 characteristics of security bugs individually and in relation to other software
-bugs. Specifically, we studied
+bugs. In particular, we analyzed every project version of the repository by using a
+popular static analysis tool. Then, by taking advantage of
+the repository's project history and dependency data we studied
 the evolution of security bugs through time. In addition, we examined
@@
 a) the size of the corresponding version, and
-b) other bug categories.\\
-{\bf Method.} We analyzed every project version of the Maven repository by
-using FindBugs, a popular static analysis tool.
-To see how security bugs evolve over time we took advantage of
-the repository's project history and dependency data.\\
-{\bf Results.} Our results indicate that there is no simple rule governing
-the number of security bugs as a project evolves.
+b) other bug categories.
+Our findings indicate that there is no simple rule governing the number of
+security bugs as a project evolves.
 In particular, we cannot say that across projects security-related
@@
 Finally, even if bugs seem to have similar behaviour,
-severe security bugs seem to be unassociated with other bug categories.\\
-{\bf Conclusions.} Our findings indicate that further research should be done
-to analyze the evolution of security bugs. Given the fact that our experiment
-included only Java projects, similar research could be done for another
-ecosystem. Finally, the fact that projects have their own idiosyncrasies
-concerning security bugs, could help us find the common characteristics
-of the projects where security bugs increase over time.
+severe security bugs seem to be unassociated with other bug categories.
+\end{abstract}
+
+\begin{keywords}
+Security Bugs, Static Analysis, Software Evolution, Software
+Security, Maven, FindBugs.
+\end{keywords}
 
@@
 A security bug is a programming error that introduces a potentially exploitable
-weakness into a computer system~\cite{SSL12}. This
+weakness into a computer system~\cite{SSL12,TJBD11,M06}. This
 weakness could lead to a security breach with unfortunate consequences in
@@
 others. Despite the significant effort to detect and eliminate such
-bugs, little attention has been paid to study them in relation to
-software evolution~\cite{LRWPT97}. 
+bugs~\cite{SZ12}, little attention has been paid to study them in relation to
+software evolution~\cite{L96,LRWPT97,IB06,RGMA06}. 
 One of the most common approaches to identify security bugs is
@@
 
-In this paper we present how we used a large software ecosystem to analyse the
-relationship of different types of security vulnerabilities to 
-evolving software packages.
-For our research we used {\it FindBugs},\endnote{\url{http://findbugs.sourceforge.net/}}
+In this
+paper we present how we used a large software ecosystem to analyse how different
+types of security vulnerabilities are related to the evolving software packages.
+For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
 a static analysis tool that examines bytecode to detect software bugs and has already been used in
-research~\cite{AP10,HP07,SHP06}.
+research~\cite{AP10,HP07,HP04,HW08,SHP06}.
 Specifically, we ran FindBugs on all the project
 versions of all the projects that exist in the
-{\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
-(approximately 265{\sc gb} of data---see Section~\ref{sec:data}).
+{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
+(approximately 265GB of data---see Section~\ref{sec:data}).
 Then we observed the changes that involved the security bugs and their characteristics.
-%This research builds upon our earlier work on the topic~\cite{MGS12}.
+This research builds upon our earlier work on the topic~\cite{MGS12}.
 
@@
 they can cause significant financial damage to
-an organization~\cite{TH04,BCL08}. 
+an organization~\cite{TH04,BCL08,R06}. 
 Specifically,
@@
 knowing the that research has produced contradictory results on this
-issue~\cite{SYTP85,NBZ06,GKMS00}.
+issue~\cite{BP84,SYTP85,NBZ06,GKMS00}.
 Finally, we examined the Maven ecosystem as a whole from a security
-perspective. Its structure gave us the opportunity to see if a project version that is a dependency of
-a large number of others contains a low rate of security bugs.
+perspective. Its structure gave us the opportunity to see if a project version that is a dependency to
+a large number of others contains a low rate of security bugs~\cite{MW10}.
 %In this case we can strengthen the relationship between Linus' Law and
@@
 In the rest of this paper we
-outline related work (Section \ref{sec:rel}),
 describe the processing of our data and our experiment (Section \ref{sec:meth}),
 present and discuss the results we obtained (Section \ref{sec:res}),
+outline related work (Section \ref{sec:rel}),
 and end up with a conclusion and directions for future work (Section \ref{sec:con}).
-
-\section{Related Work}
-\label{sec:rel}
-
-There are numerous methods for mining software repositories in the context
-of software evolution~\cite{KCM07}. In this section we focus on the ones
-that highlight the relationship between software bugs and evolution and try to
-extract useful conclusions.
-
-{\it Refactoring identification} through software evolution is an approach used to
-relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
-ratio of refactorings is usually followed by an increasing ratio of bug
-reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
-after an incomplete refactoring~\cite{GW05}.
-Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
-refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
-refactorings aid bug fixes.
-
-{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
-detect bug-prone patterns among source code. Micro patterns describe programming
-idioms like inheritance, data management, immutability and others. The approach
-involved the examination of all revisions of three open-source projects to extract bug
-introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
-prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
-pattern prevalence tends to be the same in software collections.
-
-{\it Querying techniques} are used to answer a broad range of questions
-regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
-al.~\cite{BN11,B11} proposed a framework that is based on
-recursively enumerable languages. The framework can correlate software
-bugs with developers in various ways. For instance, return the list of
-bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
-an approach for populating a release history database that combines code
-information with bug tracking data. In this way, a developer can couple files
-that contain common bugs, estimate code maturity with respect to the bugs,
-etc. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
-framework that integrates information about the Debian project from various
-sources to answer queries related to software bugs and source code.
-
-D'Ambros et al. have used {\it bug history analysis} to detect
-the critical components of a project~\cite{D08}. This is done by using an
-evolutionary meta-model~\cite{DL08}. The same approach was
-also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
-of bugs with software properties like code complexity, process quality and others
-and to predict future properties.
-
-The evolution of software artifacts has also been analysed to {\it reduce the false
-alarms} of the various static analysis tools. To achieve this, Spacco et
-al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
-former, they tried to pair sets of bugs between versions in order to find
-similar patterns. In the latter, they computed a signature for every bug. This
-signature contained elements like the name of the class where the bug was found,
-the method and others. Then they searched for similar signatures between
-versions. In their research they studied the evolution of 116 sequential
-builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
-high priority bugs are fixed over time. To improve the precision of bug
-detection, Kim et al.~\cite{KE07b} proposed a history-based warning
-prioritization algorithm by mining the history of bug-fixes of three
-different projects. Working towards the same direction, Heckman
-et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
-correlation algorithms and classification techniques to evaluate alert
-prioritization approaches.
-
-Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
-Specifically, they analysed the changes of Linux file-system patches to extract
-bug patterns and categorize bugs based on their impact. Their findings
-indicated that the number of file-system bugs does not die down over time. By
-categorizing bugs they also showed the frequency of specific bugs in specific
-components.
-
-Completing the above approaches, our work focuses on the subset of security bugs.
-Focusing on such bugs is not a new idea.
-Ozment and Schechter~\cite{OS06} examined the code base of the Open{\sc bsd}
-operating system to determine whether its security is increasing
-over time. In particular, they measured the rate at which new code
-has been introduced and the rate at which defects have been reported over
-a 7.5 year period and fifteen releases.
-Even though the authors present statistical evidence
-of a decrease in the rate at which vulnerabilities are being reported,
-defects seem to appear persistent for a period of at least 2.6 years.
-Massacci et al.~\cite{MNN11} observed
-the evolution of software defects by examining six major versions of Firefox.
-To achieve this they created a database schema that contained information
-coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
-list,\endnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
-Bugzilla entries and others. Their findings indicated that security bugs are
-persistent over time. They also showed that there are many web users that use
-old versions of Firefox, meaning that old attacks will continue to work.
-Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
-security bugs with performance bugs. This was also done by analysing the project's
-Bugzilla. Their research presented evidence that security bugs require more experienced developers
-to be fixed. In addition, they suggested that security bug fixes are more complex than the
-fixes of performance and other bugs.
-Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
-various features of the vulnerabilities that they considered critical. Such features
-were the functionality and the criticality of the defects. Their analysis
-included the observation of vulnerability disclosures, the behavior of
-hackers in releasing exploits for vulnerabilities, patching and others. In
-their findings they highlighted the most exploited defects and showed that
-the percentage of remotely exploitable vulnerabilities has gradually increased
-over the years. Finally, Edwards et al.~\cite{EC12} have recently conducted
-a study similar  to ours in which they have considered only four projects.
-Their results demonstrate that the number of exploitable bugs does not
-always improve with each new release and that the rate of discovery of
-exploitable bugs begins to drop three to five years after the
-initial release.
 
@@
 
-Our experiment involved the collection of the metric results of the
-FindBugs tool. Before and during the experiment, we performed a number
-of filters on the data coming from the Maven repository, for reasons
-that we will describe below.
+Our experiment involved the collection of the metric results of the FindBugs
+tool. Before and during the experiment, we performed a number of functional
+fits on the data coming from the Maven repository, for reasons that we will describe below.
 
@@
 \label{sec:exp}
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[scale=0.75]{figures/arch.pdf}
+  \end{center}
+  \caption{The Data Processing Architecture}
+  \label{fig:arch}
+\end{figure}
 
@@
 a number of {\it workers} (a custom Python script), a {\it task queue}
-mechanism (Rabbit{\sc mq}---version 3.0.1),
-a {\it data repository} (Mongo{\sc db}---version 2.2),
+mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
+a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
 and the {\it code repository}, which in our case it was
@@
 
-Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.
-It uses {\sc xml} to describe the software project being built, its dependencies
-on other external modules, the build order, and required plug-ins.
-To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven central repository,
-and stores them in a local cache. The repository can be updated with
-new projects and also with new versions of existing projects.
-
 First, we scanned the Maven repository for appropriate {\sc jar}s and created a
@@
 
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[scale=0.73]{figures/arch.pdf}
-  \end{center}
-  \caption{The data processing architecture.}
-  \label{fig:arch}
-\end{figure}
-
 \subsection{Data Provenance}
 \label{sec:data}
+
+Maven is a build automation tool used primarily for Java projects and it is
+hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
+To describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins Maven uses
+{\sc xml}. To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects.
 
@@
 {\it group id}, {\it artifact id} and {\it version}.
-
-FindBugs works by examining the compiled Java virtual
-machine bytecodes of the programs it checks, using the bytecode engineering
-library ({\sc bcel}).
-To detect a bug, FindBugs uses various formal methods like
-{\it control flow} and {\it data flow
-analysis}. It has also other detectors that employ {\it visitor patterns} over
-classes and methods by using {\it state machines} to reason about values stored
-in variables or on the stack.
 Since FindBugs analyses applications written in the Java
@@
 hosts projects from languages other than Java such as Scala, Groovy,
-Clojure, etc., we filtered out such projects by performing a series of checks in
+Clojure etc. we filtered out such projects by performing a series of checks in
 the repository data and metadata.
-
-In addition, we implemented a series of audits in the worker scripts that
-checked if the {\sc jar}s are valid in terms of implementation. For instance,
-for every {\sc jar} the worker checked if there were any {\it .class} files
-before invoking FindBugs. After the project filtering, we narrowed down
-our data set to 17,505 projects with 115,214 versions.
-Table~\ref{tbl:repository} summarises the data set information and
-provides the basic descriptive statistic measurements. The distribution of version
-count among the selected projects is presented in Figure~\ref{fig:version-count}.
-
-The statistical measurements presented in Table~\ref{tbl:repository}
-indicate that we have 17,505 projects and the data set's median is 3,
-which means that almost 50\% (8,753 projects) of the project
-population have 1 to 3 versions. In general, most projects have a few
-number of versions, there are some projects with ten versions and
-only a few with hundreds of versions. The maximum number of versions
-for a project is 338. The 3$^{rd}$ quartile measurement also indicated
-that 75\% (13,129) of the projects have a maximum of 8 versions.
 
@@
 \centering
-\caption{Descriptive statistics measurements for the Maven repository.}
+\caption{Descriptive Statistics Measurements for the Maven Repository}
 \label{tbl:repository}
@@
 
-\begin{figure}[t]
+In addition, we implemented a series of audits in the worker scripts that
+checked if the {\sc jar}s are valid in terms of implementation. For instance,
+for every {\sc jar} the worker checked if there were any {\it .class} files
+before invoking FindBugs. After the project filtering, we narrowed down
+our data set to 17,055 projects with 115,214 versions.
+Table~\ref{tbl:repository} summarises the data set information and
+provides the basic descriptive statistic measurements. The distribution of version
+count among the selected projects is presented in Figure \ref{fig:version-count}.
+
+\begin{figure*}[t]
 	\centering
-	\includegraphics[scale=0.37]{version_count.pdf}
-	\caption{Distribution of version count among project population.}
+	\includegraphics[scale=0.45]{version_count.pdf}
+	\caption{Distribution of Version Count Among Project Population}
 	\label{fig:version-count}
-\end{figure}
+\end{figure*}
+
+The statistical measurements presented in Table~\ref{tbl:repository}
+indicate that we have 17,505 projects and the data set's median is 3,
+which means that almost 50\% (8,753 projects) of the project
+population have 1 to 3 versions. In general, most projects have a few
+number of versions, there are some projects with ten versions and
+only a few with hundreds of versions. The maximum number of versions
+for a project is 338. The 3$^{rd}$ quartile measurement also indicated
+that 75\% (13,129) of the projects have a maximum of 8 versions.
 
@@
 A threat to the internal validity of our experiment could be the false alarms of the
-FindBugs tool~\cite{AP10, HP04}. False positives and negatives of static analysis tools and
+FindBugs tool. False positives and negatives of static analysis tools and
 how they can be reduced is an issue that has already been discussed in the literature
@@
 programming languages, ecosystems, and development cultures.
-In particular, a large class of security problems such as
-buffer overflows~\cite{K11} do not apply in our study since
-Java enforces bound checking at runtime.
 
@@
 
-Our findings can be analysed at two levels. First, we discuss some
-primary observations concerning the security bugs of the Maven repository as a whole.
-Then, we provide a comprehensive analysis of the results and highlight our key findings.
-
-\begin{table*}[t]
+\begin{table}[t]
 \centering
-\caption{Bug categorisation according to FindBugs.}
+\caption{Bug Categorisation According to FindBugs}
 \label{tbl:bug-cat}
-\begin{tabular}{l p{29em}}
+\begin{tabular}{l p{23em}}
 \hline
@@
 \end{tabular}
-\end{table*}
+\end{table}
+
+Our findings can be analysed at two levels. First, we discuss some
+primary observations concerning the security bugs of the Maven repository as a whole.
+Then, we provide a comprehensive analysis of the results and highlight our key findings.
 
@@
 
-Our first results involve the most popular bugs in the Maven repository.
-Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
-repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
-security bugs (the sum of the {\it Security} and {\it Malicious Code}
-categories - 0.21\% + 21.81\%) are the most popular in the repository ($\geq 21\%$ each).
-This could be a strong indication that programmers write code
-that implements the required functionality without considering its many
-security aspects; an issue that has already been reported in
-literature~\cite{SH09}.
-% An interesting observation is that 4,908 projects did not
-% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
-% This goes along with the relationship between the size of an artifact and it's
-% bugs that is presented in the upcoming section.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[scale=0.35]{bug_percent}
-	\caption{Bug percentage in Maven repository.}
-	\label{fig:bug-per} 
-\end{figure}
-
-Another observation involves bugs that we could call {\it
-Security High} and they are a subset of the {\it Security} category.
-Such bugs are related to vulnerabilities that appear due to the lack of user-input
-validation and can lead to damaging attacks like {\sc sql} injection and
-Cross-Site Scripting~\cite{RL12}.
-To exploit such vulnerabilities, a malicious user does
-not have to know anything about the application internals.
-For almost all the other security bugs (coming from
-the {\it Malicious Code} category and the rest of
-the {\it Security} category bugs),
-another program should be written to incorporate references to
-mutable objects, access non-final fields, etc.
-Also, as bug descriptions indicate,\endnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-if an application has bugs coming from the {\it Security High} category,
-it might have more vulnerabilities that FindBugs doesn't report.
-Table~\ref{tbl:severe} presents the number
-of releases where at least one of these bugs exists. In essence, 5,501 releases
-($\approx 4,77\% $), contained at
-least one severe security bug. Given the fact that other projects include these
-versions as their dependencies, they are automatically rendered vulnerable if
-they use the code fragments that include the defects.
-The remaining bugs of the {\it Security} category
-are grouped together with the bugs of the {\it Malicious Code} category
-in another subcategory that we call {\it Security Low}.
-This category contains for the most part, bugs
-that imply violations of good {\sc oop} (object-oriented programming)
-design (i.e. keeping variables private to classes and others).
-The above categorization was done specifically to point out the
-behaviour of bugs that currently top the corresponding lists of most
-security providers.\endnote{\url{http://cwe.mitre.org/top25/index.html}}
-
 \begin{table*}[t]
 \centering
-\caption{Number of project releases that contain at least one ``Security
-  High" bug.}
-\label{tbl:severe}
+\caption{Number of Project Releases that Contain at Least One Severe Security Bug}
+\label{tbl:sev}
 \leavevmode
-	\begin{tabular}{p{31em} r}
+	\begin{tabular}{p{24em} r}
 	\hline
@@
 
-{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow''.
-In a context like this, we expect that
-the project versions that are dependencies to many other projects
-would have a small number of security
-bugs. To examine this variation of the Linus's Law and highlight the
+Our first results involve the most popular bugs in the Maven repository.
+Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
+repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
+security bugs (the sum of the {\it Security} and {\it Malicious Code}
+categories) are the most popular in the repository ($\geq 21\%$ each).
+This could be a strong indication that programmers write code
+that implements the required functionality without considering its many
+security aspects; an issue that has already been reported in
+literature~\cite{SH09}.
+% An interesting observation is that 4,908 projects did not
+% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
+% This goes along with the relationship between the size of an artifact and it's
+% bugs that is presented in the upcoming section.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[scale=0.45]{bug_percent}
+	\caption{Bug Percentage in Maven Repository}
+	\label{fig:bug-per} 
+\end{figure*}
+
+Another observation involves bugs that we could call {\it
+severe} and they are a subset of the {\it Security} category.
+Such bugs are related to vulnerabilities that appear due to the lack of user-input
+validation and can lead to damaging attacks like {\sc sql} injection~\cite{RL12} and
+Cross-Site Scripting~\cite{WS08}.
+Note that to exploit such vulnerabilities, a malicious user does
+not have to know anything about the application internals. For all the other
+bugs, another program should be written to incorporate references to
+mutable objects, access non-final fields, etc.
+Also, as bug descriptions indicate,\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+if an application has bugs coming from the {\it Security High} category,
+it might have more vulnerabilities that FindBugs doesn't report.
+Table~\ref{tbl:sev} presents the number
+of releases where at least one of these bugs exists. In essence, 5,501 releases
+($\approx 4,77\% $), contained at
+least one severe security bug. Given the fact that other projects include these
+versions as their dependencies, they are automatically rendered vulnerable if
+they use the code fragments that include the defects.
+In the following section
+we provide results separately for this subcategory which we call {\it Security High}.
+The remaining bugs of the {\it Security} category
+are grouped together with the bugs of the {\it Malicious Code} category
+in another subcategory that we call {\it Security Low}.
+
+{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow".
+To examine Linus's Law in relation to the rate of the
+security bugs~\cite{MW10}, and highlight the
 {\it domino effect}~\cite{TH04} we did the
@@
 Contrary to Linus's Law, thirty three of them contained bugs coming from the
-{\it Security Low} subcategory, while two of them contained {\it
-  Security High} bugs.
+{\it Security Low} subcategory, while two of them contained severe bugs.
 Twenty five of them were latest versions at the time. This also highlights
-the domino effect.
-%No matter how well a programmer secures a software component
-%it won't matter if he or she is using vulnerable code fragments coming
-%from another library.
+the domino effect. No matter how well a programmer secures a software component
+it won't matter if he or she is using vulnerable code fragments coming
+from another library.
 
@@
 \subsubsection{How Security Bugs Evolve Over Time}
+
+\begin{table}[t]
+    \centering
+    \caption{Correlations between Version and Defects Count}
+    \label{tbl:bugsperversion}
+    \input{bugsperversion.tex}
+\end{table}
 
@@
 
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{bugsversionscorr}
+  \caption{Histograms of correlations between bug counts and version
+    ordinals per project. In brackets the total population size and
+    the number of no correlation instances.}
+  \label{fig:bugsversionscorr}
+\end{figure*}
+
 Overall, Table~\ref{tbl:bugsperversion} and
@@
 of defects; this may be the result of doing and undoing a pervasive
-code change that runs foul of some bug identification rule.
+code change that falls foul of some bug identification rule.
 
-\begin{table}[tphp]
+\begin{figure*}[t]
   \centering
-    \caption{Correlations between version and defects count.}
-    \label{tbl:bugsperversion}
-    \input{bugsperversion.tex}
-\end{table}
-
-\begin{figure*}[p]
-  \centering
-  \includegraphics[scale=0.30]{bugsversionscorr}
-  \caption{Histograms of correlations between bug counts and version
-    ordinals per project. In brackets the total population size and
-    the number of no correlation instances.}
-  \label{fig:bugsversionscorr}
-  \centering
-  \includegraphics[scale=0.35]{bugdiffs}
-  \caption{Changes in bug counts between versions.}
+  \includegraphics[width=\textwidth]{bugdiffs}
+  \caption{Histograms of the time, measure in versions, it takes for a bug to be closed. }
   \label{fig:bugdiffs}
@@
 bugs, and of security bugs in particular, we used as a persistence
-indicator the number of versions a bug remains open in a project. To
-``tag" a bug we created a bug identifier by using the type of the bug,
-the method name and the class name in which the bug was found in. We
-chose not to use the line number of the location of the bug since it
-could change from version to version and after a possible code
-refactoring. We grouped the persistence numbers by bug categories and
-then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
-category pairs. The results are presented in
-Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
-brackets show pairs where no statistically significant difference was
-found.
+indicator the number of versions a bug remains open in a project. We
+grouped the persistence numbers by bug categories and then performed a
+Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
+presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
+pairs where no statistically significant difference was found.
 
 In general, although the average number of versions bugs in different
-bug categories that remained open was statistically different in many
+bug categories remained opened was statistically different in many
 cases, the difference is not spectacular. \textbf{In all cases a bug persists
@@
 
-\subsubsection{The Relation of Defects with the size of a JAR}
+\begin{landscape}
+  \begin{table}
+    \setlength{\extrarowheight}{0.10cm}
+    \caption{Bug Persistence Comparison}
+    \label{tbl:bug_persistence}
+    \resizebox{0.95\columnwidth}{!}{
+    \input{bug_persistence.tex}}\\
+    The matrix presents pairwise Mann-Whitney $U$ test results
+    between the different bug categories. Each cell contains the test
+    result (the value of $U$), the $p$-value, the average for each
+    category and the sample size for each category. Cells in brackets show
+    pairs where no statistically significant difference was found.
+  \end{table}
+\end{landscape}
+
+\subsubsection{The Relation of Defects with the size of a {\sc jar}}
 
@@
 effect than the other categories}, even {\it Security Low} that nearly
-tops the list. As we mentioned earlier, bugs that belong to the
-{\it Security High} category are related to
-user-input validation issues. Hence, even if a programmer adds
-code to a new version, if this code does not require user
-input, the possibility of such bug is minimal. 
-% dds proposed the following:
-%Given that, we could say that it would be productive to search for and fix
-%security bugs even if a project grows bigger.
+tops the list.
 
-\begin{table}[hbt]
+\begin{table}[t]
     \centering
-    \caption{Correlations between {\sc jar} size and defects count.}
+    \caption{Correlations between {\sc jar} size and Defects Count}
     \label{tbl:jarsizecorr}
@@
 
-\subsubsection{Security Bugs VS Other Bug Categories}
+\subsubsection{Security Bugs {\sc vs} Other Bug Categories}
 
@@
 number of distinct bugs that appeared in a project throughout its
-lifetime, see Figure~\ref{fig:corrplot}. We found significant, but not always
+lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
+Figure~\ref{fig:corrplot}. We found significant, but not always
 strong, correlations between all pairs. In general, the {\it Security
@@
 associated with other bugs, or only weakly so. Perhaps it takes a
-special kind of blunder to make it a security hazard. Thus, to find such
-defects, code reviewers with experience in software security
-issues might be needed.
+special kind of blunder to make it a security hazard.
 
-%\begin{table*}[t]
-%    \centering
-%    \caption{Correlation matrix}
-%    \label{tbl:corrmatrix}
-%    \input{corrmatrix.tex}
-%    \\
-%    \small The matrix presents pairwise correlations between the
-%        different bug categories.
-%\end{table*}
+\begin{table}[t]
+    \centering
+    \caption{Correlation matrix}
+    \label{tbl:corrmatrix}
+    \input{corrmatrix.tex}
+    \\
+    \small The matrix presents pairwise correlations between the
+        different bug categories.
+\end{table}
 
-\begin{figure}[t]
+\begin{figure*}[t]
   \centering
-  \includegraphics[scale=0.43]{corrplot.pdf}
-  \caption{Correlation matrix plot for bug categories.}
+  \includegraphics[scale=0.6]{corrplot.pdf}
+  \caption{Correlation matrix plot for bug categories}
   \label{fig:corrplot}
-\end{figure}
+\end{figure*}
+
+\section{Related Work}
+\label{sec:rel}
+
+There are numerous methods for mining software repositories in the context
+of software evolution~\cite{KCM07}. In this section we focus on the ones
+that highlight the relationship between software bugs and evolution and try to
+extract useful conclusions. The key idea behind this is
+similar to ours: the combination of information like bug descriptions,
+documentation and others with the information retrieved from either the source
+or object code of a project version.
+
+{\it Refactoring identification} through software evolution is an approach used to
+relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
+ratio of refactorings is usually followed by an increasing ratio of bug
+reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
+after an incomplete refactoring~\cite{GW05}.
+Ratzinger et al.~\cite{RSG08} showed that the number of bugs decreases, when the number of
+refactorings increases. Finally, Kim M. et al.~\cite{KCK11} indicated that {\sc api}-level
+refactorings aid bug fixes.
+
+{\it Micro patterns}, proposed by Kim et al.~\cite{KPW06}
+detect bug-prone patterns among source code. Micro patterns describe programming
+idioms like inheritance, data management, immutability and others. The approach
+involves the examination of all revisions of three open-source projects to extract bug
+introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
+prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
+pattern prevalence tends to be the same in software collections.
+
+{\it Querying techniques} are used to answer a broad range of questions
+regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
+al.~\cite{BN11,B11} proposed a framework that is based upon
+recursively enumerable languages. The framework can correlate software
+bugs with developers in various ways. For instance, return the list of
+bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
+an approach for populating a release history database that combines code
+information with bug tracking data. In this way, a developer can couple files
+that contain common bugs, estimate code maturity with respect to the bugs
+and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
+framework that integrates information about the Debian project from various
+sources to answer queries related to software bugs and source code.
+
+D'Ambros et al. have used {\it bug history analysis} to detect
+the critical components of a project~\cite{D08}. This is done by using an
+evolutionary meta-model~\cite{DL08}. The same approach was
+also used by Zimmermann et al.~\cite{ZNA08} to check the correlation
+of bugs with software properties like code complexity, process quality and others
+and predict future properties.
+
+The evolution of software artifacts has also been analysed to {\it reduce the false
+alarms} of the various static analysis tools. To achieve this, Spacco et
+al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
+former, they tried to pair sets of bugs between versions in order to find
+similar patterns. In the latter, they computed a signature for every bug. This
+signature contained elements like the name of the class where the bug was found,
+the method and others. Then they searched for similar signatures between
+versions. In their research they also studied the evolution of 116 sequential
+builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
+high priority bugs are fixed over time. To improve the precision of bug
+detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
+prioritization algorithm by mining the history of bug-fixes of three
+different projects. The algorithm was based on the following hypothesis: if a
+bug that belongs to a specific category is eliminated by a code change, then
+this warning category is important. Working towards the same direction, Heckman
+et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
+correlation algorithms and classification techniques to evaluate alert
+prioritization approaches.
+
+Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
+Specifically, they analysed the changes of Linux file-system patches to extract
+bug patterns and categorize bugs based on their impact. Their findings
+indicated that the number of file-system bugs does not die down over time. By
+categorizing bugs they also showed the frequency of specific bugs in specific
+components.
+
+Completing the above approaches, our work focuses on the subset of security bugs.
+Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
+the evolution of software defects by examining six major versions of Firefox.
+To achieve this they created a database schema that contained information
+coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
+list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
+Bugzilla entries and others. Their findings indicated that security bugs are
+persistent over time. They also showed that there are many web users that use
+old versions of Firefox, meaning that old attacks will continue to work.
+Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
+security bugs with performance bugs. This was also done by analysing the project's
+Bugzilla. Their research presented evidence that security bugs require more experienced developers
+to be fixed. In addition, they suggested that security bug fixes are more complex than the
+fixes of performance and other bugs.
+Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
+various features of the vulnerabilities that they considered critical. Such features
+were the functionality and the criticality of the defects. Their analysis
+included the observation of vulnerability disclosures, the behavior of
+hackers in releasing exploits for vulnerabilities, patching and others. In
+their findings they highlighted the most exploited defects and showed that
+the percentage of remotely exploitable vulnerabilities has gradually increased
+over the years.
 
@@
 
-We analysed more than 260{\sc gb} of interdependent project versions to see
-how security bugs evolve over time, their persistence, their relation
-with other bug categories, and their relationship with size in terms
-of bytecode.\endnote{Our data and code are available online at:
-\url{https://github.com/bkarak/evol_security_publication_2012}}
+In this work we analyzed a large software repository to examine the
+behavior of security bugs. Specifically, we analysed more than 260GB
+of interdependent project versions to see how security bugs evolve
+over time, their persistence, their relation with other bug
+categories, and their relationship with size in terms of bytecode.
 
@@
 of the projects have three versions, is not a positive result especially in the
-case of the {\it Security High} bugs. Concerning the relation between
-severe security bugs and a project's size
-we showed that they are not proportionally related.
-Given that, we could say that it would be productive to search for and fix
-security bugs even if a project grows bigger.
-Furthermore, the pairwise correlations between all categories
-indicated that even though all the other
+case of the {\it Security High} bugs. Concerning the relation between severe security bugs and a project's size
+we showed that they are not proportionally related. Furthermore, the
+pairwise correlations between all categories indicated that even though all the other
 categories are related, severe bugs do not appear together with the other bugs.
@@
 
-Contrary to the approaches that examine versions
+Contrary to the approaches that examine all versions
 formed after every change that has been committed to the repository,
@@
 characteristics of the projects where security bugs increase over time?
-In addition, by examining source code repositories more closely we could see how
-different development styles (i.e. size of commits, number of developers)
-affect projects.
 
-By selecting an large ecosystem that includes applications written only
-in Java, we excluded by default measurements that involve vulnerabilities like
-the infamous buffer overflow defects~\cite{K11}. Still, by examining software
-artifacts with similar characteristics facilitates the formation of
-an experiment. Thus, future work on our approach could also involve
-the observation of other ecosystems, that serve different languages,
-in the same manner such as, Python's PyPY (Python Package Index),
-Perl's {\sc cpan} (Comprehensive Perl Archive Network), and Ruby's
-RubyGems.
+Future work on our approach could also involve the observation of other ecosystems, that
+serve different languages, in the same manner such as, Python's PyPY
+(Python Package Index),\footnote{\url{https://pypi.python.org/pypi}}
+Perl's {\sc cpan} (Comprehensive Perl Archive Network),\footnote{\url{http://www.cpan.org/}}
+and Ruby's RubyGems.\footnote{\url{http://rubygems.org/}}
 
-\section{Acknowledgments}
+Our data and code will be publicly available upon publication.
+
+\section*{Acknowledgements}
+
 This research has been co-financed by the European Union (European Social Fund
-- {\sc esf}) and Greek national funds through the Operational Program
-``Education and Lifelong Learning'' of the National Strategic Reference Framework -
+--– {\sc esf}) and Greek national funds through the Operational Program
+``Education and Lifelong Learning'' of the National Strategic Reference Framework –
 Research Funding Program: Heracleitus II. Investing in knowledge society
@@
 
-%The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
-%and national funds and is a part of the Operational Programme ``Competitiveness \&
-%Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).
+The project has been also co-financed by the European Regional Development Fund ({\sc erdf})
+and national funds and is a part of the Operational Programme ``Competitiveness \&
+Entrepreneurship" ({\sc opce} II), Measure ``{\sc cooperation}" (Action I).
 
-{\footnotesize \bibliographystyle{acm}
+\bibliographystyle{splncs}
 \bibliography{evol}
 
-\theendnotes
-
-\begin{landscape}
-  \begin{table}
-    \setlength{\extrarowheight}{0.10cm}
-    \caption{Bug persistence comparison.}
-    \label{tbl:bug_persistence}
-    \resizebox{0.95\columnwidth}{!}{
-    \input{bug_persistence.tex}}\\
-    The matrix presents pairwise Mann-Whitney $U$ test results
-    between the different bug categories. Each cell contains the test
-    result (the value of $U$), the $p$-value, the average for each
-    category and the sample size for each category. Cells in brackets show
-    pairs where no statistically significant difference was found.
-  \end{table}
-\end{landscape}
-
 \end{document}

### 2013-12-16 analysis/examples/analyze.py

@@ -1,0 +1,58 @@
+import pymongo
+
+
+MONGO_HOST   = '83.212.106.194'
+MONGO_DB     = 'findbugs'
+MONGO_COL    = 'findbugs'
+MONGO_UNAME  = 'findbugs'
+MONGO_PASSWD = 'findbags'
+
+
+def get_mongo_db():
+    """
+    Gets a connection to MongoDB
+    """
+    conn = pymongo.Connection(host=MONGO_HOST, max_pool_size=10, network_timeout=1)
+    mongo_db = conn[MONGO_DB]
+    mongo_db.authenticate(MONGO_UNAME, MONGO_PASSWD)
+    
+    return mongo_db
+
+def record_exists(col_obj, group_id, artifact_id):
+    try:
+        q = {'JarMetadata.group_id' : group_id,
+             'JarMetadata.artifact_id' : artifact_id}
+
+        for c in col_obj.find(q, timeout=False):
+            print c['JarMetadata']['version']
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
+        return record_exists(col_obj, group_id, artifact_id)
+        
+def count_security_category_records(col_obj, skip=0):
+    counter = skip
+    try:     
+        q = {'BugCollection.BugInstance.category':'SECURITY'}
+        
+        for c in col_obj.find(q, timeout = False, skip=skip):
+            for bi in c['BugCollection']['BugInstance']:
+                if bi['category'] == 'SECURITY':                    
+                    counter += 1
+                    print counter
+            
+        print counter
+    except pymongo.errors.AutoReconnect, ae:
+        print 'Mongo Connection is Down. Reconnecting! (record_exists, %s)' % (ae,)
+        count_security_category_records(col_obj, skip=counter)
+                    
+
+def main():
+    mongo_db = get_mongo_db()
+    col = mongo_db[MONGO_COL]
+    count_security_category_records(col)
+    #record_exists(col, 'org.apache.geronimo.modules', 'geronimo-j2ee-builder')
+    
+    
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/bug_correlation.py

@@ -1,0 +1,97 @@
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file, load_evolution_projects_json
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_evolution_projects_json()
+    results = {}
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
+    total_projects = len(projects)
+    count = 0
+
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.Method.name', 'BugCollection.BugInstance.Field.name'])
+        doc_list = piter.documents_list()
+        proj_array_count = ArrayCount()
+        bug_list = []
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            for bi in d.get('BugCollection', {}).get('BugInstance', []):
+                if not isinstance(bi, dict):
+                    #print 'Invalid BugInstance (%s)' % (bi,)
+                    continue
+
+                bug_c = bi.get('category', '')
+                if bug_c == 'SECURITY':
+                    bug_type = bi.get('type', None)
+                    
+                    if bug_type is None:
+                        print 'Invalid Type!'
+                        continue
+                        
+                    if bug_type in security_bugs:
+                        bug_category = 'SECURITY_HIGH'
+                    else:
+                        bug_category = 'SECURITY_LOW'
[…]

### 2013-12-16 analysis/repo-statistics/bug_correlation_calc.R

@@ -1,0 +1,36 @@
+# Calculates pairwise correlations from the data in
+# data/bug_correlation_counters.csv, which is produced
+# by bug_correlation_tab.py
+
+library(ellipse)
+
+bug.counts <- read.csv("data/bug_correlation_counters.csv")
+
+bug.counts$SECURITY_HIGH <- bug.counts$SECURITY_HIGH + bug.counts$MALICIOUS_CODE
+
+bug.counts$MALICIOUS_CODE <- NULL
+
+bug.counts$TOTAL_MALICIOUS_CODE <- NULL
+bug.counts$TOTAL_SECURITY_HIGH <- NULL
+bug.counts$TOTAL_SECURITY_LOW <- NULL
+bug.counts$TOTAL_STYLE <- NULL
+bug.counts$TOTAL_BAD_PRACTICE <- NULL
+bug.counts$TOTAL_CORRECTNESS <- NULL
+bug.counts$TOTAL_MT_CORRECTNESS <- NULL
+bug.counts$TOTAL_PERFORMANCE <- NULL
+bug.counts$TOTAL_I18N <- NULL
+bug.counts$TOTAL_EXPERIMENTAL <- NULL
+
+for (i in (2:(ncol(bug.counts) - 1))) {
+  for (j in ((i + 1):(ncol(bug.counts) - 1))) {
+    print(paste(colnames(bug.counts)[i], ":", colnames(bug.counts[j])))
+    print(cor.test(bug.counts[, i], bug.counts[, j]))
+  }
+}
+
+ctab <- cor(bug.counts[,-1], method="pearson", use="pairwise.complete.obs")
+png('corrplot.png')
+colorfun <- colorRamp(c("#ff0000","white","#3366CC"), space="Lab")
+plotcorr(ctab, col=rgb(colorfun((ctab+1)/2), maxColorValue=255))
+dev.off()
+ctab

### 2013-12-16 analysis/repo-statistics/bug_correlation_calc.py

@@ -1,0 +1,92 @@
+# Calculates pairwise correlations from the data in
+# data/bug_correlation_counters.json
+
+import json
+import pandas as pd
+import numpy as np
+import scipy.stats as st
+from itertools import izip
+import sys
+import itertools
+from corrplot import corrplot
+
+bug_types = [
+    'SECURITY_HIGH',
+    'SECURITY_LOW',
+    'MALICIOUS_CODE',
+    'STYLE',
+    'BAD_PRACTICE',
+    'CORRECTNESS',
+    'MT_CORRECTNESS',
+    'PERFORMANCE',
+    'I18N',
+    'EXPERIMENTAL'
+    ]
+
+labels = []
+for bug_type in bug_types:
+    if bug_type == 'I18N':
+        labels.append(bug_type.lower())
+    elif bug_type == 'MT_CORRECTNESS':
+        labels.append('MT Correctness')
+    elif bug_type == 'MALICIOUS_CODE':
+        pass
+    else:
+        labels.append(bug_type.title().replace('_', ' '))
+
+with open("data/bug_correlation_counters.json") as infile:
+    json_input = json.load(infile)
+
+data = pd.DataFrame(json_input).T
+
+for bug_type in bug_types:
+    print bug_type, data[bug_type].count()
+
+print "MALICIUS_CODE & SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
+                                                * data['SECURITY_LOW'] > 0])
+    
+data['SECURITY_LOW'] = (data['MALICIOUS_CODE'].fillna(0)
+                        + data['SECURITY_LOW'].fillna(0)).replace(0, np.nan)
+data['TOTAL_SECURITY_LOW'] = (data['TOTAL_MALICIOUS_CODE'].fillna(0)
+                              + data['TOTAL_SECURITY_LOW'].fillna(0)
+                              ).replace(0, np.nan)
+data = data.drop(['MALICIOUS_CODE', 'TOTAL_MALICIOUS_CODE'], axis=1)
+bug_types.remove('MALICIOUS_CODE')
+
+num_bug_types = len(bug_types)
+corrmatrix = np.identity(num_bug_types)
+pvalues = np.zeros([num_bug_types, num_bug_types])
+
+for i in xrange(num_bug_types):
+    for j in xrange(i + 1, num_bug_types):
+        icolumn = bug_types[i]
+        jcolumn = bug_types[j]
[…]

### 2013-12-16 analysis/repo-statistics/bug_correlation_counters_full.py

@@ -1,0 +1,97 @@
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file, load_projects_json
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_projects_json()
+    results = {}
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
+    total_projects = len(projects)
+    count = 0
+
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.Method.name', 'BugCollection.BugInstance.Field.name'])
+        doc_list = piter.documents_list()
+        proj_array_count = ArrayCount()
+        bug_list = []
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            for bi in d.get('BugCollection', {}).get('BugInstance', []):
+                if not isinstance(bi, dict):
+                    #print 'Invalid BugInstance (%s)' % (bi,)
+                    continue
+
+                bug_c = bi.get('category', '')
+                if bug_c == 'SECURITY':
+                    bug_type = bi.get('type', None)
+                    
+                    if bug_type is None:
+                        print 'Invalid Type!'
+                        continue
+                        
+                    if bug_type in security_bugs:
+                        bug_category = 'SECURITY_HIGH'
+                    else:
+                        bug_category = 'SECURITY_LOW'
+                else:
[…]

### 2013-12-16 analysis/repo-statistics/bug_correlation_tab.py

@@ -1,0 +1,44 @@
+# Extracts the bug correlation data from the JSON representation
+# and outputs them in CSV format so that it can be read by R.
+
+import ijson
+import sys
+import csv
+
+bug_types = set()
+
+def get_bug_type(prefix):
+    return prefix[prefix.rfind(".") + 1:]
+
+with open("data/bug_correlation_counters.json", "r") as json_input:
+    parser = ijson.parse(json_input)
+    for prefix, event, value in parser:
+        if (event == 'number'):
+            bug_types.add(get_bug_type(prefix))
+
+with open("data/bug_correlation_counters.json", "r") as json_input, \
+        open("data/bug_correlation_counters.csv", "w") as csv_output:
+    csvwriter = csv.writer(csv_output)
+    parser = ijson.parse(json_input)
+    project_counts = {}
+    project_key = ""
+    row = ['project']
+    for bug_type in bug_types:
+        row.append(bug_type)
+    csvwriter.writerow(row)
+    for prefix, event, value in parser:
+        if (event == 'start_map'):
+            if prefix == '':
+                continue
+            project_key = prefix
+        if (event == 'number'):
+            project_counts[get_bug_type(prefix)] = value
+        if (event == 'end_map'):
+            row = [project_key]
+            for bug_type in bug_types:
+                bug_count = project_counts[bug_type] if bug_type in project_counts else 'NA'
+                row.append(bug_count)
+            csvwriter.writerow(row)
+            project_counts = {}
+            project_key = ""
+            

### 2013-12-16 analysis/repo-statistics/bug_persistence_calc.py

@@ -1,0 +1,147 @@
+# Calculates the bug persistence statistics
+
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+import collections
+
+bug_types_closed = collections.OrderedDict()
+bug_types_closed['SECURITY_HIGH'] = []
+bug_types_closed['SECURITY_LOW'] = []
+bug_types_closed['STYLE'] =  []
+bug_types_closed['CORRECTNESS'] = []
+bug_types_closed['BAD_PRACTICE'] = []
+bug_types_closed['MT_CORRECTNESS'] = []
+bug_types_closed['I18N'] =  []
+bug_types_closed['PERFORMANCE'] = []
+bug_types_closed['EXPERIMENTAL'] = []
+
+bug_labels = [
+    'Security High',
+    'Security Low',
+    'Style',
+    'Correctness',
+    'Bad Practice',
+    'MT Correctness',
+    'i18n',
+    'Performance',
+    'Experimental'
+]
+
+projects_closed = set()
+
+with open("data/bug_persistence.json", "r") as json_file:
+    json_input = json.load(json_file, object_pairs_hook=collections.OrderedDict)
+    bugs_opened = {}
+    prev_project = ''
+    for project_version, data in json_input.iteritems():
+        project = project_version.rpartition('||')[0]
+        if project != prev_project:
+            bugs_opened = {}
+            projects_closed.add(prev_project)
+            if project in projects_closed:
+                print project, "met again!"
+            prev_project = project
+        version_order = data.get('version_order', 0)
+        #print project_version, version_order
+        if version_order == 0:
+            continue
+        bugs = data['Bugs']
+        for bug in bugs_opened.keys():
+            if bug not in bugs:
+                bug_type = bug.partition('||')[0]
+                if bug_type == 'MALICIOUS_CODE':
+                    bug_type = 'SECURITY_LOW'
+                diff = version_order - bugs_opened[bug]
+                bug_types_closed[bug_type].append(diff)
+                if diff < 1:
+                    print (project, bug_type, diff, version_order,
+                           bugs_opened[bug])
+                del bugs_opened[bug]
+        for bug in bugs:
+            if bug == 'MALICIOUS_CODE':
+                bug = 'SECURITY_LOW'
+            if bug not in bugs_opened:
+                bugs_opened[bug] = version_order
+
+bug_type_arrays = []
+bug_type_desc = []
+
[…]

### 2013-12-16 analysis/repo-statistics/build_dep_graph.py

@@ -1,0 +1,50 @@
+import json
+
+from helpers.mongo_helper import MongoDocumentIterator
+from helpers.data_helper import save_to_file
+
+#
+# This script generates the "data/project_versions.json", which is a json dict (object)
+# with the following structure {<group_id>||<artifact_id> : version_count}
+#
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+def main():
+    results = {}
+    miter = MongoDocumentIterator(fields=['JarMetadata'])
+
+    print 'Found %d Documents' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        try:
+            if d is not None:
+                print 'Working %d of %d' % (miter.count(), miter.total(),)
+                node_key = '%s||%s||%s' % (d['JarMetadata']['group_id'], d['JarMetadata']['artifact_id'], d['JarMetadata']['version'])
+                deps = []
+
+                for dep in d.get('JarMetadata', {}).get('dependencies', {}):
+                    if isinstance(dep, dict):
+                        dep_group_id = dep.get('groupId', None)
+                        dep_artifact_id = dep.get('artifactId', None)
+                        dep_version = dep.get('version', None)
+
+                        if dep_group_id is None or dep_artifact_id is None:
+                            continue
+
+                        if dep_version is None:
+                            deps.append('%s||%s' % (dep_group_id, dep_artifact_id))
+                        else:
+                            deps.append('%s||%s||%s' % (dep_group_id, dep_artifact_id, dep_version))
+
+                results[node_key] = {'dependencies ' : deps, 'timestamp' : d['JarMetadata'].get('jar_last_modification_date', 0), 'version_order' : d['JarMetadata']['version_order']}
+        except Exception, e:
+            print d
+
+    save_to_file('project_graph.json', json.dumps(results))
+
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/check_duplicates.py

@@ -1,0 +1,36 @@
+import json
+from helpers.data_helper import ArrayCount, save_to_file
+from helpers.mongo_helper import MongoDocumentIterator
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+
+def main():
+    versions = []
+    dup_versions = ArrayCount()
+    miter = MongoDocumentIterator(fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version'])
+
+    print 'Found %d Documents' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        if d is not None:
+            group_id = d['JarMetadata']['group_id']
+            artifact_id = d['JarMetadata']['artifact_id']
+            version = d['JarMetadata']['version']
+            ga = '%s||%s||%s' % (group_id, artifact_id, version)
+
+            if ga not in versions:
+                versions.append(ga)
+            else:
+                dup_versions.incr(ga)
+
+            print '[%d:%d:%d]: Processed %s' % (dup_versions.item_count(), len(versions), miter.count(), ga)
+
+    print 'Total documents: %d, dups: %d, versions: %d' % (miter.total(), dup_versions.item_count(), len(versions))
+    save_to_file('duplicates.json', json.dumps(dup_versions.get_series()))
+
+if __name__ == "__main__":
+    main()
+

### 2013-12-16 analysis/repo-statistics/check_missing.py

@@ -1,0 +1,63 @@
+import xmldict
+import httplib
+
+from urllib2 import urlopen
+
+from helpers.mongo_helper import get_version, get_mongo_connection, MONGO_COL
+
+def url_exists(base_url, path):
+    conn = httplib.HTTPConnection(base_url)
+    conn.request('HEAD', path)
+    response = conn.getresponse()
+    conn.close()
+    return response.status == 200
+
+
+def main():
+    base_url = 'http://mirrors.ibiblio.org/maven2'
+    col_obj = get_mongo_connection()[MONGO_COL]
+    fp = open('data/missing_versions.txt', 'r')
+
+    total_jars = 0
+    missing = 0
+    really_missing = 0
+
+    for line in fp:
+        (group_id, artifact_id) = line.strip().split('||')
+        maven_base_url = '%s/%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
+        maven_metadata_name = '%smaven-metadata.xml' % (maven_base_url,)
+
+        try:
+            fp = urlopen(maven_metadata_name)
+            json_xml = xmldict.parse(fp.read())
+            versions = json_xml.get('metadata', {}).get('versioning', {}).get('versions', {}).get('version')
+            version_list = []
+
+            if isinstance(versions, list):
+                version_list.extend(versions)
+            else:
+                version_list.append(versions)
+
+            for v in version_list:
+                docs = get_version(col_obj, group_id, artifact_id, v)
+                total_jars += 1
+
+                if len(docs) == 0:
+                    missing += 1
+                    print '[%d]: Missing %s||%s||%s' % (total_jars, group_id, artifact_id, v)
+                    url_jar_path = '/maven2/%s/%s/%s/%s-%s.jar' % (group_id.replace('.', '/'), artifact_id, v, artifact_id, v)
+
+                    if not url_exists('mirrors.ibiblio.org', url_jar_path):
+                        really_missing += 1
+                        print '%s%s' % ('mirrors.ibiblio.org', url_jar_path)
+        except Exception, e:
+            print '[%d] ERROR: %s (%s)' % (total_jars, maven_metadata_name, e)
+            continue
+
+    fp.close()
+
+    print 'Total: %d, Missing: %d (%d)' % (total_jars, missing - really_missing, missing)
+
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/corrplot.py

@@ -1,0 +1,97 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from matplotlib.patches import Ellipse
+import string
+
+def corrplot(data, pvalues, labels):
+    """Creates a correlation plot of the passed data.
+
+    The function returns the plot which can then be shown with
+    plot.show(), saved to a file with plot.savefig(), or manipulated
+    in any other standard matplotlib way.
+
+    data is the correlation matrix, a 2-D numpy array containing
+    the pairwise correlations between variables;
+
+    pvalues is a matrix containing the pvalue for each corresponding
+    correlation value; if none it is assumed to be the zero matrix
+
+    labels is an array containing the variable names
+    """
+
+    plt.figure(1)
+
+    column_labels = labels
+    row_labels = labels
+    
+    ax = plt.subplot(1, 1, 1, aspect='equal')
+
+    width, height = data.shape
+    num_cols, num_rows = width, height
+
+    if pvalues is None:
+        pvalues = np.zeros([num_rows, num_cols])
+        
+    shrink = 0.9
+
+    poscm = cm.get_cmap('Blues')
+    negcm = cm.get_cmap('Oranges')
+
+    for x in xrange(width):
+        for y in xrange(height):
+            d = data[x, y]
+            c = pvalues[x, y]
+            rotate = -45 if d > 0 else +45
+            clrmap = poscm if d >= 0 else negcm
+            d_abs = np.abs(d)
+            ellipse = Ellipse((x, y),
+                              width=1 * shrink,
+                              height=(shrink - d_abs*shrink),
+                              angle=rotate)
+            ellipse.set_edgecolor('black')
+            ellipse.set_facecolor(clrmap(d_abs))
+            if c > 0.05:
+                ellipse.set_linestyle('dotted')
+            ax.add_artist(ellipse)
+
+    ax.set_xlim(-1, num_cols)
+    ax.set_ylim(-1, num_rows)
+        
+    ax.xaxis.tick_top()
+    xtickslocs = np.arange(len(row_labels))
+    ax.set_xticks(xtickslocs)
+    ax.set_xticklabels(row_labels, rotation=30, fontsize='small', ha='left')
+
+    ax.invert_yaxis()
+    ytickslocs = np.arange(len(row_labels))
+    ax.set_yticks(ytickslocs)
+    ax.set_yticklabels(column_labels, fontsize='small')
+
+    return plt
+
+if __name__ == "__main__":
+    
[…]

### 2013-12-16 analysis/repo-statistics/count_bugless_projects.py

@@ -1,0 +1,33 @@
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file, load_projects_json
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_projects_json()
+    total_projects = len(projects)
+    count = 0
+    bugless_count = 0
+
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
+        doc_list = piter.documents_list()
+        proj_array_count = ArrayCount()
+        bug_list = []
+        count += 1
+
+        for d in doc_list:
+        	bug_instances = d.get('BugCollection', {}).get('BugInstance', [])
+        	if len(bug_instances) == 0:
+        		bugless_count += 1
+        		break
+
+        print '[%d:%d:%d] %s||%s: %d versions' % (count, total_projects, bugless_count, p.group_id(), p.artifact_id(), len(doc_list))
+
+    print "bugless: %d, total: %d" % (bugless_count, total)
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/create_category_totals.py

@@ -1,0 +1,31 @@
+import json
+from helpers.data_helper import ArrayCount
+
+
+def main():
+    fp = open('data/bug_correlation_counters_full.json', 'r')
+    json_corr = json.load(fp)
+    fp.close()
+
+    totals = ArrayCount()
+
+    for (k, v) in json_corr.iteritems():
+        if len(v) > 0:
+            for (key, value) in v.iteritems():
+                totals.incr(key, delta=value)
+
+    total = 0
+
+    for (k, v) in totals.get_series().iteritems():
+        if k.startswith('TOTAL_'):
+            total += v
+
+    print 'Total: %d' % (total,)
+
+    for (k, v) in totals.get_series().iteritems():
+        if k.startswith('TOTAL_'):
+            print '%s %.2f' % (k.replace('TOTAL_', '').title(), (float(v) / float(total))*100)
+
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/create_version_count_graph.py

@@ -1,0 +1,21 @@
+import StringIO
+from helpers.data_helper import load_projects_json, ArrayCount, save_to_file
+
+
+def main():
+    statistics = ArrayCount()
+
+    for p in load_projects_json():
+        statistics.incr(p.version_count())
+
+    strio = StringIO.StringIO()
+
+    for (k, v) in statistics.get_series().iteritems():
+        strio.write(str(k) + "," + str(v) + "\n")
+
+    save_to_file('version_count.dat', strio.getvalue())
+
+
+if __name__ == "__main__":
+    main()
+

### 2013-12-16 analysis/repo-statistics/find_projects.py

@@ -1,0 +1,33 @@
+import json
+
+from helpers.mongo_helper import MongoDocumentIterator
+from helpers.data_helper import ArrayCount, save_to_file
+
+#
+# This script generates the "data/project_versions.json", which is a json dict (object)
+# with the following structure {<group_id>||<artifact_id> : version_count}
+#
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+def main():
+    results = ArrayCount()
+    miter = MongoDocumentIterator(fields=['JarMetadata.group_id', 'JarMetadata.artifact_id'])
+
+    print 'Found %d Documents' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        if d is not None:
+            group_id = d['JarMetadata']['group_id']
+            artifact_id = d['JarMetadata']['artifact_id']
+            ga = '%s||%s' % (group_id, artifact_id)
+            results.incr(ga)
+            print 'Working %d of %d' % (miter.count(), miter.total(),)
+
+    save_to_file('project_versions.json', json.dumps(results.get_series()))
+
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/find_vulnerable_projects.py

@@ -1,0 +1,47 @@
+import json
+
+from helpers.data_helper import save_to_file
+from helpers.mongo_helper import MongoDocumentIterator
+
+
+def main():
+    project_list = []
+
+    miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'SECURITY'},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id'])
+
+    print 'Found %d documents with SECURITY bugs' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        if d is not None:
+            print '%d of %d (security)' % (miter.count(), miter.total())
+            group_id = d.get('JarMetadata', {}).get('group_id', 'NotSet')
+            artifact_id = d.get('JarMetadata', {}).get('artifact_id', 'NotSet')
+            project_key = '%s||%s' % (group_id, artifact_id)
+
+            if project_key not in project_list:
+                project_list.append(project_key)
+
+    miter = MongoDocumentIterator(query={'BugCollection.BugInstance.category':'MALICIOUS_CODE'},fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version','BugCollection.BugInstance.category', 'BugCollection.BugInstance.type'])
+
+    print 'Found %d documents with MALICIOUS_CODE bugs' % (miter.total(),)
+
+    while miter.has_next():
+        d = miter.next()
+
+        if d is not None:
+            print '%d of %d (malicious_code)' % (miter.count(), miter.total())
+            group_id = d.get('JarMetadata', {}).get('group_id', 'NotSet')
+            artifact_id = d.get('JarMetadata', {}).get('artifact_id', 'NotSet')
+            project_key = '%s||%s' % (group_id, artifact_id)
+            if project_key not in project_list:
+                project_list.append(project_key)
+
+    print "Total: %d Projects" % (len(project_list),)
+
+    save_to_file('vuln_projects.json', json.dumps(project_list))
+
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/get_persistence.py

@@ -1,0 +1,101 @@
+from collections import OrderedDict
+import json
+
+from helpers.data_helper import ArrayCount, save_to_file, load_evolution_projects_json
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_evolution_projects_json()
+    results = OrderedDict()
+    total_projects = len(projects)
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
+    count = 0
+
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.version_order', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.Method.name', 'BugCollection.BugInstance.Field.name'])
+        doc_list = piter.documents_list()
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            if d['JarMetadata']['version_order'] == 0:
+                continue
+
+            proj_array_count = ArrayCount()
+            signatures = []
+
+            for bi in d.get('BugCollection', {}).get('BugInstance', []):
+                if not isinstance(bi, dict):
+                    #print 'Invalid BugInstance (%s)' % (bi,)
+                    continue
+
+                bug_c = bi.get('category', '')
+                if bug_c == 'SECURITY':
+                    bug_type = bi.get('type', None)
+                    
+                    if bug_type is None:
+                        print 'Invalid Type!'
+                        continue
+                        
[…]

### 2013-12-16 analysis/repo-statistics/graph.rb

@@ -1,0 +1,124 @@
+#!/usr/bin/env ruby
+
+require 'json'
+require 'zlib'
+require 'pp'
+
+file = ARGV[0] || fail("No file to parse")
+
+STDERR.puts "Reading file #{file}"
+
+f = File.open(file)
+gz = Zlib::GzipReader.new(f).read
+js = JSON.parse(gz)
+
+STDERR.puts "Building graph"
+
+graph = js.map do |e|
+  e[1]['dependencies '].map do |d|
+    [e[0], d]
+  end
+end.flat_map { |i| i }
+
+STDERR.puts "Build graph - number of edges: #{graph.size}"
+STDERR.puts "Collecting all versions for all artifacts"
+all_versions = js.reduce(Hash.new { |hash, key| hash[key] = [] }) do |acc, e|
+  group, artifact, version = e[0].split(/\|\|/)
+
+  if e[1]['version_order'].nil?
+    STDERR.puts "Name: #{e[0]} no version order"
+  else
+    acc["#{group}.#{artifact}"] << [version, e[1]['version_order']]
+  end
+  acc
+end
+
+STDERR.puts "Computing the latest version for each artifact"
+latest_versions = all_versions.reduce(Hash.new {}) do |acc, e|
+  k = e[0]
+  v = e[1]
+  max_version = v.max { |a, b| a[1] <=> b[1] }
+  acc[k] = max_version[0]
+  acc
+end
+
+STDERR.puts "Resolving dependency versions"
+processed = resolved = not_found = 0
+graph = graph.reduce([]) do |acc, edge|
+  processed += 1
+  group, artifact, version = edge[1].split(/\|\|/)
+  name = "#{group}.#{artifact}"
+
+  if version.nil?
+    latest = latest_versions[name]
+
+    if latest.nil?
+      not_found += 1
+      acc
+    else
+      resolved += 1
+      acc << [edge[0], "#{group}||#{artifact}||#{latest}"]
+    end
+  else
+    version_exists = all_versions[name].find { |v| v[0] == version }.nil?
+    unless version_exists
+      acc << edge
+    else
+      #STDERR.puts "#{}"
+      not_found += 1
+      acc
+    end
+  end
+
+  STDERR.print "\rProcessed: #{processed}, resolved: #{resolved},",
+               " unresolved: #{not_found}, ",
+               "no resolution needed: #{processed - resolved - not_found}"
+  acc
+end
+
+STDERR.puts
[…]

### 2013-12-16 analysis/repo-statistics/helpers/mongo_helper.py

@@ -1,0 +1,187 @@
+import pymongo
+
+MONGO_HOST   = '127.0.0.1'
+MONGO_DB     = 'findbugs'
+MONGO_COL    = 'findbugs'
+MONGO_UNAME  = 'findbugs'
+MONGO_PASSWD = 'findbags'
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+
+class MongoDocumentIterator(object):
+    def __init__(self, query=None, fields=None):
+        super(MongoDocumentIterator, self).__init__()
+        self.__doc_count = 0
+        self.__total_count = 0
+        self.__connection = get_mongo_connection()
+        self.__collection = self.__connection[MONGO_COL]
+
+        if fields is None:
+            self.__fields = []
+        else:
+            self.__fields = fields
+
+        if query is None:
+            self.__query = {}
+        else:
+            self.__query = query
+
+        self.__count_documents()
+
+    def __count_documents(self):
+        try:
+            self.__total_count = self.__collection.find(self.__query, timeout=False).count()
+        except pymongo.errors.AutoReconnect, ar:
+            print '__count_documents() - %s (reconnecting)' % (ar,)
+
+    def reset(self):
+        self.__doc_count = 0
+
+
+    def has_next(self):
+        return self.__doc_count < self.__total_count
+
+    def next(self):
+        try:
+            d = None
+
+            for c in self.__collection.find(self.__query, skip=self.__doc_count, limit=1, fields=self.__fields):
+                d = c
+
+            self.__doc_count += 1
+
+            return d
+        except pymongo.errors.AutoReconnect, ar:
+            print 'next() - %s (reconnecting)' % (ar,)
+            return None
+
+    def total(self):
+        return self.__total_count
+
+    def count(self):
+        return self.__doc_count
+
+
+class MongoProjectIterator(MongoDocumentIterator):
+    def __init__(self, group_id, artifact_id, query=None, fields=None):
+        __q = {'JarMetadata.group_id': group_id,
+               'JarMetadata.artifact_id': artifact_id}
+
+        __f = ['JarMetadata.version_order']
+
+        if query is not None:
+            __q.update(query)
+
+        if fields is not None:
+            __f.extend(fields)
+
+        super(MongoProjectIterator, self).__init__(query=__q, fields=__f)
+        self.__evol_documents = []
+        self.__documents = []
+
+    def evolution_list(self):
[…]

### 2013-12-16 analysis/repo-statistics/maths/statistics.py

@@ -1,0 +1,90 @@
+#
+# Basic statistical measurements
+# includes:
+#
+#
+# * min, max range
+# * 1st, 2rd Quartile
+# * Median
+# * Arithmetic mean
+# * standard deviation
+# * z-test implementation to find outliers
+#
+
+import math
+
+
+# range
+def stat_range(input_data):
+    return stat_max(input_data) - stat_min(input_data)
+
+# maximum value
+def stat_max(input_data):
+    return max(input_data)
+
+# minimum value
+def stat_min(input_data):
+    return min(input_data)
+
+# third quartile
+def third_quartile(input_data):
+    _length = len(input_data)
+
+    if (3*_length) / 4 == 1:
+        return (3*_length) + 1
+
+    return 3*_length / 4
+
+# first quartile
+def first_quartile(input_data):
+    _length = len(input_data)
+
+    if _length % 4 == 1:
+        return (_length / 4) + 1
+
+    return _length / 4
+
+# median
+def median(input_data):
+    _length = len(input_data)
+
+    if _length % 2 == 1:
+        return (_length / 2) + 1
+
+    return _length / 2
+
+# arithmetic mean
+def mean(input_data):
+    _length = len(input_data)
+    _total = 0
+
+    for i in input_data:
+        _total = _total + i
+
+    return float(_total) / float(_length)
+
+# standard deviation
+def stddev(input_data):
+    _length = len(input_data)
+    _mean = mean(input_data)
+    _total = 0
+
+    for i in input_data:
+        _total += math.pow((i - _mean), 2)
+
+    _total = float(_total) / float(_length)
+
+    return math.sqrt(_total)
+
+
+def ztest(input_data):
+    _result = []
+    _mean = mean(input_data)
+    _stddev = stddev(input_data)
+
+    for i in input_data:
+        _z = float(math.fabs(float(i) - float(_mean))) / float(_stddev)
+        if _z < 3:
+            _result.append(i)
+
+    return _result

### 2013-12-16 analysis/repo-statistics/models/project.py

@@ -1,0 +1,34 @@
+
+
+class Project(object):
+    def __init__(self, group_id, artifact_id):
+        super(Project, self).__init__()
+        self.__group_id = group_id
+        self.__artifact_id = artifact_id
+        self.__version_count = 0
+
+    def group_id(self):
+        return self.__group_id
+
+    def artifact_id(self):
+        return self.__artifact_id
+
+    def key(self):
+        return '%s||%s' % (self.group_id, self.artifact_id())
+
+    def set_version_count(self, c):
+        self.__version_count = c
+
+    def version_count(self):
+        return self.__version_count
+
+    @staticmethod
+    def parse_project(project_key, version_count):
+        pk_arr = project_key.split('||')
+        prj_obj = Project(pk_arr[0].strip(), pk_arr[1].strip())
+        prj_obj.set_version_count(version_count)
+
+        return prj_obj
+
+
+

### 2013-12-16 analysis/repo-statistics/project_bugs_counts.py

@@ -1,0 +1,115 @@
+# Extracts the project counters data from the JSON representation
+# and calculates correlations between version numbers and number
+# of bugs.
+
+import json
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+import math
+import collections
+
+bugs_per_version = collections.OrderedDict()
+bugs_per_version['SECURITY_HIGH'] = []
+bugs_per_version['SECURITY_LOW'] = []
+bugs_per_version['STYLE'] =  []
+bugs_per_version['CORRECTNESS'] = []
+bugs_per_version['BAD_PRACTICE'] = []
+bugs_per_version['MT_CORRECTNESS'] = []
+bugs_per_version['I18N'] =  []
+bugs_per_version['PERFORMANCE'] = []
+bugs_per_version['EXPERIMENTAL'] = []
+
+bugs_per_version_labels = [
+    'Security High',
+    'Security Low',
+    'Style',
+    'Correctness',
+    'Bad Practice',
+    'MT Correctness',
+    'i18n',
+    'Performance',
+    'Experimental'
+]
+
+with open("data/project_counters.json", "r") as json_file:
+    json_input = json.load(json_file)
+    for project, data in json_input.iteritems():
+        for version in data['versions']:
+            version_order = version['JarMetadata']['version_order']
+            if version_order == 0:
+                continue
+            counters = version['Counters']
+            if 'MALICIOUS_CODE' in counters:
+                malicious_code = counters.pop('MALICIOUS_CODE')
+                if 'SECURITY_LOW' in counters:
+                    counters['SECURITY_LOW'] += malicious_code
+                else:
+                    counters['SECURITY_LOW'] = malicious_code
+            for counter in bugs_per_version.keys():
+                if counter in counters:
+                    value = counters[counter]
+                    bugs_per_version[counter].append((version_order, value))
+
+bug_counts_matrix = []
+                    
+for counter, counter_list in bugs_per_version.iteritems():
+    bugs_per_version_arr = np.array(counter_list).transpose()            
+    (rho, p_value) = st.spearmanr(bugs_per_version_arr[0],
+                                  bugs_per_version_arr[1])
+    print counter, rho, p_value
+    bug_counts_matrix.append([counter, rho, p_value])
+
[…]

### 2013-12-16 analysis/repo-statistics/project_counters.py

@@ -1,0 +1,91 @@
+import json
+
+from helpers.data_helper import load_vuln_projects_json, ArrayCount, save_to_file
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_vuln_projects_json()
+    results = {}
+    security_bugs = ['HRS_REQUEST_PARAMETER_TO_COOKIE',
+                     'HRS_REQUEST_PARAMETER_TO_HTTP_HEADER',
+                     'PT_ABSOLUTE_PATH_TRAVERSAL',
+                     'SQL_NONCONSTANT_STRING_PASSED_TO_EXECUTE',
+                     'SQL_PREPARED_STATEMENT_GENERATED_FROM_NONCONSTANT_STRING',
+                     'XSS_REQUEST_PARAMETER_TO_JSP_WRITER',
+                     'XSS_REQUEST_PARAMETER_TO_SEND_ERROR',
+                     'XSS_REQUEST_PARAMETER_TO_SERVLET_WRITER']
+
+    total_projects = len(projects)
+    count = 0
+    print 'Found %d Projects' % (total_projects,)
+
+    for p in projects:
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.group_id', 'JarMetadata.artifact_id', 'JarMetadata.version', 'JarMetadata.jar_size', 'JarMetadata.version_order', 'JarMetadata.jar_last_modification_date', 'BugCollection.BugInstance.category', 'BugCollection.BugInstance.type', 'BugCollection.BugInstance.Class.classname','BugCollection.BugInstance.priority'])
+        doc_list = piter.documents_list()
+        documents = []
+        count += 1
+
+        print '[%d:%d] %s||%s: %d versions' % (count, total_projects, p.group_id(), p.artifact_id(), len(doc_list))
+
+        for d in doc_list:
+            doc_results = {'JarMetadata': d['JarMetadata']}
+            doc_array_count = ArrayCount()
+            sec_instances = []
+
+            for bi in d.get('BugCollection', {}).get('BugInstance', []):
+                if not isinstance(bi, dict):
+                    print bi
+                    continue
+
+                bug_category = bi.get('category', '')
+
+                # method
+                if bug_category == 'SECURITY' or bug_category == 'MALICIOUS_CODE':
+                    classnames = bi['Class']
+                    classresults = []
+
+                    if isinstance(classnames, list):
+                        for c in classnames:
[…]

### 2013-12-16 analysis/repo-statistics/project_counters_diffs.py

@@ -1,0 +1,168 @@
+# Calculate various statistics on the diffs between bug type counts
+
+import json
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+import math
+from collections import defaultdict, OrderedDict
+import itertools
+
+bug_types = (
+    'SECURITY_HIGH',
+    'SECURITY_LOW',
+    'STYLE',
+    'CORRECTNESS',
+    'BAD_PRACTICE',
+    'MT_CORRECTNESS',
+    'I18N',
+    'PERFORMANCE',
+    'EXPERIMENTAL',
+)
+
+# the bug_types_diffs dict contains, for each bug type, a list of the
+# diffs for that bug type, for all projects
+bug_types_diffs = OrderedDict()
+for bug_type in bug_types:
+    bug_types_diffs[bug_type] = []
+
+bug_labels = {
+    'SECURITY_HIGH': 'Security High',
+    'SECURITY_LOW': 'Security Low',
+    'STYLE': 'Style',
+    'CORRECTNESS': 'Correctness',
+    'BAD_PRACTICE': 'Bad Practice',
+    'MT_CORRECTNESS': 'MT Correctness',
+    'I18N': 'i18n',
+    'PERFORMANCE': 'Performance',
+    'EXPERIMENTAL': 'Experimental'
+}
+
+# diffs is a dict with the projects as keys. The value for each key
+# is itself a dict with the various bug types as keys and a list of
+# their diffs as values.
+diffs = {}
+
+counts = {}
+
+counts_corrs = {}
+
+# get defect counts
+with open("data/project_counters.json", "r") as json_file:
+    json_input = json.load(json_file)
+    for project, data in json_input.iteritems():
+        counts[project] = []
+        bad_project = False
+        for version in data['versions']:
+            if bad_project == True:
+                break
+            version_order = version['JarMetadata']['version_order']
+            if version_order == 0:
+                bad_project = True
+                continue
+            counts[project].append({})
+            counters = version['Counters']
+            if 'MALICIOUS_CODE' in counters:
+                malicious_code = counters.pop('MALICIOUS_CODE')
+                if 'SECURITY_LOW' in counters:
+                    counters['SECURITY_LOW'] += malicious_code
+                else:
+                    counters['SECURITY_LOW'] = malicious_code
+            for counter, value in counters.iteritems():
+                if version_order != len(counts[project]):
+                    bad_project = True
[…]

### 2013-12-16 analysis/repo-statistics/project_counters_jarsize_calc.R

@@ -1,0 +1,8 @@
+jarsize.counts <- read.csv('data/project_counters_jarsize.csv',
+                           header=TRUE)
+
+for (i in names(jarsize.counts)[4:length(colnames(jarsize.counts))]) {
+  cor.result = cor.test(jarsize.counts$jarsize, jarsize.counts[[i]])
+  cor.result$data.name = paste("jarsize", "and", i)
+  print(cor.result)
+}

### 2013-12-16 analysis/repo-statistics/project_counters_jarsize_tab.py

@@ -1,0 +1,51 @@
+# Extracts the bug counters data from the JSON representation
+# and outputs them in CSV format so that it can be read by R.
+
+import ijson
+import json
+import sys
+import csv
+
+bug_types = [
+    'SECURITY_HIGH',
+    'SECURITY_LOW',
+    'STYLE',
+    'CORRECTNESS',
+    'BAD_PRACTICE',
+    'MT_CORRECTNESS',
+    'I18N',
+    'PERFORMANCE',
+    'EXPERIMENTAL',
+]
+
+with open("data/project_counters_jarsize.csv", "w") as csv_output:
+    csvwriter = csv.writer(csv_output)        
+    project_counts = {}
+    project_key = ""
+    row = ['project', 'version', 'jarsize']
+    for bug_type in bug_types:
+        row.append(bug_type)
+    csvwriter.writerow(row)
+    with open("data/project_counters.json", "r") as json_file:
+        json_input = json.load(json_file)
+        for project, data in json_input.iteritems():
+            for version in data['versions']:
+                meta_data = version['JarMetadata']                    
+                row = [project, meta_data['version_order'],
+                       meta_data['jar_size']]
+                counters = version['Counters']
+                counters = version['Counters']
+                if 'MALICIOUS_CODE' in counters:
+                    malicious_code = counters.pop('MALICIOUS_CODE')
+                    if 'SECURITY_LOW' in counters:
+                        counters['SECURITY_LOW'] += malicious_code
+                    else:
+                        counters['SECURITY_LOW'] = malicious_code
+                security_low = 0
+                for bug_type in bug_types:
+                    if bug_type in counters:
+                        row.append(counters[bug_type])
+                    else:
+                        row.append('NA')
+                csvwriter.writerow(row)
+            

### 2013-12-16 analysis/repo-statistics/repository_statistics.py

@@ -1,0 +1,28 @@
+from helpers.data_helper import load_projects_json
+
+from maths import statistics
+
+__author__ = 'Vassilios Karakoidas (vassilios.karakoidas@gmail.com)'
+
+
+def main():
+    project_list = load_projects_json()
+
+    project_count = len(project_list)
+    version_list = [x.version_count() for x in project_list]
+    version_count = sum(version_list)
+
+    version_list = sorted(version_list)
+
+    print "Projects: %d" % (project_count,)
+    print "Versions (total): %d" % (version_count,)
+    print "Max. Version Count: %d" % (statistics.stat_max(version_list),)
+    print "Min. Version Count: %d" % (statistics.stat_min(version_list),)
+    print "Mean: %.2f" % (statistics.mean(version_list))
+    print "Median: %d" % (version_list[statistics.median(version_list)])
+    print "Range: %d" % (statistics.stat_range(version_list))
+    print "1st Qrt: %d" % (version_list[statistics.first_quartile(version_list)])
+    print "3rd Qrt: %d" % (version_list[statistics.third_quartile(version_list)])
+
+if __name__ == "__main__":
+    main()

### 2013-12-16 analysis/repo-statistics/top_nodes_counters.py

@@ -1,0 +1,38 @@
+import csv
+import json
+
+def main():
+    with open("data/project_counters.json") as data_file:
+        data = json.load(data_file)
+
+    with open('data/graph-results.csv', 'rb') as f:
+        reader = csv.reader(f)
+        counter = 0
+        for row in reader:
+            counter = counter + 1
+            try:
+                (group_id,artifact,version) = row[0].split("||")
+                #print "%s %s %s" % (group_id,artifact,version)
+                #print row[1]
+                #print row[2]
+                #print row[3]
+        
+                my_key = ''.join([group_id,"||",artifact]) 
+                if my_key in data:
+                    #print data.get(my_key)
+                    #json_object = json.load(data.get(my_key))
+                    obj = data.get(my_key)
+                    for my_version in obj[u'versions']:
+                        if my_version[u'JarMetadata'][u'version'] == version:
+                            print "%s %s %s" % (group_id,artifact,version)
+                            print row[1]
+                            print row[2]
+                            print row[3]
+                            print my_version[u'Counters']
+            except:
+                pass
+            if counter == 50:
+                break
+            
+if __name__== "__main__":
+ main()

### 2013-12-16 test/convert-findbugs-xml/convert-test.py

@@ -1,0 +1,36 @@
+#!/usr/bin/env python
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+#   1. Redistributions of source code must retain the above copyright
+#      notice, this list of conditions and the following disclaimer.
+#
+#  2. Redistributions in binary form must reproduce the above copyright
+#     notice, this list of conditions and the following disclaimer in the
+#     documentation and/or other materials provided with the distribution.
+#
+# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
+# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
+# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+# SUCH DAMAGE.
+#
+#
+# Test Naive conversion of Findbugs XML to JSON (using the xmldict utility) 
+#
+# Authors:
+#    Vassilios Karakoidas (vassilios.karakoidas@gmail.com)
+
+import xmldict, json
+
+findbugs_xml = open('acegi-security-0.5.jar-findbugs.xml', 'r')
+
+print json.dumps(xmldict.parse(findbugs_xml)).replace('"@','"')

### 2013-12-16 test/convert-findbugs-xml/xmldict.py

@@ -1,0 +1,252 @@
+#!/usr/bin/env python
+"Makes working with XML feel like you are working with JSON"
+
+from xml.parsers import expat
+from xml.sax.saxutils import XMLGenerator
+from xml.sax.xmlreader import AttributesImpl
+try: # pragma no cover
+    from cStringIO import StringIO
+except ImportError: # pragma no cover
+    try:
+        from StringIO import StringIO
+    except ImportError:
+        from io import StringIO
+try: # pragma no cover
+    from collections import OrderedDict
+except ImportError: # pragma no cover
+    OrderedDict = dict
+
+try: # pragma no cover
+    _basestring = basestring
+except NameError: # pragma no cover
+    _basestring = str
+try: # pragma no cover
+    _unicode = unicode
+except NameError: # pragma no cover
+    _unicode = str
+
+__author__ = 'Martin Blech'
+__version__ = '0.3'
+__license__ = 'MIT'
+
+class ParsingInterrupted(Exception): pass
+
+class _DictSAXHandler(object):
+    def __init__(self,
+                 item_depth=0,
+                 item_callback=lambda *args: True,
+                 xml_attribs=True,
+                 attr_prefix='@',
+                 cdata_key='#text',
+                 force_cdata=False,
+                 cdata_separator='',
+                 postprocessor=None):
+        self.path = []
+        self.stack = []
+        self.data = None
+        self.item = None
+        self.item_depth = item_depth
+        self.xml_attribs = xml_attribs
+        self.item_callback = item_callback
+        self.attr_prefix = attr_prefix
+        self.cdata_key = cdata_key
+        self.force_cdata = force_cdata
+        self.cdata_separator = cdata_separator
+        self.postprocessor = postprocessor
+
+    def startElement(self, name, attrs):
+        self.path.append((name, attrs or None))
+        if len(self.path) > self.item_depth:
+            self.stack.append((self.item, self.data))
+            attrs = OrderedDict((self.attr_prefix+key, value)
+                for (key, value) in attrs.items())
+            self.item = self.xml_attribs and attrs or None
+            self.data = None
+
+    def endElement(self, name):
+        if len(self.path) == self.item_depth:
+            item = self.item
+            if item is None:
+                item = self.data
+            should_continue = self.item_callback(self.path, item)
+            if not should_continue:
+                raise ParsingInterrupted()
+        if len(self.stack):
+            item, data = self.item, self.data
[…]

### 2013-12-16 test/maven_test.sh

@@ -1,0 +1,56 @@
+#!/usr/bin/env python
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+#   1. Redistributions of source code must retain the above copyright
+#      notice, this list of conditions and the following disclaimer.
+#
+#  2. Redistributions in binary form must reproduce the above copyright
+#     notice, this list of conditions and the following disclaimer in the
+#     documentation and/or other materials provided with the distribution.
+#
+# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
+# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
+# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+# SUCH DAMAGE.
+#
+#
+# initial script to test findbugs time.
+# change the path of the repository accordingly.
+#
+# Authors:
+#    Vassilios Karakoidas (vassilios.karakoidas@gmail.com)
+#    Dimitrios Mitropoulos (dimitro@aueb.gr)
+#
+
+# configuration variables
+MAVEN_REPOSITORY=/Users/dimitro/Software/uk.maven.org/maven2
+MAVEN_FULL_JARS=maven-full-jars.text
+MAVEN_BINARIES=maven-binaries-jars.text
+
[…]

### 2013-12-16 workers/worker-findbugs/process-win.py

@@ -1,0 +1,456 @@
+#!/usr/bin/env python
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+#   1. Redistributions of source code must retain the above copyright
+#      notice, this list of conditions and the following disclaimer.
+#
+#  2. Redistributions in binary form must reproduce the above copyright
+#     notice, this list of conditions and the following disclaimer in the
+#     documentation and/or other materials provided with the distribution.
+#
+# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
+# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
+# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+# SUCH DAMAGE.
+
+""" Read URLs from an AMQP queue, download referenced JAR, process it with
+Findbugs, store the results to a MongoDB collection.
+
+"""
+import json, pika, sys, os, logging, pymongo, time, urllib
+
+from subprocess import Popen, PIPE, STDOUT
+from threading import Thread
+
+__author__ = 'Georgios Gousios <gousiosg@gmail.com>, Vassilios Karakoidas (vassilios.karakoidas@gmail.com), Dimitrios Mitropoulos (dimitro@aueb.gr)'
+
+
+RETRY_ATTEMPTS = 3
+
[…]

### 2014-01-19 docs/msr.tex
paper skeleton

\documentclass{sig-alternate}

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{color}

\begin{document}

\title{The Bug Catalog of the Maven Repository Ecosystem}

\numberofauthors{5}

\author{
% 1st. author
\alignauthor
Dimitris Mitropoulos\\
       \affaddr{Athens University of Economics and Business}\\
       \affaddr{Department of Management Science and Technology}\\
       \email{dimitro@aueb.gr}
% 2nd. author
\alignauthor Vassilios Karakoidas\\
       \affaddr{Athens University of Economics and Business}\\
       \affaddr{Department of Management Science and Technology}\\
       \email{bkarak@aueb.gr}
% 3rd. author
\alignauthor Panos Louridas\\
       \affaddr{Athens University of Economics and Business}\\
       \affaddr{Department of Management Science and Technology}\\
       \email{louridas@aueb.gr}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Georgios Gousios\\
       \affaddr{Delft University of Technology}\\
       \affaddr{Software Engineering Research Group}\\
       \email{G.Gousios@tudelft.nl}
% 5th. author
\alignauthor Diomidis Spinellis\\
       \affaddr{Athens University of Economics and Business}\\
       \affaddr{Department of Management Science and Technology}\\
       \email{dds@aueb.gr}
}

\maketitle
\begin{abstract}
The abstract is coming
\end{abstract}

\category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]
\category{D.2.5}{Software Engineering}{Testing and Debugging}[Code inspections and walk-throughs]
\category{D.2.7}{Software Engineering}{Distribution, Maintenance, and Enhancement}[Version control]

\terms{Static Analysis, Software Ecosystems}

\keywords{Maven Repository, FindBugs, Software Bugs}

\section{Introduction}
\label{sec:intro}
Intorduction.

\section{Data Collection Experiment}
\label{sec:exp}
Body.

\section{Repository Statistics}
\label{sec:repo}
Repo stats.

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.35]{figures/bug_percent}
	\caption{Bug percentage in Maven repository.}
	\label{fig:bug-per} 
\end{figure}

\section{Initial Findings}
\label{sec:find}
Findings.

\section{Tools}
\label{sec:exp}
Tools.

\section{Related Work}
\label{sec:rel}

\section{Conclusions}
\label{sec:conc}

\section{Acknowledgments}
possible acks.

\bibliographystyle{abbrv}
\bibliography{evol}  
\end{document}

### 2014-01-19 docs/msr.tex
adding content, minor structure changes

@@
 \label{sec:intro}
-Intorduction.
+
+In this paper we present a dataset produced after
+analyzing a large software ecosystem to detect
+software bugs. For our research we used
+{\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+a static analysis tool that examines bytecode to detect software bugs and has already been used in
+research~\cite{AP10,SHP06}.
+Specifically, we ran FindBugs on all the project
+versions of all the projects that exist in the
+{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
+(approximately 265{\sc gb} of data.
 
@@
 	\centering
-	\includegraphics[scale=0.35]{figures/bug_percent}
+	\includegraphics[scale=0.38]{figures/bug_percent}
 	\caption{Bug percentage in Maven repository.}
@@
 \bibliographystyle{abbrv}
-\bibliography{evol}  
+\bibliography{msr}  
 \end{document}

### 2014-01-19 docs/msr.tex
added abstract, more content in the introduction

--- 2014-01-19 docs/msr.tex
@@
 \begin{abstract}
-The abstract is coming
+Examining software ecosystems can provide the research community
+with useful information. To examine the Maven Central Repository
+(approximately 265{\sc gb} of data), we performed an experiment
+where we statically analyzed the repository to detect its software
+bugs. For our analysis we used FindBugs, a tool that
+examines Java bytecode to detect numerous types of bugs.
+In this paper, we present our data collection experiment
+and show how our dataset can be used to extract interesting
+findings on software evolution.
 \end{abstract}
@@
 \label{sec:intro}
-Intorduction.
+
+A software ecosystem can be seen as a collection of software projects,
+which are developed and co-evolve in the same environment~\cite{LL10}.
+Components can and be interdependent and have multiple versions.
+Examples of such ecosystems, are Python's {\sc p}y{\sc py} (Python Package Index),
+Perl's {\sc cpan} (Comprehensive Perl Archive Network), Ruby's RubyGems and the
+Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}
+
+Maven is a build automation tool used primarily for Java projects and it is
+hosted by the Apache Software Foundation.
+It uses {\sc xml} to describe the software project being built, its dependencies
+on other external modules, the build order, and required plug-ins.
+To build a software component, it dynamically downloads Java libraries
+and Maven plug-ins from the Maven central repository,
+and stores them in a local cache. The repository can be updated with
+new projects and also with new versions of existing projects
+that can depend on other versions.
 
@@
 
+Cite~\cite{RDV13}.
+
 \section{Conclusions}

### 2014-01-19 docs/msr.tex
intro draft ready

@@
 which are developed and co-evolve in the same environment~\cite{LL10}.
-Components can and be interdependent and have multiple versions.
-Examples of such ecosystems, are Python's {\sc p}y{\sc py} (Python Package Index),
-Perl's {\sc cpan} (Comprehensive Perl Archive Network), Ruby's RubyGems and the
-Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}
+Components can be interdependent and have multiple versions.
+Examples of such ecosystems include Python's
+{\sc p}y{\sc py}\footnote{\url{http://pypy.org/}}
+(Python Package Index), Perl's
+{\sc cpan}\footnote{\url{http://www.cpan.org/}}
+(Comprehensive Perl Archive Network), Ruby's
+RubyGems\footnote{\url{http://rubygems.org/}}
+and the Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}
 
@@
 that can depend on other versions.
+
+To statically analyze the Maven repository
+we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+a static analysis tool that examines bytecode to detect software bugs
+and has already been used in research~\cite{AP10,SHP06}.
+Specifically, we ran FindBugs on all the project versions of all
+the projects that exist in the repository
+to identify all bugs contained in it.
+
+In this paper we present: a) the experiment performed to obtain the
+collection of the metric results that the FindBugs tool produces and
+b) how researchers can actually use the dataset and include it in
+their research.
 

### 2014-01-19 docs/msr.tex
changed title, adding content in Section 2

@@
 
-\title{The Bug Catalog of the Maven Repository Ecosystem}
+\title{The Bug Catalog of the Maven Ecosystem}
 
@@
 \label{sec:exp}
-Body.
+
+First, we scanned the Maven repository only
+for appropriate {\sc jar}s and created a list that included them.
+This is because FindBugs analyzes applications written in Java,
+and the Maven repository hosts projects from
+languages other than Java such as Scala, Groovy,
+Clojure, etc. Thus we filtered out such projects.
+In particular, we obtained a snapshot (January 2012) of
+the repository and handled it locally to retrieve a list of all
+the names of the project versions that existed in it.
+A project version can be uniquely identified by the triplet:
+{\it group id}, {\it artifact id} and {\it version}.
+
+With the {\sc jar} list at hand, we created a series of processing tasks
+and added them to the task queue. Then we executed twenty five (Unix-based)
+workers that checked out tasks from the queue, processed the data and stored the
+results to the data repository.
+
+A typical processing cycle of a worker included the following steps: after
+the worker spawned, it requested a task from the queue. This task contained
+the {\sc jar} name, which was typically a project version that was downloaded locally.
+First, specific {\sc jar} metadata were calculated and stored. Such metadata included
+its size, its dependencies, and a number that represented the chronological order of the
+release. This order was derived from an {\sc xml} file that
+accompanies every project in the Maven repository called {\it
+maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
+also stored in the data repository. When the task was completed the queue
+was notified and the next task was requested. This process was executed for
+all the available {\sc jar}s in the task queue. A schematic representation of
+the data processing architecture can be seen in Figure~\ref{fig:arch}.
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[scale=0.73]{figures/arch.pdf}
+  \end{center}
+  \caption{The data processing architecture.}
+  \label{fig:arch}
+\end{figure}
 
@@
 
-\section{Tools}
-\label{sec:exp}
-Tools.
-
 \section{Related Work}
@@
 
-\section{Acknowledgments}
-possible acks.
-
 \bibliographystyle{abbrv}

### 2014-01-20 docs/msr.tex
section 2 draft ready

@@
 Examining software ecosystems can provide the research community
-with useful information. To examine the Maven Central Repository
-(approximately 265{\sc gb} of data), we performed an experiment
-where we statically analyzed the repository to detect its software
-bugs. For our analysis we used FindBugs, a tool that
-examines Java bytecode to detect numerous types of bugs.
-In this paper, we present our data collection experiment
-and show how our dataset can be used to extract interesting
-findings on software evolution.
+with useful information. To examine the ecosystem of
+the Maven Central Repository (approximately 265{\sc gb} of data),
+we performed an experiment where we statically analyzed the
+repository to detect its software bugs. For our analysis we
+used FindBugs, a tool that examines Java bytecode to detect
+numerous types of bugs. In this paper, we present our data
+collection experiment and show how our dataset can be used
+to extract interesting findings on software evolution.
 \end{abstract}
@@
 Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.
+hosted by the Apache Software Foundation.\footnote{\url{http://maven.apache.org/}}
 It uses {\sc xml} to describe the software project being built, its dependencies
@@
 collection of the metric results that the FindBugs tool produces and
-b) how researchers can actually use the dataset and include it in
-their research.
+b) how researchers can use the dataset and include it in their research.
+
+\begin{table}
+\centering
+\begin{tabular}{l r}
+\hline
+Measurement & Value\\
+ \hline
+Projects & 17,505\\
+Versions (total) & 115,214\\
+Min (versions per project) & 1\\
+Max (versions per project) & 338\\
+Mean (versions per project) & 6.58\\
+Median (versions per project) & 3\\
+Range (over versions) & 337\\
+1$^{st}$ Quartile (over versions) & 1\\
+3$^{rd}$ Quartile (over versions) & 8\\
+\hline
+\end{tabular}
+\caption{Descriptive statistic measurements for the Maven repository.}
+\label{tbl:repository}
+\end{table}
 
@@
 the names of the project versions that existed in it.
-A project version can be uniquely identified by the triplet:
-{\it group id}, {\it artifact id} and {\it version}.
+The statistic measurements concerning the repository can be seen in 
+Table~\ref{tbl:repository}.
 
 With the {\sc jar} list at hand, we created a series of processing tasks
-and added them to the task queue. Then we executed twenty five (Unix-based)
-workers that checked out tasks from the queue, processed the data and stored the
-results to the data repository.
+and added them to task queue mechanism (a Rabbit{\sc mq} message
+broker). Then we executed twenty five (Unix-based)
+workers (custom Python scripts) that checked out tasks
+from the queue, processed the data and stored the
+results to the data repository (a Mongo{\sc db}).
 
@@
 maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
-also stored in the data repository. When the task was completed the queue
-was notified and the next task was requested. This process was executed for
-all the available {\sc jar}s in the task queue. A schematic representation of
+also stored in the data repository. 
+FindBugs separates software bugs into nine
+categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
+(including Bad Practice, Security, Performance and others)
+and reports bug collections that include all the bugs discovered in a
+{\sc jar} file. For every registered bug, there are numerous accompanying features
+like the class, the method and the line that the bug was found.
+When the task was completed the queue
+was notified and the next task was requested. A schematic representation of
 the data processing architecture can be seen in Figure~\ref{fig:arch}.
 
-\begin{figure}[t]
+\begin{figure} [h]
   \begin{center}
@@
 
-\section{Repository Statistics}
-\label{sec:repo}
-Repo stats.
+\section{Tools and Findings}
+\label{sec:find}
+Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
+repository.
 
@@
 \end{figure}
-
-\section{Initial Findings}
-\label{sec:find}
-Findings.
 

### 2014-01-20 docs/msr.tex
minor changes, fixes

@@
 In this paper we present: a) the experiment performed to obtain the
-collection of the metric results that the FindBugs tool produces and
-b) how researchers can use the dataset and include it in their research.
+collection of the metric results that the FindBugs tool produces 
+for every project version of the repository (115,214 {\sc jar}s)
+and b) how researchers can use the dataset and include it in their research.
 
@@
 With the {\sc jar} list at hand, we created a series of processing tasks
-and added them to task queue mechanism (a Rabbit{\sc mq} message
-broker). Then we executed twenty five (Unix-based)
-workers (custom Python scripts) that checked out tasks
-from the queue, processed the data and stored the
-results to the data repository (a Mongo{\sc db}).
+and added them to a task queue mechanism (a Rabbit{\sc mq} message
+broker). Then we executed twenty five workers (custom Python scripts)
+that checked out tasks from the queue, processed each project version
+and stored the results to the data
+repository (a Mongo{\sc db} database system).
 

### 2014-01-20 docs/msr.tex
added related work section draft

@@
 
-Cite~\cite{RDV13}.
+The Maven ecosystem has been previously analyzed by
+Raemaekers et al.~\cite{RDV13}
+to produce the {\it Maven dependency dataset}.
+Apart from basic information like individual methods, classes,
+packages and lines of code for every {\sc jar}, the dataset
+also includes a database with all the
+connections between the aforementioned elements.
 

### 2014-01-21 docs/msr.tex
adding content in the "tools and findings" section

--- 2014-01-20 docs/msr.tex
@@
 \label{sec:find}
+
+As we mentioned earlier our data was stored in a
+Mongo{\sc db} database. Hence, it is easy to either create
+queries to find out basic information like:
+``how many bad practice bugs exist in the repository", or
+create scripts that can help us capture correlations
+that could provide valuable findings.
 Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
@@
 
-Cite~\cite{RDV13}.
+The Maven ecosystem has been previously analyzed by
+Raemaekers et al.~\cite{RDV13}
+to produce the {\it Maven dependency dataset}.
+Apart from basic information like individual methods, classes,
+packages and lines of code for every {\sc jar}, this dataset
+also includes a database with all the
+connections between the aforementioned elements.
 

### 2014-02-12 analysis/repo-statistics/bug_correlation_calc.py
handle bug types as in FindBugs

@@ -13,6 +13,7 @@ from corrplot import corrplot
 bug_types = [
     'SECURITY_HIGH',
     'SECURITY_LOW',
+    'SECURITY',
     'MALICIOUS_CODE',
     'STYLE',
     'BAD_PRACTICE',
@@ -23,35 +24,42 @@ bug_types = [
     'EXPERIMENTAL'
     ]
 
-labels = []
-for bug_type in bug_types:
-    if bug_type == 'I18N':
-        labels.append(bug_type.lower())
-    elif bug_type == 'MT_CORRECTNESS':
-        labels.append('MT Correctness')
-    elif bug_type == 'MALICIOUS_CODE':
-        pass
-    else:
-        labels.append(bug_type.title().replace('_', ' '))
-
 with open("data/bug_correlation_counters.json") as infile:
     json_input = json.load(infile)
 
 data = pd.DataFrame(json_input).T
 
+print "Raw"
 for bug_type in bug_types:
-    print bug_type, data[bug_type].count()
+    if bug_type in data:
+        count = data[bug_type].count()
+    else:
+        count = 0
+    print bug_type, count
 
-print "MALICIUS_CODE & SECURITY_LOW ", len(data[data['MALICIOUS_CODE']
-                                                * data['SECURITY_LOW'] > 0])
-    
-data['SECURITY_LOW'] = (data['MALICIOUS_CODE'].fillna(0)
-                        + data['SECURITY_LOW'].fillna(0)).replace(0, np.nan)
-data['TOTAL_SECURITY_LOW'] = (data['TOTAL_MALICIOUS_CODE'].fillna(0)
-                              + data['TOTAL_SECURITY_LOW'].fillna(0)
-                              ).replace(0, np.nan)
-data = data.drop(['MALICIOUS_CODE', 'TOTAL_MALICIOUS_CODE'], axis=1)
-bug_types.remove('MALICIOUS_CODE')
+sec_high = np.where(data['SECURITY_HIGH'].notnull())[0]
+sec_low = np.where(data['SECURITY_LOW'].notnull())[0]
+intersection_sec = np.intersect1d(sec_high, sec_low)
+
+data['SECURITY'] = (data['SECURITY_HIGH'].fillna(0)
+                    + data['SECURITY_LOW'].fillna(0)).replace(0, np.nan)
+                                                
+data['TOTAL_SECURITY'] = (data['TOTAL_SECURITY_HIGH'].fillna(0)
[…]

### 2014-02-13 analysis/repo-statistics/bug_correlation_calc.R
security subsumes high and low

@@ -6,13 +6,12 @@ library(ellipse)
 
 bug.counts <- read.csv("data/bug_correlation_counters.csv")
 
-bug.counts$SECURITY_HIGH <- bug.counts$SECURITY_HIGH + bug.counts$MALICIOUS_CODE
+bug.counts$SECURITY <- bug.counts$SECURITY_HIGH + bug.counts$SECURITY_LOW
 
 bug.counts$MALICIOUS_CODE <- NULL
 
 bug.counts$TOTAL_MALICIOUS_CODE <- NULL
-bug.counts$TOTAL_SECURITY_HIGH <- NULL
-bug.counts$TOTAL_SECURITY_LOW <- NULL
+bug.counts$TOTAL_SECURITY <- NULL
 bug.counts$TOTAL_STYLE <- NULL
 bug.counts$TOTAL_BAD_PRACTICE <- NULL
 bug.counts$TOTAL_CORRECTNESS <- NULL

### 2014-02-13 analysis/repo-statistics/bug_persistence_calc.py

@@ -7,8 +7,8 @@ import scipy.stats as st
 import collections
 
 bug_types_closed = collections.OrderedDict()
-bug_types_closed['SECURITY_HIGH'] = []
-bug_types_closed['SECURITY_LOW'] = []
+bug_types_closed['SECURITY'] = []
+bug_types_closed['MALICIOUS_CODE'] = []
 bug_types_closed['STYLE'] =  []
 bug_types_closed['CORRECTNESS'] = []
 bug_types_closed['BAD_PRACTICE'] = []
@@ -18,8 +18,8 @@ bug_types_closed['PERFORMANCE'] = []
 bug_types_closed['EXPERIMENTAL'] = []
 
 bug_labels = [
-    'Security High',
-    'Security Low',
+    'Security',
+    'Malicious Code',
     'Style',
     'Correctness',
     'Bad Practice',
@@ -51,8 +51,8 @@ with open("data/bug_persistence.json", "r") as json_file:
         for bug in bugs_opened.keys():
             if bug not in bugs:
                 bug_type = bug.partition('||')[0]
-                if bug_type == 'MALICIOUS_CODE':
-                    bug_type = 'SECURITY_LOW'
+                if bug_type == 'SECURITY_LOW' or bug_type == 'SECURITY_HIGH':
+                    bug_type = 'SECURITY'
                 diff = version_order - bugs_opened[bug]
                 bug_types_closed[bug_type].append(diff)
                 if diff < 1:
@@ -60,8 +60,6 @@ with open("data/bug_persistence.json", "r") as json_file:
                            bugs_opened[bug])
                 del bugs_opened[bug]
         for bug in bugs:
-            if bug == 'MALICIOUS_CODE':
-                bug = 'SECURITY_LOW'
             if bug not in bugs_opened:
                 bugs_opened[bug] = version_order
 

### 2014-02-13 analysis/repo-statistics/project_bugs_counts.py

@@ -11,8 +11,8 @@ import math
 import collections
 
 bugs_per_version = collections.OrderedDict()
-bugs_per_version['SECURITY_HIGH'] = []
-bugs_per_version['SECURITY_LOW'] = []
+bugs_per_version['SECURITY'] = []
+bugs_per_version['MALICIOUS_CODE'] = []
 bugs_per_version['STYLE'] =  []
 bugs_per_version['CORRECTNESS'] = []
 bugs_per_version['BAD_PRACTICE'] = []
@@ -22,8 +22,8 @@ bugs_per_version['PERFORMANCE'] = []
 bugs_per_version['EXPERIMENTAL'] = []
 
 bugs_per_version_labels = [
-    'Security High',
-    'Security Low',
+    'Security',
+    'Malicious Code',
     'Style',
     'Correctness',
     'Bad Practice',
@@ -41,12 +41,16 @@ with open("data/project_counters.json", "r") as json_file:
             if version_order == 0:
                 continue
             counters = version['Counters']
-            if 'MALICIOUS_CODE' in counters:
-                malicious_code = counters.pop('MALICIOUS_CODE')
-                if 'SECURITY_LOW' in counters:
-                    counters['SECURITY_LOW'] += malicious_code
-                else:
-                    counters['SECURITY_LOW'] = malicious_code
+            if 'SECURITY_LOW' in counters:
+                security_low = counters.pop('SECURITY_LOW')
+            else:
+                security_low = 0
+            if 'SECURITY_HIGH' in counters:
+                security_high = counters.pop('SECURITY_HIGH')
+            else:
+                security_high = 0
+            if security_low or security_high:
+                counters['SECURITY'] = security_low + security_high
             for counter in bugs_per_version.keys():
                 if counter in counters:
                     value = counters[counter]

### 2014-02-13 analysis/repo-statistics/project_counters_diffs.py

@@ -10,8 +10,8 @@ from collections import defaultdict, OrderedDict
 import itertools
 
 bug_types = (
-    'SECURITY_HIGH',
-    'SECURITY_LOW',
+    'SECURITY',
+    'MALICIOUS_CODE',
     'STYLE',
     'CORRECTNESS',
     'BAD_PRACTICE',
@@ -28,8 +28,8 @@ for bug_type in bug_types:
     bug_types_diffs[bug_type] = []
 
 bug_labels = {
-    'SECURITY_HIGH': 'Security High',
-    'SECURITY_LOW': 'Security Low',
+    'SECURITY': 'Security',
+    'MALICIOUS_CODE': 'Malicious Code',
     'STYLE': 'Style',
     'CORRECTNESS': 'Correctness',
     'BAD_PRACTICE': 'Bad Practice',
@@ -63,12 +63,16 @@ with open("data/project_counters.json", "r") as json_file:
                 continue
             counts[project].append({})
             counters = version['Counters']
-            if 'MALICIOUS_CODE' in counters:
-                malicious_code = counters.pop('MALICIOUS_CODE')
-                if 'SECURITY_LOW' in counters:
-                    counters['SECURITY_LOW'] += malicious_code
-                else:
-                    counters['SECURITY_LOW'] = malicious_code
+            if 'SECURITY_LOW' in counters:
+                security_low = counters.pop('SECURITY_LOW')
+            else:
+                security_low = 0
+            if 'SECURITY_HIGH' in counters:
+                security_high = counters.pop('SECURITY_HIGH')
+            else:
+                security_high = 0
+            if security_low or security_high:
+                counters['SECURITY'] = security_low + security_high
             for counter, value in counters.iteritems():
                 if version_order != len(counts[project]):
                     bad_project = True
@@ -112,7 +116,7 @@ for project, project_counts in counts.iteritems():
             (rho, p_value) = st.spearmanr(cc_arr, versions_arr)
             if p_value < 0.05:
                 counts_corrs.setdefault(counter, []).append(rho)
-                if counter == 'SECURITY_HIGH':
+                if counter == 'SECURITY':
                     print project, counter, len(cc_arr), cc_arr, rho, p_value
             else:
                 counts_corrs.setdefault(counter, []).append(0)

### 2014-02-13 analysis/repo-statistics/project_counters_jarsize_tab.py

@@ -1,14 +1,13 @@
 # Extracts the bug counters data from the JSON representation
 # and outputs them in CSV format so that it can be read by R.
 
-import ijson
 import json
 import sys
 import csv
 
 bug_types = [
-    'SECURITY_HIGH',
-    'SECURITY_LOW',
+    'SECURITY',
+    'MALICIOUS_CODE',
     'STYLE',
     'CORRECTNESS',
     'BAD_PRACTICE',
@@ -34,14 +33,16 @@ with open("data/project_counters_jarsize.csv", "w") as csv_output:
                 row = [project, meta_data['version_order'],
                        meta_data['jar_size']]
                 counters = version['Counters']
-                counters = version['Counters']
-                if 'MALICIOUS_CODE' in counters:
-                    malicious_code = counters.pop('MALICIOUS_CODE')
-                    if 'SECURITY_LOW' in counters:
-                        counters['SECURITY_LOW'] += malicious_code
-                    else:
-                        counters['SECURITY_LOW'] = malicious_code
-                security_low = 0
+                if 'SECURITY_LOW' in counters:
+                    security_low = counters.pop('SECURITY_LOW')
+                else:
+                    security_low = 0
+                if 'SECURITY_HIGH' in counters:
+                    security_high = counters.pop('SECURITY_HIGH')
+                else:
+                    security_high = 0
+                if security_low or security_high:
+                    counters['SECURITY'] = security_low + security_high
                 for bug_type in bug_types:
                     if bug_type in counters:
                         row.append(counters[bug_type])

### 2014-02-13 docs/msr.tex
A bit better arrangement for names in the header

@@
 
-\numberofauthors{5}
+\numberofauthors{1}
+
+%\author{
+%% 1st. author
+%\alignauthor
+%Dimitris Mitropoulos\\
+%       \affaddr{Athens University of Economics and Business}\\
+%       \affaddr{Department of Management Science and Technology}\\
+%       \email{dimitro@aueb.gr}
+%% 2nd. author
+%\alignauthor Vassilios Karakoidas\\
+%       \affaddr{Athens University of Economics and Business}\\
+%       \affaddr{Department of Management Science and Technology}\\
+%       \email{bkarak@aueb.gr}
+%% 3rd. author
+%\alignauthor Panos Louridas\\
+%       \affaddr{Athens University of Economics and Business}\\
+%       \affaddr{Department of Management Science and Technology}\\
+%       \email{louridas@aueb.gr}
+%\and  % use '\and' if you need 'another row' of author names
+%% 4th. author
+%\alignauthor Georgios Gousios\\
+%       \affaddr{Delft University of Technology}\\
+%       \affaddr{Software Engineering Research Group}\\
+%       \email{G.Gousios@tudelft.nl}
+%% 5th. author
+%\alignauthor Diomidis Spinellis\\
+%       \affaddr{Athens University of Economics and Business}\\
+%       \affaddr{Department of Management Science and Technology}\\
+%       \email{dds@aueb.gr}
+%}
+
+\def\aueb{\textsuperscript{*}}
+\def\tud{\textsuperscript{\dag}}
 
 \author{
-% 1st. author
-\alignauthor
-Dimitris Mitropoulos\\
-       \affaddr{Athens University of Economics and Business}\\
-       \affaddr{Department of Management Science and Technology}\\
-       \email{dimitro@aueb.gr}
-% 2nd. author
-\alignauthor Vassilios Karakoidas\\
-       \affaddr{Athens University of Economics and Business}\\
-       \affaddr{Department of Management Science and Technology}\\
-       \email{bkarak@aueb.gr}
-% 3rd. author
-\alignauthor Panos Louridas\\
-       \affaddr{Athens University of Economics and Business}\\
-       \affaddr{Department of Management Science and Technology}\\
-       \email{louridas@aueb.gr}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Georgios Gousios\\
-       \affaddr{Delft University of Technology}\\
-       \affaddr{Software Engineering Research Group}\\
-       \email{G.Gousios@tudelft.nl}
-% 5th. author
-\alignauthor Diomidis Spinellis\\
-       \affaddr{Athens University of Economics and Business}\\
-       \affaddr{Department of Management Science and Technology}\\
-       \email{dds@aueb.gr}
+  Dimitris Mitropoulos\aueb \and Vassilios Karakoidas\aueb \and Panos Louridas\aueb \and Georgios Gousios\tud \and Diomidis Spinellis\aueb \\
+  \begin{tabular}{ccc}
+  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\tud Software Engineering Research Group}\\
+    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\tud Delft University of Technology}\\
+   \affaddr{Athens, Greece} & & \affaddr{Delft, the Netherlands}\\
+   \email{\{dimitro,bkarak,louridas,dds\}@aueb.gr}& & \email{g.gousios@tudelft.nl} \\
+  \end{tabular}
 }

### 2014-02-16 docs/msr.tex
added corrplot in the text.
analysing data structure (initial)

@@
 
-\section{Tools and Findings}
+\section{Data and Findings}
 \label{sec:find}
@@
 As we mentioned earlier our data was stored in a
-Mongo{\sc db} database. Hence, it is easy to either create
+Mongo{\sc db} database, thus all the data stored 
+converted to the {\sc json} format. Originally, FindBugs output is in {\sc xml}, the conversion was a straight forward mapping
+of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a header metadata section, which contained
+several additional information regarding the jar file that has been processed.
+% dimitro@bkarak: add content here.
+Hence, it is easy to either create
 queries to find out basic information like:
@@
 	\label{fig:bug-per} 
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.43]{corrplot.pdf}
+  \caption{Correlation matrix plot for bug categories.}
+  \label{fig:corrplot}
 \end{figure}

### 2014-02-16 docs/msr.tex
added JSON schema

@@
 of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a header metadata section, which contained
-several additional information regarding the jar file that has been processed.
-% dimitro@bkarak: add content here.
+several additional information regarding the jar file that has been processed. The following listing contains a sample document:
+
+\begin{verbatim}
+{"JarMetadata": {"jar_filename": "",
+                 "jar_last_modification_date": "",
+                 "jar_size": "",
+                 "version": "",
+                 "version_list": "",
+                 "artifact_id": "",
+                 "group_id": "",
+                 "version_order": "",
+                 "dependencies": ""}, 
+ "BugCollection": { /* FindBugs data */ }}
+\end{verbatim}
+
 Hence, it is easy to either create

### 2014-02-16 docs/msr.tex
added table

--- 2014-02-16 docs/msr.tex
@@
 converted to the {\sc json} format. Originally, FindBugs output is in {\sc xml}, the conversion was a straight forward mapping
-of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a header metadata section, which contained
-several additional information regarding the jar file that has been processed.
-% dimitro@bkarak: add content here.
+of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
+several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains a sample document:
+
+\begin{verbatim}
+{"JarMetadata": {"jar_filename": "",
+                 "jar_size": "",
+                 "version": "",
+                 "version_list": "",
+                 "artifact_id": "",
+                 "group_id": "",
+                 "dependencies": ""}, 
+ "BugCollection": { /* FindBugs data */ }}
+\end{verbatim}
+
+\begin{table}
+\centering
+\caption{Jar metadata description}
+\label{tbl:metadata-description}
+\begin{tabular}{l p{5.0cm}}
+ \hline
+\textbf{Key} & \textbf{Value}\\
+ \hline
+\verb|jar_filename| & JAR's filename\\
+\verb|jar_size| & The size of the JAR file\\
+\verb|version| & The version of the project in Maven repository\\
+\verb|version_list| & A list of project's version numbers\\
+\verb|artifact_id| & The artifact id of the project in Maven repository\\
+\verb|group_id| & The group id of the project in Maven repository\\
+\verb|dependencies| & List of all dependencies for the project\\
+ \hline
+ \end{tabular}
+\end{table}
+
 Hence, it is easy to either create

### 2014-02-16 docs/msr.tex
updated data section

@@
 As we mentioned earlier our data was stored in a
-Mongo{\sc db} database, thus all the data stored 
-converted to the {\sc json} format. Originally, FindBugs output is in {\sc xml}, the conversion was a straight forward mapping
+Mongo{\sc db} database, thus all the data were 
+converted to the {\sc json} format. Originally, FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
 of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
-several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains a sample document:
+several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:
 
@@
 
+Since Mongo{\sc db} provides a rich query interface, it was easy to either create
+queries to find out basic information like:
+``how many bad practice bugs exist in the repository", or
+create scripts that can help us capture correlations
+that could provide valuable findings. Figure~\ref{fig:bug-per} shows how software 
+bugs are distributed among the repository.
+
 \begin{table}
@@
 \begin{tabular}{l p{5.0cm}}
- \hline
-\textbf{Key} & \textbf{Value}\\
  \hline
@@
 \end{table}
-
-Hence, it is easy to either create
-queries to find out basic information like:
-``how many bad practice bugs exist in the repository", or
-create scripts that can help us capture correlations
-that could provide valuable findings.
-Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
-repository.
 

### 2014-02-17 docs/msr.tex
minors
added updated persistence

@@
 used FindBugs, a tool that examines Java bytecode to detect
-numerous types of bugs. In this paper, we present our data
-collection experiment and show how our dataset can be used
-to extract interesting findings on software evolution.
+numerous types of bugs. In this paper we present our data collection
+experiment and show our findings regarding software evolution.
 \end{abstract}
@@
 Mongo{\sc db} database, thus all the data were 
-converted to the {\sc json} format. Originally, FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
+converted to the {\sc json} format. FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
 of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
@@
 \bibliography{msr}
+
+\begin{landscape}
+  \begin{table}
+    \setlength{\extrarowheight}{0.10cm}
+    \caption{Bug persistence comparison.}
+    \label{tbl:bug_persistence}
+    \resizebox{0.95\columnwidth}{!}{
+    \input{bug_persistence.tex}}\\
+    The matrix presents pairwise Mann-Whitney $U$ test results
+    between the different bug categories. Each cell contains the test
+    result (the value of $U$), the $p$-value, the average for each
+    category and the sample size for each category. Cells in brackets show
+    pairs where no statistically significant difference was found.
+  \end{table}
+\end{landscape}
+
 \end{document}

### 2014-02-17 analysis/repo-statistics/project_counters_jarsize_calc.py
added forgotten file

@@ -1,0 +1,116 @@
+# Extracts the bug counters data from the JSON representation
+# and calculates correlations between bug types and jarsizes
+
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.stats as st
+
+bug_types = [
+    'SECURITY',
+    'MALICIOUS_CODE',
+    'STYLE',
+    'CORRECTNESS',
+    'BAD_PRACTICE',
+    'MT_CORRECTNESS',
+    'I18N',
+    'PERFORMANCE',
+    'EXPERIMENTAL',
+]
+
+bug_type_labels = [
+    'Security',
+    'Malicious Code',
+    'Style',
+    'Correctness',
+    'Bad Practice',
+    'MT Correctness',
+    'i18n',
+    'Performance',
+    'Experimental',
+]
+
+rows = []
+
+with open("data/project_counters.json", "r") as json_file:
+    json_input = json.load(json_file)
+    for project, data in json_input.iteritems():
+        for version in data['versions']:
+            meta_data = version['JarMetadata']
+            row = [meta_data['jar_size']]
+            jar_size = meta_data['jar_size']
+            counters = version['Counters']
+            if 'SECURITY_LOW' in counters:
+                security_low = counters.pop('SECURITY_LOW')
+            else:
+                security_low = 0
+            if 'SECURITY_HIGH' in counters:
+                security_high = counters.pop('SECURITY_HIGH')
+            else:
+                security_high = 0
+            if security_low or security_high:
+                counters['SECURITY'] = security_low + security_high
+            for bug_type in bug_types:
+                if bug_type in counters:
+                    row.append(counters[bug_type])
+                else:
+                    row.append(np.nan)
+            rows.append(row)
+                                     
+num_plots = len(bug_types)
+num_cols = 4
+num_rows = num_plots / num_cols
+if num_rows % num_cols != 0:
+    num_rows += 1
+num_plot = 1
+
+fig1 = plt.figure(1, figsize=(16, 10))
+fig1.subplots_adjust(hspace=0.4)
+
+kilobyte = 1024.0
+
+counts_arr = np.array(rows)
+
+jarsizematrix = []
+column_indx = 1
+for i, bug_type in enumerate(bug_types):
[…]

### 2014-02-17 docs/msr.tex
added content

--- 2014-02-17 docs/msr.tex
@@
 When the task was completed the queue
-was notified and the next task was requested. A schematic representation of
-the data processing architecture can be seen in Figure~\ref{fig:arch}.
+was notified and the next task was requested.
 
-\begin{figure} [h]
-  \begin{center}
-    \includegraphics[scale=0.73]{figures/arch.pdf}
-  \end{center}
-  \caption{The data processing architecture.}
-  \label{fig:arch}
-\end{figure}
+A threat to the internal validity of our experiment
+could be the false alarms of the
+FindBugs tool~\cite{AP10, HP04}.
+For instance, reported security bugs may not
+be applicable to an application's typical use context.
+For instance, FindBugs could report an {\sc sql}
+injection vulnerability~\cite{RL12}
+in an application that receives no external input.
+In this particular context, this would be a false positive alarm.
 
@@
 
+\begin{table}
+\centering
+\begin{tabular}{l p{5.0cm}}
+ \hline
+\verb|jar_filename| & {\sc jar}'s filename. \\
+\verb|jar_size| & The size of the {\sc jar} file. \\
+\verb|version| & The version of the project in the repository. \\
+\verb|version_list| & A list of all available version's of this project. \\
+\verb|artifact_id| & The artifact {\sc id} of the project in Maven repository. \\
+\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
+\verb|dependencies| & List of all dependencies for the project. \\
+ \hline
+ \end{tabular}
+\caption{Jar metadata description.}
+\label{tbl:metadata-description}
+\end{table}
+
 As we mentioned earlier our data was stored in a
 Mongo{\sc db} database, thus all the data were 
-converted to the {\sc json} format. FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
-of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
-several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:
-
-\begin{verbatim}
-{"JarMetadata": {"jar_filename": "",
-                 "jar_size": "",
-                 "version": "",
-                 "version_list": "",
-                 "artifact_id": "",
-                 "group_id": "",
-                 "dependencies": ""}, 
- "BugCollection": { /* FindBugs data */ }}
-\end{verbatim}
-
-Since Mongo{\sc db} provides a rich query interface, it was easy to either create
-queries to find out basic information like:
-``how many bad practice bugs exist in the repository", or
-create scripts that can help us capture correlations
-that could provide valuable findings. Figure~\ref{fig:bug-per} shows how software 
-bugs are distributed among the repository.
-
-\begin{table}
-\centering
-\caption{Jar metadata description}
-\label{tbl:metadata-description}
-\begin{tabular}{l p{5.0cm}}
- \hline
-\verb|jar_filename| & JAR's filename\\
-\verb|jar_size| & The size of the JAR file\\
-\verb|version| & The version of the project in Maven repository\\
-\verb|version_list| & A list of project's version numbers\\
-\verb|artifact_id| & The artifact id of the project in Maven repository\\
-\verb|group_id| & The group id of the project in Maven repository\\
-\verb|dependencies| & List of all dependencies for the project\\
- \hline
- \end{tabular}
-\end{table}
+converted to the {\sc json} format. FindBugs output
+data is in {\sc xml} format. The conversion was a
+straight forward mapping
+of the {\sc xml} elements to {\sc json} objects.
+In addition, to the FindBugs data, we added a metadata
+section, which contained
+several additional information regarding the {\sc jar}
+file that has been processed
+(see Table~\ref{tbl:metadata-description}).
 
@@
 \end{figure}
+
+Since Mongo{\sc db} provides a rich query interface,
+it was easy to either create
+queries to find out basic information like:
+``how many bad practice bugs exist in the repository", or
+create scripts that can help us capture correlations
+that could provide interesting findings. For instance,
+Figure~\ref{fig:bug-per} shows how software 
+bugs are distributed among the repository.
+
+Together with our dataset, we have created a series of
+scripts to exhibit how it can be used regarding
+the evolution of software bugs.
+Table~\ref{tbl:bugsperversion} shows the relation between
+bugs and time. This relation, can be traced from the number of
+bugs per category in each project version. We can then calculate the
+Spearman correlations between the defects count and the ordinal
+version number across all projects to see if bigger versions relate to
+higher or lower defect counts.
+The zero tendency though, applies to all versions of all projects together.
+Thus, we also performed Spearman correlations between bug counts and version
+ordinals in all projects we examined individually. These paint a different picture
+from the above table, shown in Figure~\ref{fig:bugsversionscorr}. The
+spike in point zero is explained by the large number of projects for
+which no correlation could be established---the scale is
+logarithmic.
+Figure~\ref{fig:bugdiffs}, presents a histogram of the changes
+of different bug counts in
+project versions. In most cases, a bug count does not change between
+versions; but when it does change, it may change upwards or downwards.
+
+\begin{table}[tphp]
+    \centering
+    \caption{Correlations between version and defects count.}
+    \label{tbl:bugsperversion}
+    \input{bugsperversion.tex}
+\end{table}
+
+\begin{figure*}[p]
+  \centering
+  \includegraphics[scale=0.30]{bugsversionscorr}
+  \caption{Histograms of correlations between bug counts and version
+    ordinals per project. In brackets the total population size and
+    the number of no correlation instances.}
+  \label{fig:bugsversionscorr}
+  \centering
+  \includegraphics[scale=0.35]{bugdiffs}
+  \caption{Changes in bug counts between versions.}
+  \label{fig:bugdiffs}
+\end{figure*}
+
+To examine the relation between the persistence of different kinds of
+bugs we used as a persistence
+indicator the number of versions a bug remains open in a project. To
+``tag" a bug we created a bug identifier by using the type of the bug,
+the method name and the class name in which the bug was found in. We
+chose not to use the line number of the location of the bug since it
+could change from version to version and after a possible code
+refactoring. We grouped the persistence numbers by bug categories and
+then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
+category pairs. The results are presented in
+Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
+brackets show pairs where no statistically significant difference was
+found.
+
+In addition, we explored the relation between defects with the size of a project
+version, measured by the size of its {\sc jar} file by carrying out
+correlation tests between the size and the defect counts for each
+project and version. The results can be seen in
+Table~\ref{tbl:jarsizecorr}.
+
+Finally, Figure~\ref{fig:corrplot} presents the pairwise correlations
+between all bug categories. To establish these correlations,
+we calculated the
+correlations between the number of distinct bugs that appeared in
+a project throughout its lifetime.
+
+\begin{table}[hbt]
+    \centering
+    \caption{Correlations between {\sc jar} size and defects count.}
+    \label{tbl:jarsizecorr}
+    \input{jarsizecorr.tex}
+\end{table}
 
@@
 connections between the aforementioned elements.
+%Our work goes a step further and includes for every {\sc jar}
+%of the repository, all the software bug that it contains.
 

### 2014-02-17 docs/msr.tex
added conclusions

@@
 connections between the aforementioned elements.
-%Our work goes a step further and includes for every {\sc jar}
-%of the repository, all the software bug that it contains.
 
@@
 \label{sec:conc}
+
+In this paper, we have presented a dataset that contains
+for every {\sc jar} of the Maven Central Repository,
+all the software bug that it contains among with some
+other metadata. We have also shown how our data can be
+used to extract results concerning software evolution.
+Research concerning the examination of specific bugs
+can be facilitated by our dataset. For instance,
+we have examined the characteristics of security
+bugs in a previous paper, based upon this dataset~\cite{MKLGS13}.
+
+% dimitro@ bkarak: add dataset and source code availability.
+% All source code and data are available ...
 

### 2014-02-17 test/convert-findbugs-xml/convert-test.py
removed test directory

@@ -1,36 +1,0 @@
-#!/usr/bin/env python
-#
-# Redistribution and use in source and binary forms, with or without
-# modification, are permitted provided that the following conditions
-# are met:
-#
-#   1. Redistributions of source code must retain the above copyright
-#      notice, this list of conditions and the following disclaimer.
-#
-#  2. Redistributions in binary form must reproduce the above copyright
-#     notice, this list of conditions and the following disclaimer in the
-#     documentation and/or other materials provided with the distribution.
-#
-# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
-# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
-# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
-# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
-# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
-# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
-# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
-# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
-# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
-# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
-# SUCH DAMAGE.
-#
-#
-# Test Naive conversion of Findbugs XML to JSON (using the xmldict utility) 
-#
-# Authors:
-#    Vassilios Karakoidas (vassilios.karakoidas@gmail.com)
-
-import xmldict, json
-
-findbugs_xml = open('acegi-security-0.5.jar-findbugs.xml', 'r')
-
-print json.dumps(xmldict.parse(findbugs_xml)).replace('"@','"')

### 2014-02-17 test/convert-findbugs-xml/xmldict.py

@@ -1,252 +1,0 @@
-#!/usr/bin/env python
-"Makes working with XML feel like you are working with JSON"
-
-from xml.parsers import expat
-from xml.sax.saxutils import XMLGenerator
-from xml.sax.xmlreader import AttributesImpl
-try: # pragma no cover
-    from cStringIO import StringIO
-except ImportError: # pragma no cover
-    try:
-        from StringIO import StringIO
-    except ImportError:
-        from io import StringIO
-try: # pragma no cover
-    from collections import OrderedDict
-except ImportError: # pragma no cover
-    OrderedDict = dict
-
-try: # pragma no cover
-    _basestring = basestring
-except NameError: # pragma no cover
-    _basestring = str
-try: # pragma no cover
-    _unicode = unicode
-except NameError: # pragma no cover
-    _unicode = str
-
-__author__ = 'Martin Blech'
-__version__ = '0.3'
-__license__ = 'MIT'
-
-class ParsingInterrupted(Exception): pass
-
-class _DictSAXHandler(object):
-    def __init__(self,
-                 item_depth=0,
-                 item_callback=lambda *args: True,
-                 xml_attribs=True,
-                 attr_prefix='@',
-                 cdata_key='#text',
-                 force_cdata=False,
-                 cdata_separator='',
-                 postprocessor=None):
-        self.path = []
-        self.stack = []
-        self.data = None
-        self.item = None
-        self.item_depth = item_depth
-        self.xml_attribs = xml_attribs
-        self.item_callback = item_callback
-        self.attr_prefix = attr_prefix
-        self.cdata_key = cdata_key
-        self.force_cdata = force_cdata
-        self.cdata_separator = cdata_separator
-        self.postprocessor = postprocessor
-
-    def startElement(self, name, attrs):
-        self.path.append((name, attrs or None))
-        if len(self.path) > self.item_depth:
-            self.stack.append((self.item, self.data))
-            attrs = OrderedDict((self.attr_prefix+key, value)
-                for (key, value) in attrs.items())
-            self.item = self.xml_attribs and attrs or None
-            self.data = None
-
-    def endElement(self, name):
-        if len(self.path) == self.item_depth:
-            item = self.item
-            if item is None:
-                item = self.data
-            should_continue = self.item_callback(self.path, item)
-            if not should_continue:
-                raise ParsingInterrupted()
-        if len(self.stack):
-            item, data = self.item, self.data
[…]

### 2014-02-17 test/maven_test.sh

@@ -1,56 +1,0 @@
-#!/usr/bin/env python
-#
-# Redistribution and use in source and binary forms, with or without
-# modification, are permitted provided that the following conditions
-# are met:
-#
-#   1. Redistributions of source code must retain the above copyright
-#      notice, this list of conditions and the following disclaimer.
-#
-#  2. Redistributions in binary form must reproduce the above copyright
-#     notice, this list of conditions and the following disclaimer in the
-#     documentation and/or other materials provided with the distribution.
-#
-# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
-# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
-# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
-# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
-# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
-# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
-# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
-# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
-# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
-# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
-# SUCH DAMAGE.
-#
-#
-# initial script to test findbugs time.
-# change the path of the repository accordingly.
-#
-# Authors:
-#    Vassilios Karakoidas (vassilios.karakoidas@gmail.com)
-#    Dimitrios Mitropoulos (dimitro@aueb.gr)
-#
-
-# configuration variables
-MAVEN_REPOSITORY=/Users/dimitro/Software/uk.maven.org/maven2
-MAVEN_FULL_JARS=maven-full-jars.text
-MAVEN_BINARIES=maven-binaries-jars.text
-
[…]

### 2014-02-17 workers/worker-findbugs/process-win.py
removed workers

@@ -1,456 +1,0 @@
-#!/usr/bin/env python
-#
-# Redistribution and use in source and binary forms, with or without
-# modification, are permitted provided that the following conditions
-# are met:
-#
-#   1. Redistributions of source code must retain the above copyright
-#      notice, this list of conditions and the following disclaimer.
-#
-#  2. Redistributions in binary form must reproduce the above copyright
-#     notice, this list of conditions and the following disclaimer in the
-#     documentation and/or other materials provided with the distribution.
-#
-# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
-# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
-# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
-# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
-# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
-# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
-# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
-# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
-# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
-# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
-# SUCH DAMAGE.
-
-""" Read URLs from an AMQP queue, download referenced JAR, process it with
-Findbugs, store the results to a MongoDB collection.
-
-"""
-import json, pika, sys, os, logging, pymongo, time, urllib
-
-from subprocess import Popen, PIPE, STDOUT
-from threading import Thread
-
-__author__ = 'Georgios Gousios <gousiosg@gmail.com>, Vassilios Karakoidas (vassilios.karakoidas@gmail.com), Dimitrios Mitropoulos (dimitro@aueb.gr)'
-
-
-RETRY_ATTEMPTS = 3
-
[…]

### 2014-02-17 workers/worker-findbugs/process.py

@@ -1,523 +1,0 @@
-#!/usr/bin/env python
-#
-# Redistribution and use in source and binary forms, with or without
-# modification, are permitted provided that the following conditions
-# are met:
-#
-#   1. Redistributions of source code must retain the above copyright
-#      notice, this list of conditions and the following disclaimer.
-#
-#  2. Redistributions in binary form must reproduce the above copyright
-#     notice, this list of conditions and the following disclaimer in the
-#     documentation and/or other materials provided with the distribution.
-#
-# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
-# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
-# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
-# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
-# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
-# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
-# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
-# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
-# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
-# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
-# SUCH DAMAGE.
-
-""" Read URLs from an AMQP queue, download referenced JAR, process it with
-Findbugs, store the results to a MongoDB collection.
-
-"""
-import json
-
-import pika
-import sys
-import os
-import logging
-import pymongo
-import time
-import urllib
-from subprocess import Popen, PIPE, STDOUT
-from signal import signal, SIGINT, SIGUSR1, SIGTERM
-from daemon import daemon
-
-# Take care of differences between python-daemon versions.
-try:
-    from daemon import pidfile
-except:
-    from daemon import pidlockfile
-
[…]

### 2014-02-17 workers/worker-findbugs/setup.py

@@ -1,4 +1,0 @@
-from distutils.core import setup
-import py2exe
-
-setup(console=['process-win.py'])

### 2014-02-17 workers/worker-findbugs/xmldict.py

@@ -1,250 +1,0 @@
-#!/usr/bin/env python
-"Makes working with XML feel like you are working with JSON"
-
-from xml.parsers import expat
-from xml.sax.saxutils import XMLGenerator
-from xml.sax.xmlreader import AttributesImpl
-try: # pragma no cover
-    from cStringIO import StringIO
-except ImportError: # pragma no cover
-    try:
-        from StringIO import StringIO
-    except ImportError:
-        from io import StringIO
-try: # pragma no cover
-    from collections import OrderedDict
-except ImportError: # pragma no cover
-    OrderedDict = dict
-
-try: # pragma no cover
-    _basestring = basestring
-except NameError: # pragma no cover
-    _basestring = str
-try: # pragma no cover
-    _unicode = unicode
-except NameError: # pragma no cover
-    _unicode = str
-
-__author__ = 'Martin Blech'
-__version__ = '0.3'
-__license__ = 'MIT'
-
-class ParsingInterrupted(Exception): pass
-
-class _DictSAXHandler(object):
-    def __init__(self,
-                 item_depth=0,
-                 item_callback=lambda *args: True,
-                 xml_attribs=True,
-                 attr_prefix='@',
-                 cdata_key='#text',
-                 force_cdata=False,
-                 cdata_separator='',
-                 postprocessor=None):
-        self.path = []
-        self.stack = []
-        self.data = None
-        self.item = None
-        self.item_depth = item_depth
-        self.xml_attribs = xml_attribs
-        self.item_callback = item_callback
-        self.attr_prefix = attr_prefix
-        self.cdata_key = cdata_key
-        self.force_cdata = force_cdata
-        self.cdata_separator = cdata_separator
-        self.postprocessor = postprocessor
-
-    def startElement(self, name, attrs):
-        self.path.append((name, attrs or None))
-        if len(self.path) > self.item_depth:
-            self.stack.append((self.item, self.data))
-            attrs = OrderedDict((self.attr_prefix+key, value)
-                for (key, value) in attrs.items())
-            self.item = self.xml_attribs and attrs or None
-            self.data = None
-
-    def endElement(self, name):
-        if len(self.path) == self.item_depth:
-            item = self.item
-            if item is None:
-                item = self.data
-            should_continue = self.item_callback(self.path, item)
-            if not should_continue:
-                raise ParsingInterrupted()
-        if len(self.stack):
-            item, data = self.item, self.data
[…]

### 2014-02-18 docs/msr.tex
minor change
updated msr.tex a little (added availability); working on README.md
added availability
minor changes

--- 2014-02-17 docs/msr.tex
@@
 with useful information. To examine the ecosystem of
-the Maven Central Repository (approximately 265{\sc gb} of data),
+the Maven central repository (approximately 265{\sc gb} of data),
 we performed an experiment where we statically analyzed the
@@
 To build a software component, it dynamically downloads Java libraries
-and Maven plug-ins from the Maven central repository,
+and Maven plug-ins from the {\it Maven central
+repository},\footnote{\url{http://mvnrepository.com/}}
 and stores them in a local cache. The repository can be updated with
@@
 for every project version of the repository (115,214 {\sc jar}s)
-and b) how researchers can use the dataset and include it in their research.
+and b) how researchers can use the dataset and produce
+meaningful results.
 
@@
 the repository and handled it locally to retrieve a list of all
-the names of the project versions that existed in it.
+the names of the Java project versions that existed in it.
 The statistic measurements concerning the repository can be seen in 
@@
 First, specific {\sc jar} metadata were calculated and stored. Such metadata included
-its size, its dependencies, and a number that represented the chronological order of the
-release. This order was derived from an {\sc xml} file that
+its size, its dependencies, and a number that represented the ordinal version number
+of the release. This number was derived from an {\sc xml} file that
 accompanies every project in the Maven repository called {\it
@@
 categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-(including Bad Practice, Security, Performance and others)
+(including {\it Bad Practice}, {\it Security}, {\it Performance} and others)
 and reports bug collections that include all the bugs discovered in a
@@
 FindBugs tool~\cite{AP10, HP04}.
-For instance, reported security bugs may not
+Specifically, reported security bugs may not
 be applicable to an application's typical use context.
@@
  \end{tabular}
-\caption{Jar metadata description.}
+\caption{{\sc jar} metadata description.}
 \label{tbl:metadata-description}
@@
 As we mentioned earlier our data was stored in a
-Mongo{\sc db} database, thus all the data were 
-converted to the {\sc json} format. FindBugs output
-data is in {\sc xml} format. The conversion was a
-straight forward mapping
-of the {\sc xml} elements to {\sc json} objects.
-In addition, to the FindBugs data, we added a metadata
+Mongo{\sc db} database. FindBugs though,
+outputs its' results in  {\sc xml} format.
+Hence all the data were
+converted to the {\sc json} format
+by mapping all {\sc xml} elements to {\sc json} objects.
+In addition, to the FindBugs data, we also added a metadata
 section, which contained
@@
 	\centering
-	\includegraphics[scale=0.38]{figures/bug_percent}
+	\includegraphics[scale=0.32]{figures/bug_percent}
 	\caption{Bug percentage in Maven repository.}
@@
 it was easy to either create
-queries to find out basic information like:
-``how many bad practice bugs exist in the repository", or
-create scripts that can help us capture correlations
-that could provide interesting findings. For instance,
-Figure~\ref{fig:bug-per} shows how software 
-bugs are distributed among the repository.
+simple scripts to find out basic information like
+``how software bugs are distributed among the
+repository?". Figure~\ref{fig:bug-per}
+actually, illustrates this distribution.
 
-Together with our dataset, we have created a series of
-scripts to exhibit how it can be used regarding
+%But apart from such simple observations
+%create scripts that can help us capture correlations
+%that could provide interesting findings. For instance,
+
+Together with our dataset, we have also created a series of
+scripts to exhibit how the dataset can be used
+to capture correlations regarding
 the evolution of software bugs.
+
 Table~\ref{tbl:bugsperversion} shows the relation between
 bugs and time. This relation, can be traced from the number of
-bugs per category in each project version. We can then calculate the
-Spearman correlations between the defects count and the ordinal
-version number across all projects to see if bigger versions relate to
-higher or lower defect counts.
-The zero tendency though, applies to all versions of all projects together.
+bugs per category in each project version. Specifically, we
+calculated the Spearman correlations between the defects
+count and the ordinal version number across all projects.
+The zero tendency that can be seen on Table~\ref{tbl:bugsperversion}
+though, applies to all versions of all projects together.
 Thus, we also performed Spearman correlations between bug counts and version
@@
     \centering
+        \input{bugsperversion.tex}
 	\caption{Correlations between version and defects count.}
     \label{tbl:bugsperversion}
-    \input{bugsperversion.tex}
 \end{table}
@@
 refactoring. We grouped the persistence numbers by bug categories and
-then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
+then performed a Mann-Whitney $U$ test among all bug
 category pairs. The results are presented in
@@
     \centering
+    \input{jarsizecorr.tex}
     \caption{Correlations between {\sc jar} size and defects count.}
     \label{tbl:jarsizecorr}
-    \input{jarsizecorr.tex}
 \end{table}
@@
 \label{sec:conc}
+
+In this paper, we have presented a dataset that contains
+for every {\sc jar} of the Maven central repository,
+all the software bug that it contains among with some
+other metadata. We have also shown how our data can be
+used to extract results concerning software evolution.
+Research concerning the examination of specific bugs
+can also be facilitated by our dataset. For instance,
+we have examined the characteristics of security
+bugs in a previous paper~\cite{MKLGS13}
+based on this dataset.
+
+The complete set of our data and source code
+can be found at
+\url{https://github.com/bkarak/data_paper_msr2014}.
 

### 2014-02-18 worker/process.py
also added the python worker and its dependencies

@@ -1,0 +1,523 @@
+#!/usr/bin/env python
+#
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions
+# are met:
+#
+#   1. Redistributions of source code must retain the above copyright
+#      notice, this list of conditions and the following disclaimer.
+#
+#  2. Redistributions in binary form must reproduce the above copyright
+#     notice, this list of conditions and the following disclaimer in the
+#     documentation and/or other materials provided with the distribution.
+#
+# THIS SOFTWARE IS PROVIDED BY THE REGENTS AND CONTRIBUTORS ``AS IS'' AND
+# ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+# IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+# ARE DISCLAIMED.  IN NO EVENT SHALL THE REGENTS OR CONTRIBUTORS BE LIABLE
+# FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+# DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
+# OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+# HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
+# LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
+# OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
+# SUCH DAMAGE.
+
+""" Read URLs from an AMQP queue, download referenced JAR, process it with
+Findbugs, store the results to a MongoDB collection.
+
+"""
+import json
+
+import pika
+import sys
+import os
+import logging
+import pymongo
+import time
+import urllib
+from subprocess import Popen, PIPE, STDOUT
+from signal import signal, SIGINT, SIGUSR1, SIGTERM
+from daemon import daemon
+
+# Take care of differences between python-daemon versions.
+try:
+    from daemon import pidfile
+except:
+    from daemon import pidlockfile
+
[…]

### 2014-02-18 docs/msr.tex
minor changes

@@
 the {\sc jar} name, which was typically a project version that was downloaded locally.
-First, specific {\sc jar} metadata were calculated and stored. Such metadata included
-its size, its dependencies, and a number that represented the ordinal version number
+First, specific {\sc jar} metadata were calculated and stored
+(see Table~\ref{tbl:metadata-description}).
+Such metadata included
+its size, its dependencies, and a number that
+represented the ordinal version number
 of the release. This number was derived from an {\sc xml} file that
@@
 like the class, the method and the line that the bug was found.
+Its results, also include additional information like
+the number of classes included in the examined {\sc jar}
+and others.
 When the task was completed the queue
@@
 
-A threat to the internal validity of our experiment
-could be the false alarms of the
-FindBugs tool~\cite{AP10, HP04}.
+A threat to the internal
+validity of our experiment could be the false
+alarms of the FindBugs tool~\cite{AP10, HP04}.
 Specifically, reported security bugs may not
@@
 in an application that receives no external input.
-In this particular context, this would be a false positive alarm.
+In this particular context, this would be a false
+positive alarm.
 
@@
 As we mentioned earlier our data was stored in a
-Mongo{\sc db} database. FindBugs though,
-outputs its' results in  {\sc xml} format.
+Mongo{\sc db} database.
+FindBugs incorporates a priori an ability to perform
+sophisticated queries on bug databases and
+track warnings across multiple versions of code being
+studied.\footnote{\url{http://findbugs.sourceforge.net/manual/datamining.html}}
+FindBugs though,
+outputs its results in  {\sc xml} format.
 Hence all the data were
@@
 by mapping all {\sc xml} elements to {\sc json} objects.
-In addition, to the FindBugs data, we also added a metadata
-section, which contained
-several additional information regarding the {\sc jar}
-file that has been processed
-(see Table~\ref{tbl:metadata-description}).
+Since Mongo{\sc db} provides a rich query interface,
+it was easy to either create
+simple scripts to find out
+how software bugs are distributed among the
+repository. Figure~\ref{fig:bug-per}
+actually, illustrates this distribution.
 
@@
 \end{figure}
-
-Since Mongo{\sc db} provides a rich query interface,
-it was easy to either create
-simple scripts to find out basic information like
-``how software bugs are distributed among the
-repository?". Figure~\ref{fig:bug-per}
-actually, illustrates this distribution.
 
@@
 the evolution of software bugs.
-
 Table~\ref{tbl:bugsperversion} shows the relation between
@@
 connections between the aforementioned elements.
+Our work differs from this research because it
+reports all bugs coming from the output of a
+static analysis tool, for each {\sc jar}
+contained in the Maven repository.
 

### 2014-02-20 docs/msr.tex
working on data collection

@@
 
-First, we scanned the Maven repository only
-for appropriate {\sc jar}s and created a list that included them.
-This is because FindBugs analyzes applications written in Java,
-and the Maven repository hosts projects from
-languages other than Java such as Scala, Groovy,
-Clojure, etc. Thus we filtered out such projects.
+The data collection process started with the mirroring of the Maven repository.
+The repository typically contains the {\sc jar} files with sources and binary distributions, 
+{\sc xml} metadata files that contain the version list for each project and its dependencies and one 
+metadata file, also in {\sc xml} format, with specific data for each version.
+
+We exported a list of all the {\sc jar} files in the repository and initially we excluded those
+that contained the source distribution for the projects. Then we kept all those {\sc jar}s that 
+referred to Java projects, because Findbugs analyzes only applications written in Java,
+and the Maven repository hosts projects from languages other than Java such as Scala, Groovy,
+Clojure, etc.
+
+The initial snapshot of the repository was obtained in January 2012 and those experinment took
+place in the end of 2012. In the meantime, several versions were released for some of the selected project.
+We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
+all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
+the missing ones.
+
+The whole process produced a file list with all the valid {\sc jar} files for our experinment.
+
 In particular, we obtained a snapshot (January 2012) of

### 2014-02-20 docs/msr.tex
added data collection

@@
 The whole process produced a file list with all the valid {\sc jar} files for our experinment.
+Each file on the list were uploaded as a separate task in the task queue (Figure~XXX).
+Concurent workers processed each task and submitted the results to the mongo database.
+
+When the processing was completed, we ran a series of sanity checks on the results, to check their validity.
+We discovered several issues, which we addressed with various approaches.
+The most common problem was Findbugs out-of-memory crashes, which demanded to repeat the process for those {\sc jar}s with the appropriate settings in the Java runtime environment.
+
+The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct.
 

### 2014-02-20 docs/msr.tex
updated section 2; merged new text with the previous one

@@
 The initial snapshot of the repository was obtained in January 2012 and those experinment took
-place in the end of 2012. In the meantime, several versions were released for some of the selected project.
+place in the end of 2012. The statistic measurements concerning the repository can be seen in 
+Table~\ref{tbl:repository}. In the meantime, several versions were released for some of the selected project.
 We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
@@
 Concurent workers processed each task and submitted the results to the mongo database.
-
-When the processing was completed, we ran a series of sanity checks on the results, to check their validity.
-We discovered several issues, which we addressed with various approaches.
-The most common problem was Findbugs out-of-memory crashes, which demanded to repeat the process for those {\sc jar}s with the appropriate settings in the Java runtime environment.
-
-The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct.
-
-In particular, we obtained a snapshot (January 2012) of
-the repository and handled it locally to retrieve a list of all
-the names of the Java project versions that existed in it.
-The statistic measurements concerning the repository can be seen in 
-Table~\ref{tbl:repository}.
-
-With the {\sc jar} list at hand, we created a series of processing tasks
-and added them to a task queue mechanism (a Rabbit{\sc mq} message
-broker). Then we executed twenty five workers (custom Python scripts)
-that checked out tasks from the queue, processed each project version
-and stored the results to the data
-repository (a Mongo{\sc db} database system).
-
 A typical processing cycle of a worker included the following steps: after
@@
 and others.
-When the task was completed the queue
-was notified and the next task was requested.
 
-A threat to the internal
+When the processing was completed, we ran a series of sanity checks on the results, to check their validity.
+We discovered several issues, which we addressed with various approaches.
+The most common problem was Findbugs out-of-memory crashes, which demanded to repeat the process for those {\sc jar}s with the appropriate settings in the Java runtime environment.
+
+The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct. A threat to the internal
 validity of our experiment could be the false

### 2014-02-20 tools/check_empty.py
added tools directory

@@ -1,0 +1,39 @@
+import urllib, xmldict
+
+
+def main():
+    base_url = 'http://mirrors.ibiblio.org/maven2/'
+
+    fp = open('data/bugless_projects.json', 'r')
+    c = 0
+
+    for l in fp:
+        arr = l.strip().split('||')
+        group_id = arr[0]
+        artifact_id = arr[1]
+        c += 1
+
+        maven_base_url = '%s%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
+        maven_metadata_name = '%smaven-metadata.xml' % (maven_base_url,)
+        local_maven_metadata_name = 'work/maven-metadata.xml.%d' % (c,)
+        urllib.urlretrieve(maven_metadata_name, local_maven_metadata_name)
+        json_xml = xmldict.parse(open(local_maven_metadata_name, 'r').read())
+        versions = json_xml.get('metadata', {}).get('versioning', {}).get('versions', {}).get('version')
+        version_list = []
+
+        if isinstance(versions, list):
+            version_list.extend(versions)
+        else:
+            version_list.append(versions)
+
+        for v in version_list:
+            vfile = '%s-%s.jar' % (artifact_id, v)
+            vfile_url = '%s%s/%s' % (maven_base_url, v, vfile)
+            urllib.urlretrieve(vfile_url, 'work/%s' % (vfile,))
+            print vfile_url
+
+    fp.close()
+
+
+if __name__ == "__main__":
+    main()

### 2014-02-20 tools/check_missing_local.py

@@ -1,0 +1,81 @@
+import os
+import zipfile
+import xmldict
+import sys
+
+from helpers.data_helper import load_projects_json
+
+from helpers.mongo_helper import get_version, get_mongo_connection, MONGO_COL
+
+
+def has_classes(filename):
+    try:
+        if zipfile.is_zipfile(filename):
+            z = zipfile.ZipFile(filename)
+            for f in z.namelist():
+                if f.endswith('.class'):
+                    #print 'Valid JAR file: %s' % (filename,)
+                    return True
+        else:
+            print '%s is not a zipfile (has_classes)' % (filename,)
+
+        return False
+    except Exception, e:
+        return False
+
+
+def main():
+    base_url = '/Users/bkarak/devel/repositories/maven/maven/'
+    col_obj = get_mongo_connection()[MONGO_COL]
+    projects = load_projects_json()
+
+    total_jars = 0
+    missing = 0
+    really_missing = 0
+
+    for proj in projects:
+        group_id = proj.group_id().strip()
+        artifact_id = proj.artifact_id().strip()
+        maven_base_url = '%s%s/%s/' % (base_url, group_id.replace('.', '/'), artifact_id)
+        maven_metadata_name = '%smaven-metadata.xml' % (maven_base_url,)
+
+        if not os.path.exists(maven_metadata_name):
+            continue
+
+        json_xml = xmldict.parse(open(maven_metadata_name, 'r').read())
+        versions = json_xml.get('metadata', {}).get('versioning', {}).get('versions', {}).get('version')
+        version_list = []
+
+        if isinstance(versions, list):
+            version_list.extend(versions)
+        else:
+            version_list.append(versions)
+
+        for v in version_list:
+            if v is not None:
+                v = v.strip()
+            docs = get_version(col_obj, group_id, artifact_id, v)
+            total_jars += 1
+
+            if len(docs) == 0:
+                missing += 1
+                sys.stderr.write('[%d]: Missing %s||%s||%s\n' % (total_jars, group_id, artifact_id, v))
+                local_jar_path = '%s%s/%s-%s.jar' % (maven_base_url, v, artifact_id, v)
+
+                if not os.path.exists(local_jar_path):
+                    sys.stderr.write('[%d]: Invalid Jar: %s||%s||%s\n' % (total_jars, group_id, artifact_id, v))
+                    really_missing += 1
+                else:
+                    if has_classes(local_jar_path):
[…]

### 2014-02-20 tools/helpers/data_helper.py

@@ -1,0 +1,85 @@
+import os, json
+
+
+__author__ = "Vassilios Karakoidas (vassilios.karakoidas@gmail.com)"
+
+
+class ArrayCount(object):
+    def __init__(self):
+        super(ArrayCount, self).__init__()
+        self.__arrayDict = {}
+
+    def incr(self, item, delta=1):
+        self.__arrayDict[item] = self.__arrayDict.get(item, 0) + delta
+
+    def get_item(self, item):
+        return self.__arrayDict.get(item, 0)
+
+    def get_series(self):
+        return self.__arrayDict
+
+    def item_count(self):
+        return len(self.__arrayDict)
+
+    def value_count(self):
+        return sum(self.__arrayDict.values())
+
+
+def save_to_file(filename, data):
+    fp = open(filename, 'w')
+    fp.write(data)
+    fp.close()
+
+
+def load_vuln_projects_json():
+    from models.project import Project
+
+    fp = open('data/vuln_projects.json', 'r')
+    prj_json = json.load(fp)
+    fp.close()
+
+    project_list = []
+
+    for pk in prj_json:
+        project_list.append(Project.parse_project(pk, 0))
+
+    return project_list
+
+
+def load_projects_json():
+    from models.project import Project
+
+    if not os.path.exists('data/project_versions.json'):
+        print '[ERROR]: data/project_versions.json does not exist!'
+        return []
+
+    project_list = []
+    fp = open('data/project_versions.json', 'r')
+    prj_json = json.load(fp)
+    fp.close()
+
+    for (k, v) in prj_json.iteritems():
+        project_list.append(Project.parse_project(k, v))
+
+    return project_list
+
+
+def load_evolution_projects_json():
+    from models.project import Project
+
+    if not os.path.exists('data/valid_projects.json'):
+        print '[ERROR]: data/valid_projects.json does not exist!'
+        return []
+
+    project_list = []
+    fp = open('data/valid_projects.json', 'r')
+    prj_json = json.load(fp)
+    fp.close()
+
+    for p in prj_json:
+        project_list.append(Project.parse_project(p, 0))
+
+    return project_list
+
+
+

### 2014-02-20 tools/local_worker.py

@@ -1,0 +1,131 @@
+import os
+import zipfile
+from helpers import mongo_helper
+
+
+def has_classes(filename):
+    try:
+        if zipfile.is_zipfile(filename):
+            z = zipfile.ZipFile(filename)
+            for f in z.namelist():
+                if f.endswith('.class'):
+                    print 'Valid JAR file: %s' % (filename,)
+                    return True
+        else:
+            print '%s is not a zipfile (has_classes)' % (filename,)
+
+        return False
+    except Exception, e:
+        return False
+
+
+def get_jar_size(filename):
+    size = 0
+
+    if zipfile.is_zipfile(filename):
+        try:
+            z = zipfile.ZipFile(filename)
+            for info in z.infolist():
+                if info.filename.endswith('.class'):
+                    size += info.file_size
+
+            return size
+        except Exception, e:
+            return 0
+    else:
+        print '%s is not a zipfile (get_jar_size)' % (filename,)
+        return 0
+
+
+def convert_findbugs_xml(findbugs_xml):
+    import xmldict
+    import json
+
+    xml_data = open(findbugs_xml, 'r').read()
+    result_json = json.loads(json.dumps(xmldict.parse(xml_data)).replace('"@', '"'))
+
+    # -1: jar, -2: version, -3: artifact_id, -4: group_id
+    _full_name = result_json.get('BugCollection', {}).get('Project', {}).get('Jar', None)
+
+    if _full_name is None:
+        raise Exception('Jar tag is not found (%s)' % (result_json,))
+
+    print 'Processing ... %s' % (_full_name,)
+
+    _jar_filename = os.path.basename(_full_name)
+    _pom_filename = _full_name.replace('.jar', '.pom')
+    _metadata_filename = '%s/maven-metadata.xml' % ('/'.join(_full_name.split('/')[:-2]),)
+    _dependencies = []
+    _versions = []
+
+    _version = None
+    _artifact_id = None
+    _group_id = None
+    _version_order = 0
+
+    if os.path.exists(_pom_filename):
+        try:
+            _pom_json = json.loads(json.dumps(xmldict.parse(open(_pom_filename, 'r').read())))
+            _dependencies = _pom_json.get('project', {}).get('dependencies', {}).get('dependency', [])
+        except Exception, e:
+            print 'Could not download/parse data from %s (%s)' % (_pom_filename, e)
+
+    if os.path.exists(_metadata_filename):
+        try:
[…]

### 2014-02-20 tools/setup.py

@@ -1,0 +1,4 @@
+from distutils.core import setup
+import py2exe
+
+setup(console=['process-win.py'])

### 2014-02-20 tools/valid_projects.py

@@ -1,0 +1,33 @@
+import json
+from helpers.data_helper import load_projects_json, save_to_file
+from helpers.mongo_helper import MongoProjectIterator
+
+
+def main():
+    projects = load_projects_json()
+    valid_projects = []
+    total = len(projects)
+    valid = 0
+    counter = 0
+
+    for p in projects:
+        counter += 1
+        key = '%s||%s' % (p.group_id(), p.artifact_id())
+        piter = MongoProjectIterator(p.group_id(), p.artifact_id(), fields=['JarMetadata.version_order'])\
+
+        piter.evolution_list()
+        print '[%d:%d:%d] Checking ... %s' % (counter, valid, total, key),
+
+        if piter.valid():
+            valid_projects.append(key)
+            print ' ... Valid (%d versions)' % (len(piter.evolution_list()))
+            valid += 1
+        else:
+            print ' ... Invalid (%d versions)' % (len(piter.evolution_list()))
+
+    print 'Total: %d, Valid: %d' % (total, valid)
+    save_to_file('valid_projects.json', json.dumps(valid_projects))
+
+
+if __name__ == "__main__":
+    main()

### 2014-02-20 tools/xmldict.py

@@ -1,0 +1,250 @@
+#!/usr/bin/env python
+"Makes working with XML feel like you are working with JSON"
+
+from xml.parsers import expat
+from xml.sax.saxutils import XMLGenerator
+from xml.sax.xmlreader import AttributesImpl
+try: # pragma no cover
+    from cStringIO import StringIO
+except ImportError: # pragma no cover
+    try:
+        from StringIO import StringIO
+    except ImportError:
+        from io import StringIO
+try: # pragma no cover
+    from collections import OrderedDict
+except ImportError: # pragma no cover
+    OrderedDict = dict
+
+try: # pragma no cover
+    _basestring = basestring
+except NameError: # pragma no cover
+    _basestring = str
+try: # pragma no cover
+    _unicode = unicode
+except NameError: # pragma no cover
+    _unicode = str
+
+__author__ = 'Martin Blech'
+__version__ = '0.3'
+__license__ = 'MIT'
+
+class ParsingInterrupted(Exception): pass
+
+class _DictSAXHandler(object):
+    def __init__(self,
+                 item_depth=0,
+                 item_callback=lambda *args: True,
+                 xml_attribs=True,
+                 attr_prefix='@',
+                 cdata_key='#text',
+                 force_cdata=False,
+                 cdata_separator='',
+                 postprocessor=None):
+        self.path = []
+        self.stack = []
+        self.data = None
+        self.item = None
+        self.item_depth = item_depth
+        self.xml_attribs = xml_attribs
+        self.item_callback = item_callback
+        self.attr_prefix = attr_prefix
+        self.cdata_key = cdata_key
+        self.force_cdata = force_cdata
+        self.cdata_separator = cdata_separator
+        self.postprocessor = postprocessor
+
+    def startElement(self, name, attrs):
+        self.path.append((name, attrs or None))
+        if len(self.path) > self.item_depth:
+            self.stack.append((self.item, self.data))
+            attrs = OrderedDict((self.attr_prefix+key, value)
+                for (key, value) in attrs.items())
+            self.item = self.xml_attribs and attrs or None
+            self.data = None
+
+    def endElement(self, name):
+        if len(self.path) == self.item_depth:
+            item = self.item
+            if item is None:
+                item = self.data
+            should_continue = self.item_callback(self.path, item)
+            if not should_continue:
+                raise ParsingInterrupted()
+        if len(self.stack):
+            item, data = self.item, self.data
[…]

### 2014-02-21 docs/msr.tex
messing around
split paragraphs
added table
work on sections 1 and 2

--- 2014-02-20 docs/msr.tex
@@
 used FindBugs, a tool that examines Java bytecode to detect
-numerous types of bugs. In this paper we present our data collection
-experiment and show our findings regarding software evolution.
+numerous types of bugs. In this paper we present our dataset. 
 \end{abstract}
@@
 
-In this paper we present: a) the experiment performed to obtain the
+In this paper we present: a) the construction process to obtain the
 collection of the metric results that the FindBugs tool produces 
@@
 
-\section{Data Collection Experiment}
+\section{Dataset Construction Process}
 \label{sec:exp}
 
-The data collection process started with the mirroring of the Maven repository.
-The repository typically contains the {\sc jar} files with sources and binary distributions, 
-{\sc xml} metadata files that contain the version list for each project and its dependencies and one 
-metadata file, also in {\sc xml} format, with specific data for each version.
+The dataset construction consisted of two basic steps,
+namely: {\it data provenance} and {\it FindBugs results
+collection}. Table~\ref{tbl:tools-size} presents some
+metrics concerning the tools created for
+the process.
 
-We exported a list of all the {\sc jar} files in the repository and initially we excluded those
-that contained the source distribution for the projects. Then we kept all those {\sc jar}s that 
-referred to Java projects, because Findbugs analyzes only applications written in Java,
-and the Maven repository hosts projects from languages other than Java such as Scala, Groovy,
-Clojure, etc.
+\begin{table}
+\centering
+\begin{tabular}{l r}
+ \hline
+\verb|Python Scripts| & 14\\
+\verb|Lines of Code| & 1256\\
+\verb|Code Size (KB)| & 92\\
+\hline
+\end{tabular}
+\caption{Size metrics concerning
+the tools created for
+the dataset construction process.}
+\label{tbl:tools-size}
+\end{table}
 
-The initial snapshot of the repository was obtained in January 2012 and those experinment took
-place in the end of 2012. In the meantime, several versions were released for some of the selected project.
-We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
-all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
-the missing ones.
+{\bf Data Provenance} Initially, we obtained a snapshot
+(January 2012) of the Maven repository and handled it
+locally to retrieve a list
+of all the names of the project versions that existed in
+it. In addition, we filtered out projects written in programming
+languages other than Java (such as Scala, Groovy, Clojure, etc.)
+because FindBugs analyzes only Java bytecode.
+Since our construction process took place at the end of 2012,
+several versions were released for some of the projects.
+Thus, we cross-checked
+the local versions with those online\footnote{\url{http://mirrors.ibiblio.org/maven2/}}
+and added the missing ones.
+The statistic measurements concerning
+the repository can be seen in Table~\ref{tbl:repository}
+and the distribution of version
+count among the selected projects is
+presented in Figure~\ref{fig:version-count}.
 
-The whole process produced a file list with all the valid {\sc jar} files for our experinment.
+\begin{figure}[t]
+	\centering
+	\includegraphics[scale=0.37]{version_count.pdf}
+	\caption{Distribution of version count among project population.}
+	\label{fig:version-count}
+\end{figure}
 
-In particular, we obtained a snapshot (January 2012) of
-the repository and handled it locally to retrieve a list of all
-the names of the Java project versions that existed in it.
-The statistic measurements concerning the repository can be seen in 
-Table~\ref{tbl:repository}.
+%The first is to filter out non-Java jars... for that we used the following heuristics:
 
-With the {\sc jar} list at hand, we created a series of processing tasks
-and added them to a task queue mechanism (a Rabbit{\sc mq} message
-broker). Then we executed twenty five workers (custom Python scripts)
-that checked out tasks from the queue, processed each project version
-and stored the results to the data
-repository (a Mongo{\sc db} database system).
+%- heuristic 1
+%- heuristic 2
 
-A typical processing cycle of a worker included the following steps: after
-the worker spawned, it requested a task from the queue. This task contained
-the {\sc jar} name, which was typically a project version that was downloaded locally.
-First, specific {\sc jar} metadata were calculated and stored
-(see Table~\ref{tbl:metadata-description}).
-Such metadata included
-its size, its dependencies, and a number that
-represented the ordinal version number
-of the release. This number was derived from an {\sc xml} file that
-accompanies every project in the Maven repository called {\it
-maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
-also stored in the data repository. 
+%The data collection process started with the mirroring of the Maven repository.
+%The repository typically contains the {\sc jar} files with sources and binary distributions, 
+%{\sc xml} metadata files that contain the version list for each project and its dependencies and one 
+%metadata file, also in {\sc xml} format, with specific data for each version.
+
+%We exported a list of all the {\sc jar} files in the repository and initially we excluded those
+%that contained the source distribution for the projects. Then we kept all those {\sc jar}s that 
+%referred to Java projects, because Findbugs analyzes only applications written in Java,
+%and the Maven repository hosts projects from languages other than Java such as Scala, Groovy,
+%Clojure, etc.
+
+%The initial snapshot of the repository was obtained in January 2012 and those experinment took
+%place in the end of 2012. The statistic measurements concerning the repository can be seen in 
+%Table~\ref{tbl:repository}. In the meantime, several versions were released for some of the selected project.
+%We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
+%all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
+%the missing ones.
+
+{\bf FindBugs Results Collection} The dataset
+size prohibited the analysis
+on a single host. For this reason,
+we opted for distributed processing.
+A schematic representation of the collection of
+the FindBugs metric results can be seen in Figure~\ref{fig:arch}.
+
+%We created an architecture that can be seen in Fig (add figure).
+%Jobs were put into the queue, results in Mongo.... It took 29 (?)
+%hours, that many records were produced that many records failed
+%because of reasons 12,,3 etc
+
+In particular, we created a series of processing tasks
+based on the {\sc jar} list from the
+previous step, and added them to a task queue mechanism (a
+Rabbit{\sc mq} message broker). Then we executed twenty five
+workers (custom Python scripts) that checked out tasks from
+the queue, processed each project version and stored the
+results to the data repository (a Mongo{\sc db} database system).
+The collection process lasted for approximately four and
+a half days.
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[scale=0.73]{figures/arch.pdf}
+  \end{center}
+  \caption{The data processing architecture.}
+  \label{fig:arch}
+\end{figure}
+
+A typical processing cycle of a worker included the
+following steps: after the worker spawned, it requested a task
+from the queue. This task contained the {\sc jar} name, which
+was typically a project version that was downloaded locally.
+First, specific {\sc jar} metadata were calculated and stored (see
+Table~\ref{tbl:metadata-description}).
+Such metadata included its size, its dependencies,
+and a number that represented the ordinal version
+number of the release. This number was derived from an {\sc xml}
+file that accompanies every project in the Maven repository
+called {\it maven-metadata.xml}. Then, FindBugs was invoked
+by the worker and its results were also stored in the data
+repository.
+Note that before invoking FindBugs,
+the worker checked if the {\sc jar} is valid in terms of implementation.
+For instance, for every {\sc jar} the worker checked
+if there were any {\it .class} files before invoking FindBugs.
 FindBugs separates software bugs into nine
 categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-(including {\it Bad Practice}, {\it Security}, {\it Performance} and others)
-and reports bug collections that include all the bugs discovered in a
-{\sc jar} file. For every registered bug, there are numerous accompanying features
-like the class, the method and the line that the bug was found.
-Its results, also include additional information like
-the number of classes included in the examined {\sc jar}
-and others.
-When the task was completed the queue
-was notified and the next task was requested.
+(including {\it Bad Practice}, {\it Security}, {\it Performance} and
+others) and reports bug collections that include all the bugs
+discovered in a {\sc jar} file. For every registered bug, there are
+numerous accompanying features like the class, the method
+and the line that the bug was found. Its results, also include
+additional information like the number of classes included in
+the examined {\sc jar} and others. When the task was completed
+the queue was notified and the next task was requested.
 
-A threat to the internal
-validity of our experiment could be the false
+When the processing was completed, we ran some tests
+to check the validity of the results.
+A common issue that we discovered was the out-of-memory
+crashes of Findbugs, which demanded the repetition of the process
+for the corresponding {\sc jar}s, with the appropriate
+settings in the Java runtime environment.
+%The sanitisation process was consisted of four iterations,
+%until all our scripts indicate that our data was correct.
+
+A threat to the internal validity of our experiment could be the false
 alarms of the FindBugs tool~\cite{AP10, HP04}.
@@
 \verb|version| & The version of the project in the repository. \\
+\verb|version_number| & The ordinal version number of the release. \\
 \verb|version_list| & A list of all available version's of this project. \\

### 2014-02-21 docs/msr.tex
update based on gousiosg comments

@@
 was typically a project version that was downloaded locally.
-First, specific {\sc jar} metadata were calculated and stored (see
-Table~\ref{tbl:metadata-description}).
-Such metadata included its size, its dependencies,
-and a number that represented the ordinal version
-number of the release. This number was derived from an {\sc xml}
-file that accompanies every project in the Maven repository
-called {\it maven-metadata.xml}. Then, FindBugs was invoked
+First, specific {\sc jar} metadata were calculated and stored
+(see Section~\ref{sec:data}).
+Then, FindBugs was invoked
 by the worker and its results were also stored in the data
@@
 if there were any {\it .class} files before invoking FindBugs.
-FindBugs separates software bugs into nine
-categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
-(including {\it Bad Practice}, {\it Security}, {\it Performance} and
-others) and reports bug collections that include all the bugs
-discovered in a {\sc jar} file. For every registered bug, there are
-numerous accompanying features like the class, the method
-and the line that the bug was found. Its results, also include
-additional information like the number of classes included in
-the examined {\sc jar} and others. When the task was completed
+When the task was completed
 the queue was notified and the next task was requested.
@@
 for the corresponding {\sc jar}s, with the appropriate
-settings in the Java runtime environment.
+settings in the Java Runtime Environment ({\sc jre}).
 %The sanitisation process was consisted of four iterations,
@@
 
-A threat to the internal validity of our experiment could be the false
-alarms of the FindBugs tool~\cite{AP10, HP04}.
-Specifically, reported security bugs may not
-be applicable to an application's typical use context.
-For instance, FindBugs could report an {\sc sql}
-injection vulnerability~\cite{RL12}
-in an application that receives no external input.
-In this particular context, this would be a false
-positive alarm.
+\section{Data}
+\label{sec:data}
 
-\section{Data and Findings}
-\label{sec:find}
+\begin{table}[t]
+\centering
+\scalebox{0.80}{
+\begin{tabular}{l p{16em}}
+\hline
+Category & Description\\
+\hline
+Bad Practice & Violations of recommended and essential
+coding practice. \\
+Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
+that was probably not what the developer intended. \\
+Experimental & Includes unsatisfied obligations. For instance,
+forgetting to close a file. \\
+Internationalization (i18n) & Indicates the use of non-localized methods. \\
+Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
+Performance & Involves inefficient memory usage allocation, usage 
+of non-static classes. \\
+Style & Code that is confusing, or
+written in a way that leads to errors.\\
+Malicious Code & Involves variables or fields exposed to classes that should
+not be using them. \\
+Security & Involves input validation issues, unauthorized database connections
+and others. \\
+\hline
+\end{tabular}}
+\caption{Bug categorization according to FindBugs.}
+\label{tbl:bug-cat}
+\end{table}
+
+As we mentioned earlier our data was stored in a
+Mongo{\sc db} database.
+%FindBugs incorporates a priori an ability to perform
+%sophisticated queries on bug databases and
+%track warnings across multiple versions of code being
+%studied.\footnote{\url{http://findbugs.sourceforge.net/manual/datamining.html}}
+FindBugs separates software bugs into nine categories (see
+Table~\ref{tbl:bug-cat}) and reports {\it bug collections}
+that include all the bugs
+discovered in a {\sc jar} file. For every registered bug, there are
+numerous accompanying features like the class, the method
+and the line that the bug was found. Its results, also include
+additional information like the number of classes included in
+the examined {\sc jar} and others.
+FindBugs though,
+outputs its results in  {\sc xml} format.
+Hence, all the data were
+converted to the {\sc json} format
+by mapping all {\sc xml} elements to {\sc json} objects.
 
@@
  \hline
+\verb|version| & The version of the project in the repository. \\
+\verb|version_order| & The ordinal version number of the release. \\
+\verb|jar_size| & The size of the {\sc jar} file. \\
+\verb|dependencies| & List of all dependencies for the project. \\
+%\verb|version_list| & A list of all available version's of this project. \\
+\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
 \verb|jar_filename| & {\sc jar}'s filename. \\
-\verb|jar_size| & The size of the {\sc jar} file. \\
-\verb|version| & The version of the project in the repository. \\
-\verb|version_number| & The ordinal version number of the release. \\
-\verb|version_list| & A list of all available version's of this project. \\
 \verb|artifact_id| & The artifact {\sc id} of the project in Maven repository. \\
-\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
-\verb|dependencies| & List of all dependencies for the project. \\
  \hline
@@
 
-As we mentioned earlier our data was stored in a
-Mongo{\sc db} database.
-FindBugs incorporates a priori an ability to perform
-sophisticated queries on bug databases and
-track warnings across multiple versions of code being
-studied.\footnote{\url{http://findbugs.sourceforge.net/manual/datamining.html}}
-FindBugs though,
-outputs its results in  {\sc xml} format.
-Hence all the data were
-converted to the {\sc json} format
-by mapping all {\sc xml} elements to {\sc json} objects.
-Since Mongo{\sc db} provides a rich query interface,
-it was easy to either create
-simple scripts to find out
-how software bugs are distributed among the
-repository. Figure~\ref{fig:bug-per}
-actually, illustrates this distribution.
+As we mentioned in Section~\ref{sec:exp}, our
+workers calculated and stored specific metadata together
+with the FindBugs results.
+Such metadata included its size (in terms of bytecode),
+its dependencies
+(derived from the {\it pom.xml} file),
+and a number that represented the ordinal version
+number of the release (see also
+Table~\ref{tbl:metadata-description}).
+This number was derived from an {\sc xml}
+file that accompanies every project in the Maven repository
+called {\it maven-metadata.xml}.
+The following listing contains a sample document
+containing all the above information (note
+that the results of FindBugs are too large to
+show. To see a complete instance please visit our
+{\tt github} repository --- see Section~\ref{sec:conc}):
+
+\begin{verbatim}
+{"JarMetadata": {
+    "version": "1.0.0",
+    "version_order": "1",
+    "jar_size": "34768",
+    "dependencies": [
+        {
+            "version" : "2.0",
+            "groupId" : "org.apache.maven",
+            "artifactId" : "maven-project"
+        },
+        { /* other dependencies */ }
+    ],
+    "group_id": "org.apache.myfaces.buildtools",
+    "jar_filename": "myfaces-jdev-plugin-1.0.0.jar",
+    "artifact_id": "myfaces-jdev-plugin",
+    }, 
+ "BugCollection": { /* FindBugs data */ }
+}
+\end{verbatim}
 
@@
 
+\section{Dataset Exploitation}
+\label{sec:exploit}
+
+Since Mongo{\sc db} provides a rich query interface,
+it was easy to create
+simple scripts to find out
+how software bugs are distributed among the
+repository (see Figure~\ref{fig:bug-per}).
+
 Together with our dataset, we have also created a series of
@@
 the evolution of software bugs.
-Table~\ref{tbl:bugsperversion} shows the relation between
-bugs and time. This relation, can be traced from the number of
-bugs per category in each project version. Specifically, we
-calculated the Spearman correlations between the defects
+First, based on the dataset we produced some metadata
+that contained the number of
+bugs per category in each project version. Based
+on these metadata we estimated the relation between
+bugs and time (see Table~\ref{tbl:bugsperversion}).
+Specifically, we calculated the Spearman correlations between the defects
 count and the ordinal version number across all projects.
 The zero tendency that can be seen on Table~\ref{tbl:bugsperversion}
-though, applies to all versions of all projects together.
-Thus, we also performed Spearman correlations between bug counts and version
-ordinals in all projects we examined individually. These paint a different picture
-from the above table, shown in Figure~\ref{fig:bugsversionscorr}. The
-spike in point zero is explained by the large number of projects for
-which no correlation could be established---the scale is
-logarithmic.
-Figure~\ref{fig:bugdiffs}, presents a histogram of the changes
-of different bug counts in
-project versions. In most cases, a bug count does not change between
-versions; but when it does change, it may change upwards or downwards.
+applies to all versions of all projects together.
 
@@
 
-\begin{figure*}[p]
-  \centering
-  \includegraphics[scale=0.30]{bugsversionscorr}
-  \caption{Histograms of correlations between bug counts and version
-    ordinals per project. In brackets the total population size and
-    the number of no correlation instances.}
-  \label{fig:bugsversionscorr}
-  \centering
-  \includegraphics[scale=0.35]{bugdiffs}
-  \caption{Changes in bug counts between versions.}
-  \label{fig:bugdiffs}
-\end{figure*}
-
-To examine the relation between the persistence of different kinds of
-bugs we used as a persistence
-indicator the number of versions a bug remains open in a project. To
-``tag" a bug we created a bug identifier by using the type of the bug,
-the method name and the class name in which the bug was found in. We
-chose not to use the line number of the location of the bug since it
-could change from version to version and after a possible code
-refactoring. We grouped the persistence numbers by bug categories and
-then performed a Mann-Whitney $U$ test among all bug
-category pairs. The results are presented in
-Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
-brackets show pairs where no statistically significant difference was
-found.
-
-In addition, we explored the relation between defects with the size of a project
+In addition, we explored the relation between defects
+with the size of a project
 version, measured by the size of its {\sc jar} file by carrying out
@@
 between all bug categories. To establish these correlations,
-we calculated the
-correlations between the number of distinct bugs that appeared in
-a project throughout its lifetime.
+we calculated the correlations between the number of
+distinct bugs that appeared in a project throughout its lifetime.
 
@@
   \includegraphics[scale=0.43]{corrplot.pdf}
-  \caption{Correlation matrix plot for bug categories.}
+  \caption{Correlation matrix plot for bug categories.
+Blue color indicates positive correlation.
+The darker the color (and the more acute the ellipsis slant),
+the stronger the correlation.}
   \label{fig:corrplot}
 \end{figure}
+
+Research concerning the examination of specific bugs
+can also be facilitated by our dataset. For instance,
+we have examined the characteristics of security
+bugs in a previous paper~\cite{MKLGS13}
+based on this dataset.
+
+\section{Limitations}
+\label{sec:limit}
+
+Limitations concerning out dataset involve some
+{\sc jar}s that were in the initial {\sc jar} list
+created during data provenance but when the
+FindBugs result collection was performed, they
+were not online.
+
+A threat to the internal validity of our experiment could be the false
+alarms of the FindBugs tool~\cite{AP10, HP04}.
+Specifically, reported security bugs may not
+be applicable to an application's typical use context.
+For instance, FindBugs could report an {\sc sql}
+injection vulnerability~\cite{RL12}
+in an application that receives no external input.
+In this particular context, this would be a false
+positive alarm.
+
+A disadvantage of our dataset is that as projects evolve
+the dataset gets older. Also, even if we checked for
+new versions before after data provenance and before
+the results collection, we did not checked for new
+projects added during this time frame.
 
@@
 all the software bug that it contains among with some
-other metadata. We have also shown how our data can be
+other metadata mentioned in Section~\ref{sec:exploit}.
+We have also shown how our data can be
 used to extract results concerning software evolution.
-Research concerning the examination of specific bugs
-can also be facilitated by our dataset. For instance,
-we have examined the characteristics of security
-bugs in a previous paper~\cite{MKLGS13}
-based on this dataset.
+
+Note that our experiment can be duplicated
+in order to collect metric results from other tools that
+examine Java programs like
+{\sc cjkm}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}}
+that calculates Chidamber and Kemerer
+object-oriented metrics~\cite{CK91},
+{\it Java Pathfinder}\footnote{\url{http://babelfish.arc.nasa.gov/trac/jpf/wiki}}
+that performs
+model checking~\cite{CEES09} on Java bytecode programs,
+and others. To achieve this, instead of invoking
+FindBugs, our worker can invoke such tools.
 
@@
 
-\begin{landscape}
-  \begin{table}
-    \setlength{\extrarowheight}{0.10cm}
-    \caption{Bug persistence comparison.}
-    \label{tbl:bug_persistence}
-    \resizebox{0.95\columnwidth}{!}{
-    \input{bug_persistence.tex}}\\
-    The matrix presents pairwise Mann-Whitney $U$ test results
-    between the different bug categories. Each cell contains the test
-    result (the value of $U$), the $p$-value, the average for each
-    category and the sample size for each category. Cells in brackets show
-    pairs where no statistically significant difference was found.
-  \end{table}
-\end{landscape}
-
 \end{document}

### 2014-02-21 docs/msr.tex
addressed Panos' comments

@@
 used FindBugs, a tool that examines Java bytecode to detect
-numerous types of bugs. In this paper we present our dataset. 
+numerous types of bugs. In this paper we present the dataset
+that was produced from this experiment.
+The dataset contains the metric results that FindBugs reports for
+every project version included in the ecosystem. For every
+version we also stored specific metadata such as the {\sc jar}'s
+size, it's dependencies and others. Finally, we present
+how researchers can use our dataset to produce interesting results.
 \end{abstract}
@@
 The dataset construction consisted of two basic steps,
-namely: {\it data provenance} and {\it FindBugs results
+namely: {\it data cleaning} and {\it FindBugs results
 collection}. Table~\ref{tbl:tools-size} presents some
@@
 
-{\bf Data Provenance} Initially, we obtained a snapshot
+{\bf Data Cleaning} Initially, we obtained a snapshot
 (January 2012) of the Maven repository and handled it
@@
 the local versions with those online\footnote{\url{http://mirrors.ibiblio.org/maven2/}}
-and added the missing ones.
+and supplemented the missing {\sc jar}s that have been
+added to the repository during this period.
 The statistic measurements concerning
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
   \begin{center}
@@
 numerous accompanying features like the class, the method
-and the line that the bug was found. Its results, also include
+and the line that the bug was found. FindBug's results, also include
 additional information like the number of classes included in
@@
 
-\begin{table}
+\begin{table}[b]
 \centering
@@
 with the FindBugs results.
-Such metadata included its size (in terms of bytecode),
+Such metadata included the {\sc jar}'s size (in terms of bytecode),
 its dependencies
@@
 called {\it maven-metadata.xml}.
-The following listing contains a sample document
-containing all the above information (note
+The following listing shows the format of the
+information we collected (note
 that the results of FindBugs are too large to
 show. To see a complete instance please visit our
-{\tt github} repository --- see Section~\ref{sec:conc}):
+GitHub repository --- see Section~\ref{sec:conc}):
 
@@
 
-\section{Dataset Exploitation}
+\section{Harnessing Our Dataset}
 \label{sec:exploit}
@@
 
-\begin{table}[tphp]
+\begin{table}[b]
     \centering
@@
 {\sc jar}s that were in the initial {\sc jar} list
-created during data provenance but when the
+created during data cleaning but when the
 FindBugs result collection was performed, they
@@
 A threat to the internal validity of our experiment could be the false
-alarms of the FindBugs tool~\cite{AP10, HP04}.
+alarms of the FindBugs tool~\cite{AP10}.
 Specifically, reported security bugs may not
@@
 For instance, FindBugs could report an {\sc sql}
-injection vulnerability~\cite{RL12}
+injection vulnerability
 in an application that receives no external input.
@@
 the dataset gets older. Also, even if we checked for
-new versions before after data provenance and before
+new versions before data cleaning and before
 the results collection, we did not checked for new
@@
 for every {\sc jar} of the Maven central repository,
-all the software bug that it contains among with some
+all the software bugs that it contains among with some
 other metadata mentioned in Section~\ref{sec:exploit}.

### 2014-02-21 docs/msr.tex
minor changes
minor changes - fixes

@@
 that was produced from this experiment.
-The dataset contains the metric results that FindBugs reports for
-every project version included in the ecosystem. For every
+The dataset contains the metrics results that FindBugs reports for
+every project version (a {\sc jar}) included in the ecosystem. For every
 version we also stored specific metadata such as the {\sc jar}'s
-size, it's dependencies and others. Finally, we present
-how researchers can use our dataset to produce interesting results.
+size, its dependencies and others. Our dataset can be used to produce
+interesting research results, as we show in specific examples.
 \end{abstract}
@@
 In this paper we present: a) the construction process to obtain the
-collection of the metric results that the FindBugs tool produces 
+collection of the metrics results that the FindBugs tool produces 
 for every project version of the repository (115,214 {\sc jar}s)
@@
 A schematic representation of the collection of
-the FindBugs metric results can be seen in Figure~\ref{fig:arch}.
+the FindBugs metrics results can be seen in Figure~\ref{fig:arch}.
 
@@
 
-\section{Data}
+\section{Dataset Contents}
 \label{sec:data}
@@
 Note that our experiment can be duplicated
-in order to collect metric results from other tools that
+in order to collect metrics results from other tools that
 examine Java programs like

### 2014-02-21 docs/msr.tex
changes based on dds' comments

@@
 Examining software ecosystems can provide the research community
-with useful information. To examine the ecosystem of
-the Maven central repository (approximately 265{\sc gb} of data),
-we performed an experiment where we statically analyzed the
-repository to detect its software bugs. For our analysis we
-used FindBugs, a tool that examines Java bytecode to detect
-numerous types of bugs. In this paper we present the dataset
-that was produced from this experiment.
+with data regarding artifacts, processes, and communities.
+We present a dataset obtained from the Maven central repository
+ecosystem (approximately 265{\sc gb} of data) by statically analyzing
+the repository to detect potential software bugs.
+For our analysis we used FindBugs, a tool that examines Java
+bytecode to detect numerous types of bugs.
 The dataset contains the metrics results that FindBugs reports for
@@
 
-A threat to the internal validity of our experiment could be the false
+A threat to the internal validity of our dataset
+construction process could be the false
 alarms of the FindBugs tool~\cite{AP10}.
@@
 
-Note that our experiment can be duplicated
+Note that our data collection process can be duplicated
 in order to collect metrics results from other tools that

### 2014-02-21 docs/msr.tex
fina changes

@@
 the repository to detect potential software bugs.
-For our analysis we used FindBugs, a tool that examines Java
+For our analysis we used {\it FindBugs}, a tool that examines Java
 bytecode to detect numerous types of bugs.
@@
 
-\terms{Static Analysis, Software Ecosystems}
+\terms{Static Analysis, Software Ecosystems.}
 
-\keywords{Maven Repository, FindBugs, Software Bugs}
+\keywords{Maven Repository, FindBugs, Software Bugs.}
 
@@
 collection of the metrics results that the FindBugs tool produces 
-for every project version of the repository (115,214 {\sc jar}s)
-and b) how researchers can use the dataset and produce
+for every project version of the repository (115,214 {\sc jar}s),
+b) our dataset
+and c) how researchers can use the dataset and produce
 meaningful results.
@@
 
-When the processing was completed, we ran some tests
+When the data collection was completed, we ran some tests
 to check the validity of the results.
@@
 \centering
-\scalebox{0.80}{
+\scalebox{0.79}{
 \begin{tabular}{l p{16em}}
@@
 
-Together with our dataset, we have also created a series of
+Furthermore, we have created a series of
 scripts to exhibit how the dataset can be used
@@
 
-Finally, Figure~\ref{fig:corrplot} presents the pairwise correlations
+Figure~\ref{fig:corrplot} presents the pairwise correlations
 between all bug categories. To establish these correlations,
@@
 the dataset gets older. Also, even if we checked for
-new versions before data cleaning and before
+new project versions that could have been added
+to the repository after the data cleaning and before
 the results collection, we did not checked for new
@@
 
-The complete set of our data and source code
-can be found at
+The complete set of our data and source code can be found at
 \url{https://github.com/bkarak/data_paper_msr2014}.

### 2014-03-19 docs/msr.tex
work on the camera ready version

@@
 Examples of such ecosystems include Python's
-{\sc p}y{\sc py}\footnote{\url{http://pypy.org/}}
+{\sc p}y{\sc py}\footnote{\small \url{http://pypy.org/}}
 (Python Package Index), Perl's
-{\sc cpan}\footnote{\url{http://www.cpan.org/}}
+{\sc cpan}\footnote{\small \url{http://www.cpan.org/}}
 (Comprehensive Perl Archive Network), Ruby's
-RubyGems\footnote{\url{http://rubygems.org/}}
-and the Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}
+RubyGems\footnote{\small \url{http://rubygems.org/}}
+and the Maven Central Repository.\footnote{\small \url{http://mvnrepository.com/}}
 
 Maven is a build automation tool used primarily for Java projects and it is
-hosted by the Apache Software Foundation.\footnote{\url{http://maven.apache.org/}}
+hosted by the Apache Software Foundation.\footnote{\small \url{http://maven.apache.org/}}
 It uses {\sc xml} to describe the software project being built, its dependencies
@@
 and Maven plug-ins from the {\it Maven central
-repository},\footnote{\url{http://mvnrepository.com/}}
+repository},\footnote{\small \url{http://mvnrepository.com/}}
 and stores them in a local cache. The repository can be updated with
@@
 To statically analyze the Maven repository
-we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
+we used {\it FindBugs},\footnote{\small \url{http://findbugs.sourceforge.net/}}
 a static analysis tool that examines bytecode to detect software bugs
@@
 \centering
+\scalebox{0.94}{
 \begin{tabular}{l r}
@@
 \end{tabular}
+}
 \caption{Descriptive statistic measurements for the Maven repository.}
@@
 Thus, we cross-checked
-the local versions with those online\footnote{\url{http://mirrors.ibiblio.org/maven2/}}
+the local versions with those online\footnote{\small \url{http://mirrors.ibiblio.org/maven2/}}
 and supplemented the missing {\sc jar}s that have been
@@
   \begin{center}
-    \includegraphics[scale=0.73]{figures/arch.pdf}
+    \includegraphics[scale=0.66]{figures/arch.pdf}
   \end{center}
@@
 \centering
-\scalebox{0.79}{
+\scalebox{0.78}{
 \begin{tabular}{l p{16em}}
@@
 
+\begin{small}
 \begin{verbatim}
@@
 \end{verbatim}
+\end{small}
 
@@
     \centering
+\scalebox{0.94}{
         \input{bugsperversion.tex}
+}
 	\caption{Correlations between version and defects count.}
@@
 
-Figure~\ref{fig:corrplot} presents the pairwise correlations
+Table~\ref{tbl:corrplot} presents the pairwise correlations
 between all bug categories. To establish these correlations,
@@
     \centering
+\scalebox{0.94}{
     \input{jarsizecorr.tex}
+}
     \caption{Correlations between {\sc jar} size and defects count.}
@@
 
-\begin{figure}
+\begin{table*}[hbt]
     \centering
-  \includegraphics[scale=0.43]{corrplot.pdf}
-  \caption{Correlation matrix plot for bug categories.
-Blue color indicates positive correlation.
-The darker the color (and the more acute the ellipsis slant),
-the stronger the correlation.}
-  \label{fig:corrplot}
-\end{figure}
+\scalebox{0.86}{
+    \input{corrmatrix.tex}
+}
+    \caption{Correlations between bug categories.}
+    \label{tbl:corrplot}
+\end{table*}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[scale=0.43]{corrplot.pdf}
+%  \caption{Correlation matrix plot for bug categories.
+%Blue color indicates positive correlation.
+%The darker the color (and the more acute the ellipsis slant),
+%the stronger the correlation.}
+%  \label{fig:corrplot}
+%\end{figure}
 
@@
 examine Java programs like
-{\sc cjkm}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}}
+{\sc cjkm}\footnote{\small \url{http://www.spinellis.gr/sw/ckjm/}}
 that calculates Chidamber and Kemerer
 object-oriented metrics~\cite{CK91},
-{\it Java Pathfinder}\footnote{\url{http://babelfish.arc.nasa.gov/trac/jpf/wiki}}
+{\it Java Pathfinder}\footnote{\small \url{http://babelfish.arc.nasa.gov/trac/jpf/wiki}}
 that performs
@@
 
+\section{Acknowledgments}
+This research has been co-financed by the
+European Union (European Social Fund---{\sc esf}) 
+and Greek national funds through the Operational
+Program ``Education and Lifelong Learning" of the
+National Strategic Reference Framework
+({\sc nsrf})---Research Funding Program: 
+Thalis---Athens University of Economics and
+Business---Software Engineering Research Platform.
+
 \bibliographystyle{abbrv}
